### 2024-09-10 causalDT-manuscript/notebooks/paper_figures.Rmd
update sims and paper figures

---
title: "Causal Distillation Trees"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Distilled Rlasso",
  "Virtual Twins",
  "Causal Tree (pruned)",
  "Causal Tree (unpruned)",
  "Linear Regression",
  "Lasso"
)
COLORS <- c(
  # "Distilled Causal Forest" = "#3153A5",
  "Distilled Causal Forest" = "#1f5d8f",
  # "Distilled Causal Forest" = "#5d8cae",
  # "Distilled Rboost" = "#94B1c9",
  # "Distilled Rboost" = "#678096",
  ## "Distilled Rboost" = "#79b2dd",
  "Distilled Rboost" = "#6aafe4",
  # "Distilled Rboost" = "#6DA7D3",
  # "Distilled Rboost" = "#6DA7D3",
  # "Distilled Rlasso" = "#ACC2D0",
  "Distilled Rlasso" = "#9ab6c8",
  # "Distilled Rlasso" = "#B8CEDD",
  "Virtual Twins" = "#768c50",
  # "Virtual Twins" = "#6F9940",
  "Causal Tree (pruned)" = "#953a2f",
  "Causal Tree (unpruned)" = "#DB9685",
  # "Linear Regression" = "#DAA520",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
  # "Lasso" = "#e4d2a4"
)

FACET_LABS <- list(
  "0.2" = "Weak",
  "0.6" = "Moderate",
  "1" = "High"
)
signal_labeller <- function(variable, value) {
  if (variable == "tau_heritability") {
    return(FACET_LABS[as.character(value)])
  } else {
    return(value)
  }
}

FIG_DIR <- here::here("results", "figures")
if (!dir.exists(FIG_DIR)) {
  dir.create(FIG_DIR, recursive = TRUE)
}
```

# Simulations {.tabset .tabset-vmodern}

```{r}
EXP_NAME <- "Test"
source(here::here(file.path("meals", "setup.R")))
source(here::here(file.path("meals", "shared_dgps.R")))
source(here::here(file.path("meals", "shared_methods.R")))
source(here::here(file.path("meals", "shared_evaluators.R")))
source(here::here(file.path("meals", "shared_visualizers.R")))
source(here::here(file.path("meals", "shared_experiments.R")))
experiment <- experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )
```

```{r results = "asis"}
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND with Linear Covariates DGP",
  "Additive with Linear Covariates DGP",
  "OR with Linear Covariates DGP"
)
sim_results_dir <- here::here(
  file.path("results", "Unbiased W")
)

plt_subgroup_ls <- list()
plt_subgroup2_ls <- list()
plt_thresholds_ls <- list()
plt_stability_ls <- list()
plt_freq_ls <- list()
for (sim_name in sim_names) {
  cat(sprintf("\n\n## %s {.tabset .tabset-pills .tabset-square}\n\n", sim_name))

  # fit_results <- readRDS(
  #   file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
  # ) |>
  #   dplyr::filter(
  #     .method_name %in% !!KEEP_METHODS
  #   )
  # eval_results <- evaluate_experiment(experiment, fit_results)
  # viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  # 
  # plt_selection <- viz_results$`Subgroup Feature Selection Errors Plot` +
  #   ggplot2::scale_color_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::scale_fill_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   )
  # 
  # plt_cate <- viz_results$`Subgroup CATE Errors Plot` +
  #   ggplot2::scale_color_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::scale_fill_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::labs(
  #     y = "CATE RMSE"
  #   ) +
  #   vthemes::theme_vmodern(
  #     axis_title_size = 16,
  #     axis_text_size = 12,
  #     legend_title_size = 16,
  #     legend_text_size = 12
  #   ) +
  #   ggplot2::theme(
  #     strip.background = ggplot2::element_blank(),
  #     strip.placement = "outside"
  #     # strip.background = ggplot2::element_rect(
  #     #   color = "transparent", fill = "transparent"
  #     # ),
  #     # strip.text = ggplot2::element_text(
  #     #   color = "black", face = "bold", size = 16
  #     # )
  #   ) +
  #   ggplot2::guides(
  #     color = "none", fill = "none"
  #   )
  # 
  # pplt <- patchwork::wrap_plots(
  #   plt_selection, plt_cate, nrow = 1, guides = "collect",
  #   widths = c(3.5, 1)
  # ) &
  #   ggplot2::labs(x = NULL)
  # plt_subgroup_ls[[sim_name]] <- pplt
  # plt <- patchwork::wrap_elements(pplt) +
  #   ggplot2::labs(
  #     tag = expression(
  #       bold(paste("Proportion of Variance Explained in ", tau))
  #     )
  #   ) +
  #   ggplot2::theme(
  #     plot.tag = ggplot2::element_text(
  #       size = 16
  #     ),
  #     plot.tag.position = c(0.45, 0),
  #     plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  #   )
  # plt_subgroup2_ls[[sim_name]] <- plt

  fit_results <- readRDS(
    file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
  ) |>
    dplyr::filter(
      .method_name %in% !!KEEP_METHODS,
      tau_heritability %in% c(0.2, 0.6, 1)
    )
  eval_results <- evaluate_experiment(experiment, fit_results)
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)

  plt_thresholds <- viz_results$`Subgroup Thresholds Distribution Plot` +
    ggplot2::scale_color_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::scale_fill_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller)
  plt_thresholds_ls[[sim_name]] <- plt_thresholds

  plt_stability <- viz_results$`Subgroup Stability Diagnostics Plot`[[1]] +
    ggplot2::scale_color_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::scale_fill_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::facet_grid(~ tau_heritability, labeller = signal_labeller) +
    ggplot2::coord_cartesian(xlim = c(1, 4)) +
    ggplot2::scale_x_continuous(
      breaks = 1:4
    ) +
    ggplot2::labs(
      x = "Tree Depth",
      y = "Mean Jaccard Stability",
      color = "Method",
      fill = "Method"
    ) +
    vthemes::theme_vmodern(size_preset = "medium")
  plt_stability_ls[[sim_name]] <- plt_stability

  plt_nsplits <- viz_results$`Number of Splits Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.15, end = 0.95, option = "magma", limits = c(0., 7)
    )
  plt_ntrees <- viz_results$`Number of Trees Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.15, end = 0.95, option = "magma", limits = c(0, 100)
    )
  plt <- patchwork::wrap_plots(
    plt_ntrees, plt_nsplits, nrow = 1
  ) +
    patchwork::plot_layout(
      axis_titles = "collect_y"
    ) &
    ggplot2::labs(
      x = "Variable"
    )

  plt_freq_ls[[sim_name]] <- plt
}
```

```{r}
plt_subgroup <- purrr::map2(
  plt_subgroup_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_subgroup_ls[idx])
    tag <- LETTERS[idx]
    if (sim_name != names(plt_subgroup_ls[2])) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
      hjust <- 0.78
    } else {
      hjust <- 0.82
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, 0.48),
        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
      # ggplot2::theme(
      #   plot.title = ggplot2::element_text(
      #     size = 16, face = "bold", hjust = hjust
      #   ),
      #   plot.title.position = "plot"
      # )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  ) |>
  patchwork::wrap_elements() +
  ggplot2::labs(
    tag = expression(
      bold(paste("Proportion of Variance Explained in ", tau))
    )
  ) +
  ggplot2::theme(
    plot.tag = ggplot2::element_text(
      size = 16
    ),
    plot.tag.position = c(0.45, 0),
    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  )
ggplot2::ggsave(
  plt_subgroup, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9, 
  width = 14
)

plt_subgroup_cov <- purrr::map2(
  plt_subgroup_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name_orig <- names(plt_subgroup_ls[idx])
    sim_name <- stringr::str_replace(
      sim_name_orig, "with", "DGP with\n"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    if (sim_name_orig != names(plt_subgroup_ls[5])) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
      hjust <- 0.78
    } else {
      hjust <- 0.82
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.06, 0.48),
        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.75), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
      # ggplot2::theme(
      #   plot.title = ggplot2::element_text(
      #     size = 16, face = "bold", hjust = hjust
      #   ),
      #   plot.title.position = "plot"
      # )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  ) |>
  patchwork::wrap_elements() +
  ggplot2::labs(
    tag = expression(
      bold(paste("Proportion of Variance Explained in ", tau))
    )
  ) +
  ggplot2::theme(
    plot.tag = ggplot2::element_text(
      size = 16
    ),
    plot.tag.position = c(0.45, 0),
    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  )
ggplot2::ggsave(
  plt_subgroup_cov, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9, 
  width = 14
)
```

```{r}
plt_thresholds <- purrr::map2(
  plt_thresholds_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_thresholds_ls[idx])
    tag <- LETTERS[idx]
    plt <- plt +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1, guides = "collect"
  ) +
  patchwork::plot_layout(
    axes = "collect"
  )
ggplot2::ggsave(
  plt_thresholds, 
  filename = file.path(FIG_DIR, "sim_thresholds.pdf"),
  height = 10, 
  width = 11
)

plt_thresholds_cov <- purrr::map2(
  plt_thresholds_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name <- stringr::str_replace(
      names(plt_thresholds_ls[idx]), "with", "DGP with\n"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    plt <- plt +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1, guides = "collect"
  ) +
  patchwork::plot_layout(
    axes = "collect"
  )
ggplot2::ggsave(
  plt_thresholds_cov, 
  filename = file.path(FIG_DIR, "sim_thresholds_cov.pdf"),
  height = 10, 
  width = 11
)
```

```{r}
# plt_ntrees_ls <- purrr::map(
#   plt_freq_ls[1:3], ~ .x[[1]]
# )
# plt_nsplits_ls <- purrr::map(
#   plt_freq_ls[1:3], ~ .x[[2]]
# )
# plt_ntrees <- patchwork::wrap_plots(
#   plt_ntrees_ls, nrow = 1, guides = "collect"
# ) +
#   patchwork::plot_layout(
#     axes = "collect"
#   )

plt_freq <- purrr::map2(
  plt_freq_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_freq_ls[idx])
    tag <- LETTERS[idx]
    plt <- patchwork::wrap_elements(plt) +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        plot.tag.position = c(0.47, 1.02),
        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt_freq, 
  filename = file.path(FIG_DIR, "sim_freq.pdf"),
  height = 16, 
  width = 14
)

plt_freq_cov <- purrr::map2(
  plt_freq_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name <- stringr::str_replace(
      names(plt_freq_ls[idx]), "with", "DGP with"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    plt <- patchwork::wrap_elements(plt) +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        plot.tag.position = c(0.47, 1.02),
        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt_freq_cov, 
  filename = file.path(FIG_DIR, "sim_freq_cov.pdf"),
  height = 16, 
  width = 14
)
```

```{r}
plt_stability <- purrr::map2(
  plt_stability_ls, 1:length(plt_stability_ls),
  function(plt, idx) {
    plt_names <- names(plt_stability_ls)
    sim_name <- dplyr::case_when(
      stringr::str_detect(plt_names, "with") ~ 
        stringr::str_replace(
          plt_names, "with", "DGP with\n"
        ) |> 
        stringr::str_remove(" DGP$"),
      TRUE ~ plt_names
    )[idx]
    tag <- LETTERS[idx]
    plt_df <- plt$data |>
      dplyr::mutate(
        sim_name = sprintf("(%s) %s", tag, sim_name)
      )
    return(plt_df)
  }
) |>
  purrr::list_rbind() |> 
  dplyr::filter(
    depth <= 4
  )
  ggplot2::ggplot() +
  ggplot2::geom_line(
    ggplot2::aes(
      x = depth, y = mean_jaccard, color = .method_name
    )
  ) +
  ggplot2::geom_ribbon(
    ggplot2::aes(
      x = depth,
      ymin = mean_jaccard - se_jaccard,
      ymax = mean_jaccard + se_jaccard,
      fill = .method_name
    ),
    alpha = 0.2
  ) +
  ggplot2::facet_grid(sim_name ~ tau_heritability, labeller = signal_labeller) +
  ggplot2::scale_color_manual(
    breaks = KEEP_METHODS,
    values = COLORS,
    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
  ) +
  ggplot2::scale_fill_manual(
    breaks = KEEP_METHODS,
    values = COLORS,
    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
  ) +
  ggplot2::coord_cartesian(xlim = c(1, 4)) +
  ggplot2::scale_x_continuous(
    breaks = 1:4
  ) +
  ggplot2::labs(
    x = "Tree Depth",
    y = "Mean Jaccard Stability",
    color = "Method",
    fill = "Method"
  ) +
  vthemes::theme_vmodern(
    size_preset = "medium", grid_color = "grey98"
  )
ggplot2::ggsave(
  plt_stability, 
  filename = file.path(FIG_DIR, "sim_stability.pdf"),
  height = 12, 
  width = 11
)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2024-09-10 causalDT-manuscript/R/dgp/dgps.R

@@ -64,6 +64,7 @@ generate_subgroup_dgp <- function(n = 2000,
 
 # Real world data
 rwd_dgp <- function(name, subsample = 1, permute = FALSE) {
+
   if (stringr::str_starts(name, "aids")) {
     data <- speff2trial::ACTG175 |>
       dplyr::filter(arms %in% c(0, 2))
@@ -74,7 +75,7 @@ rwd_dgp <- function(name, subsample = 1, permute = FALSE) {
     vars_all <- c(
       "age", "wtkg", "hemo", "homo", "drugs", "karnof", "race", "gender",
       "symptom", "preanti", "strat", "str2", "oprior", "z30", "zprior",
-      "cd80"#, "cd40"
+      "cd80"
     )
     if (name == "aids_full") {
       X <- data |>
@@ -84,13 +85,6 @@ rwd_dgp <- function(name, subsample = 1, permute = FALSE) {
         dplyr::select(
           tidyselect::all_of(
             setdiff(vars_all, c("str2", "oprior", "z30", "zprior"))
-          )
-        )
-    } else if (name == "aids_strat") {
-      X <- data |>
-        dplyr::select(
-          tidyselect::all_of(
-            setdiff(vars_all, c("str2", "oprior", "z30", "zprior", "preanti"))
           )
         )
     }

### 2024-09-10 causalDT-manuscript/R/dgp/tau-funs.R

@@ -1,3 +1,11 @@
+generate_tau_simple <- function(X, beta = 1) {
+  result <- beta * (X[, 1] > 0)
+  thresholds <- list(
+    X1 = 0
+  )
+  return(list(result = result, thresholds = thresholds))
+}
+
 generate_tau_or <- function(X) {
   result <- 2 * (X[, 1] > 0) - (X[, 2] > 0.5 | X[, 2] < -0.5)
   thresholds <- list(
@@ -22,5 +30,17 @@ generate_tau_and <- function(X) {
     X1 = 0,
     X2 = 0.5
   )
+  return(list(result = result, thresholds = thresholds))
+}
+
+generate_tau_random <- function(X) {
+  result <- rbinom(nrow(X), 1, 0.5)
+  thresholds <- list()
+  return(list(result = result, thresholds = thresholds))
+}
+
+generate_tau_null <- function(X) {
+  result <- rep(0, nrow(X))
+  thresholds <- list()
   return(list(result = result, thresholds = thresholds))
 }

### 2024-09-10 causalDT-manuscript/R/eval/eval-utils.R

@@ -1,0 +1,42 @@
+collapse_dummy_vars <- function(x) {
+  stringr::str_remove(x, "\\.\\..*")
+}
+
+
+get_subgroup_vars <- function(subgroups) {
+  purrr::map(
+    subgroups,
+    function(subgroup) {
+      stringr::str_remove(setdiff(subgroup, "root"), ">.*|<.*") |>
+        collapse_dummy_vars() |>
+        stringr::str_trim()
+    }
+  ) |>
+    purrr::compact()
+}
+
+
+add_best_distilled_method <- function(fit_results,
+                                      vary_params = NULL,
+                                      max_depths = 1:4) {
+  id_cols <- c(".rep", ".dgp_name", ".method_name", vary_params)
+  return(fit_results)
+
+  best_methods_df <- get_best_distilled_method_info(
+    fit_results,
+    vary_params = vary_params,
+    max_depths = max_depths
+  ) |>
+    dplyr::select(-jaccard, -cum_jaccard) |>
+    dplyr::left_join(fit_results, by = id_cols) |>
+    dplyr::mutate(
+      .method_name = "Most Stable Distilled Method"
+    ) |>
+    tidyr::unite(
+      col = ".method_name", .method_name, depth, sep = " Depth "
+    ) |>
+    dplyr::ungroup()
+
+  fit_results <- dplyr::bind_rows(fit_results, best_methods_df)
+  return(fit_results)
+}

### 2024-09-10 causalDT-manuscript/R/eval/evaluators.R

@@ -1,0 +1,287 @@
+eval_subgroup_feature_selection_err <- function(fit_results,
+                                                vary_params = NULL,
+                                                nested_cols = NULL,
+                                                group_cols = NULL,
+                                                na_rm = FALSE,
+                                                summary_funs = c("mean", "median", "min",
+                                                                 "max", "sd", "raw"),
+                                                custom_summary_funs = list(
+                                                  "se_feature_selection_err" =
+                                                    function(x) sd(x) / sqrt(length(x))
+                                                ),
+                                                eval_id = "feature_selection_err") {
+
+  group_vars <- c(
+    ".dgp_name", ".method_name", vary_params, group_cols, ".metric"
+  )
+
+  fit_results <- add_best_distilled_method(
+    fit_results = fit_results,
+    vary_params = vary_params
+  )
+
+  subgroup_feature_selection_err <- function(data) {
+    true_vars <- names(data[["true_thresholds"]][[1]])
+    model_info <- data[["model_info"]][[1]]
+
+    if (is.null(model_info)) {
+      tp <- 0
+      fp <- 0
+      fn <- length(true_vars)
+      f1 <- 0
+    } else {
+      subgroup_vars <- unique(collapse_dummy_vars(model_info$var))
+      tp <- sum(subgroup_vars %in% true_vars)
+      fp <- sum(!(subgroup_vars %in% true_vars))
+      fn <- sum(!(true_vars %in% subgroup_vars))
+      f1 <-  (2 * tp) / (2 * tp + fp + fn)
+    }
+    return(tibble::tibble(F1 = f1, tp = tp, fp = fp, fn = fn))
+  }
+
+  eval_data <- simChef::eval_constructor(
+    fit_results = fit_results, vary_params = vary_params,
+    fun = subgroup_feature_selection_err,
+    nested_cols = nested_cols, group_cols = group_cols, na_rm = na_rm
+  ) |>
+    tidyr::unnest(.eval_result) |>
+    tidyr::pivot_longer(
+      cols = c(F1, tp, fp, fn), names_to = ".metric", values_to = ".estimate"
+    ) |>
+    dplyr::group_by(dplyr::across(tidyselect::any_of(group_vars)))
+
[…]

### 2024-09-10 causalDT-manuscript/R/viz/visualizers.R

@@ -1,0 +1,563 @@
+plot_subgroup_feature_selection_err <- function(fit_results = NULL,
+                                                eval_results,
+                                                vary_params = NULL,
+                                                eval_name = "Subgroup Feature Selection Errors Summary",
+                                                eval_id = "feature_selection_err",
+                                                facet_type = "wrap",
+                                                facet_args = list(
+                                                  nrow = 1,
+                                                  scales = "free_y",
+                                                  strip.position = "left"
+                                                ),
+                                                show = c("point", "line"),
+                                                axis_title_size = 16,
+                                                axis_text_size = 12,
+                                                legend_title_size = 16,
+                                                legend_text_size = 12,
+                                                ...) {
+  eval_results[[eval_name]] <- eval_results[[eval_name]] |>
+    dplyr::mutate(
+      .metric = dplyr::case_when(
+        # .metric == "fn" ~ "False Negatives",
+        .metric == "fp" ~ "# False Positives",
+        .metric == "tp" ~ "# True Positives",
+        TRUE ~ .metric
+      ) |>
+        factor(
+          levels = c("F1", "# True Positives", "# False Positives")
+        )
+    ) |>
+    dplyr::filter(
+      !is.na(.metric)
+    )
+
+  plt <- plot_pred_err(
+    eval_results = eval_results,
+    vary_params = vary_params,
+    eval_name = eval_name,
+    eval_id = eval_id,
+    facet_type = facet_type,
+    facet_args = facet_args,
+    show = show,
+    ...
+  ) +
+    vthemes::theme_vmodern(
+      axis_title_size = axis_title_size,
+      axis_text_size = axis_text_size,
+      legend_title_size = legend_title_size,
+      legend_text_size = legend_text_size
+    ) +
+    ggplot2::theme(
+      strip.background = ggplot2::element_rect(
+        fill = "transparent", color = "transparent"
+      ),
[…]

### 2024-09-10 causalDT-manuscript/R/viz/viz-utiils.R

@@ -1,0 +1,40 @@
+get_best_distilled_method_info <- function(fit_results,
+                                           vary_params = NULL,
+                                           max_depths = 1:4) {
+  id_cols <- c(".rep", ".dgp_name", ".method_name", vary_params)
+
+  best_methods_df <- fit_results |>
+    dplyr::filter(
+      stringr::str_detect(.method_name, "Distilled")
+    ) |>
+    dplyr::mutate(
+      jaccard = purrr::map(
+        stability_diagnostics,
+        ~ tibble::tibble(
+          depth = 1:length(.x$jaccard_mean),
+          jaccard = .x$jaccard_mean
+        )
+      )
+    ) |>
+    dplyr::select(
+      tidyselect::all_of(id_cols), jaccard
+    ) |>
+    tidyr::unnest(jaccard) |>
+    dplyr::filter(depth <= max(!!max_depths)) |>
+    dplyr::group_by(
+      dplyr::across(tidyselect::all_of(id_cols))
+    ) |>
+    dplyr::mutate(
+      cum_jaccard = cumsum(jaccard)
+    ) |>
+    dplyr::filter(depth %in% !!max_depths) |>
+    dplyr::group_by(
+      dplyr::across(
+        tidyselect::all_of(c(".rep", ".dgp_name", vary_params, "depth"))
+      )
+    ) |>
+    dplyr::slice_max(cum_jaccard)
+
+  return(best_methods_df)
+}
+

### 2024-09-10 causalDT-manuscript/meals/01a_and_subgroup.R

@@ -2,18 +2,18 @@ rm(list = ls())
 EXP_NAME <- "Unbiased W"
 N_REPS <- 100
 SAVE <- TRUE
-USE_CACHED <- FALSE
-# USE_CACHED <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
 CHECKPOINT_N_REPS <- 0
 set.seed(331)
 
 source(here::here(file.path("meals", "setup.R")))
 N_REPS <- 100
 
-#### Cluster setup for parallelization (or comment out) ####
-# n_workers <- min(N_REPS, availableCores() - 1)
-n_workers <- 8
-plan(multisession, workers = n_workers)
+# #### Cluster setup for parallelization (or comment out) ####
+# # n_workers <- min(N_REPS, availableCores() - 1)
+# n_workers <- 8
+# plan(multisession, workers = n_workers)
 
 #### DGPs ####
 
@@ -45,6 +45,17 @@ out <- run_experiment(
   use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
+
+fit_results <- get_cached_results(experiment, "fit")
+eval_results <- get_cached_results(experiment, "eval")
+viz_results <- visualize_experiment(experiment, fit_results, eval_results)
+plotly::ggplotly(viz_results$`Subgroup Feature Selection Errors Plot`)
+plotly::ggplotly(viz_results$`Subgroup CATE Errors Plot`)
+viz_results$`Subgroup Thresholds Distribution Plot`
+viz_results$`Number of Splits Plot`
+viz_results$`Number of Trees Plot`
+viz_results$`Subgroup CATEs Plot`
+viz_results$`Subgroup Stability Diagnostics Plot`
 
 render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
 

### 2024-09-10 causalDT-manuscript/meals/01b_or_subgroup.R

@@ -2,19 +2,19 @@ rm(list = ls())
 EXP_NAME <- "Unbiased W"
 N_REPS <- 100
 SAVE <- TRUE
-USE_CACHED <- FALSE
-# USE_CACHED <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
 CHECKPOINT_N_REPS <- 0
 set.seed(331)
 
 source(here::here(file.path("meals", "setup.R")))
 N_REPS <- 100
 
-#### Cluster setup for parallelization (or comment out) ####
-# n_workers <- min(N_REPS, availableCores() - 1)
-n_workers <- 8
-# n_workers <- 2
-plan(multisession, workers = n_workers)
+# #### Cluster setup for parallelization (or comment out) ####
+# # n_workers <- min(N_REPS, availableCores() - 1)
+# n_workers <- 8
+# # n_workers <- 2
+# plan(multisession, workers = n_workers)
 
 #### DGPs ####
 
@@ -46,6 +46,17 @@ out <- run_experiment(
   use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
+
+# fit_results <- get_cached_results(experiment, "fit")
+# eval_results <- get_cached_results(experiment, "eval")
+# viz_results <- visualize_experiment(experiment, fit_results, eval_results)
+# plotly::ggplotly(viz_results$`Subgroup Feature Selection Errors Plot`)
+# plotly::ggplotly(viz_results$`Subgroup CATE Errors Plot`)
+# viz_results$`Subgroup Thresholds Distribution Plot`
+# viz_results$`Number of Splits Plot`
+# viz_results$`Number of Trees Plot`
+# viz_results$`Subgroup CATEs Plot`
+# viz_results$`Subgroup Stability Diagnostics Plot`
 
 render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
 

### 2024-09-10 causalDT-manuscript/meals/01d_and_subgroup_cov.R

@@ -2,19 +2,19 @@ rm(list = ls())
 EXP_NAME <- "Unbiased W"
 N_REPS <- 100
 SAVE <- TRUE
-USE_CACHED <- FALSE
-# USE_CACHED <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
 CHECKPOINT_N_REPS <- 0
 set.seed(331)
 
 source(here::here(file.path("meals", "setup.R")))
 N_REPS <- 100
 
-#### Cluster setup for parallelization (or comment out) ####
-# n_workers <- min(N_REPS, availableCores() - 1)
-n_workers <- 8
-# n_workers <- 2
-plan(multisession, workers = n_workers)
+# #### Cluster setup for parallelization (or comment out) ####
+# # n_workers <- min(N_REPS, availableCores() - 1)
+# n_workers <- 8
+# # n_workers <- 2
+# plan(multisession, workers = n_workers)
 
 #### DGPs ####
 
@@ -46,6 +46,17 @@ out <- run_experiment(
   use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
+
+fit_results <- get_cached_results(experiment, "fit")
+eval_results <- get_cached_results(experiment, "eval")
+viz_results <- visualize_experiment(experiment, fit_results, eval_results)
+plotly::ggplotly(viz_results$`Subgroup Feature Selection Errors Plot`)
+plotly::ggplotly(viz_results$`Subgroup CATE Errors Plot`)
+viz_results$`Subgroup Thresholds Distribution Plot`
+viz_results$`Number of Splits Plot`
+viz_results$`Number of Trees Plot`
+viz_results$`Subgroup CATEs Plot`
+viz_results$`Subgroup Stability Diagnostics Plot`
 
 render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
 

### 2024-09-10 causalDT-manuscript/meals/05_case_study_aids.R

@@ -1,0 +1,143 @@
+rm(list = ls())
+EXP_NAME <- "AIDS"
+N_REPS <- 100
+SAVE <- TRUE
+USE_CACHED <- FALSE
+# USE_CACHED <- TRUE
+CHECKPOINT_N_REPS <- 0
+set.seed(331)
+
+source(here::here(file.path("meals", "setup.R")))
+N_REPS <- 100
+
+# #### Cluster setup for parallelization (or comment out) ####
+# # n_workers <- min(N_REPS, availableCores() - 1)
+# n_workers <- 8
+# plan(multisession, workers = n_workers)
+
+#### DGPs ####
+
+source(here::here(file.path("meals", "shared_dgps.R")))
+
+#### Methods ####
+
+source(here::here(file.path("meals", "shared_methods.R")))
+
+#### Evaluators and Visualizers ####
+
+source(here::here(file.path("meals", "shared_evaluators.R")))
+source(here::here(file.path("meals", "shared_visualizers.R")))
+
+#### Run Experiment ####
+dgp <- aids_dgp
+print(dgp$name)
+
+source(here::here(file.path("meals", "shared_experiments.R")))
+rwd_experiment <- rwd_experiment |>
+  add_dgp(dgp) #|>
+  # add_vary_across(
+  #   .dgp = dgp$name,
+  #   subsample = c(100, 200, 300, 400, 500, 600, 792) / 792
+  # )
+# out <- run_experiment(rwd_experiment)
+out <- run_experiment(
+  rwd_experiment, n_reps = N_REPS, save = SAVE,
+  use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
+  future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
+)
+
+keep_methods <- c(
+  "Causal Tree (pruned)",
+  "Causal Tree (unpruned)",
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Distilled Rlasso",
+  "Lasso",
+  "Linear Regression",
+  "Virtual Twins"
+)
+fit_results <- get_cached_results(rwd_experiment, "fit") |>
+  dplyr::filter(
+    .method_name %in% !!keep_methods
+  )
+# eval_results <- get_cached_results(rwd_experiment, "eval")
+eval_results <- evaluate_experiment(rwd_experiment, fit_results)
+# eval_results <- evaluate_experiment(rwd_experiment, fit_results, save = TRUE)
[…]

### 2024-09-10 causalDT-manuscript/meals/shared_dgps.R

@@ -66,3 +66,43 @@ gaussian_X_unbiased_Z_additive_cov <- create_dgp(
   beta = c(0, 0, 1, 1, 0, 0, 0, 0, 0, 0),
   y_err_sd = 0.1
 )
+
+gaussian_X_unbiased_Z_null <- create_dgp(
+  .dgp_fun = generate_subgroup_dgp,
+  .name = "No Subgroup DGP",
+  n = 500, p = 10,
+  X_fun = generate_gaussian_X,
+  Z_fun = generate_unbiased_Z,
+  tau_fun = generate_tau_null,
+  tau_err_sd = 0.2,
+  y_err_sd = 0.1
+)
+
+theory_p1_gaussian_X_unbiased_Z_tau <- create_dgp(
+  .dgp_fun = generate_subgroup_dgp,
+  .name = "Theory Sim (p = 1)",
+  n = 500, p = 1,
+  X_fun = generate_gaussian_X,
+  Z_fun = generate_unbiased_Z,
+  tau_fun = generate_tau_simple,
+  tau_heritability = 0.2,
+  y_err_sd = 0.1
+)
+
+theory_p10_gaussian_X_unbiased_Z_tau <- create_dgp(
+  .dgp_fun = generate_subgroup_dgp,
+  .name = "Theory Sim (p = 10)",
+  n = 500, p = 10,
+  X_fun = generate_gaussian_X,
+  Z_fun = generate_unbiased_Z,
+  tau_fun = generate_tau_simple,
+  tau_heritability = 0.2,
+  y_err_sd = 0.1
+)
+
+aids_dgp <- create_dgp(
+  .dgp_fun = rwd_dgp,
+  .name = "AIDS DGP",
+  name = "aids_small",
+  subsample = 0.75
+)

### 2024-09-10 causalDT-manuscript/meals/shared_evaluators.R

@@ -1,0 +1,44 @@
+#### Subgroup Feature Selection Evaluators ####
+subgroup_feature_selection_errors_summary <- create_evaluator(
+  .eval_fun = eval_subgroup_feature_selection_err,
+  .name = "Subgroup Feature Selection Errors Summary"
+)
+
+subgroup_feature_selection_errors_eval <- create_evaluator(
+  .eval_fun = eval_subgroup_feature_selection_err,
+  .name = "Subgroup Feature Selection Errors",
+  summary_funs = NULL
+)
+
+#### Subgroup Threshold Evaluators ####
+subgroup_thresholds_summary <- create_evaluator(
+  .eval_fun = eval_subgroup_thresholds,
+  .name = "Thresholds Summary"
+)
+
+subgroup_thresholds_eval <- create_evaluator(
+  .eval_fun = eval_subgroup_thresholds,
+  .name = "Thresholds",
+  summary_funs = NULL
+)
+
+#### Subgroup CATE Evaluators ####
+subgroup_cate_err_summary <- create_evaluator(
+  .eval_fun = eval_subgroup_cate_err,
+  .name = "Subgroup CATE Errors Summary",
+  custom_summary_funs = list(
+    "se_cate_err" = function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))
+  )
+)
+
+subgroup_cate_err_eval <- create_evaluator(
+  .eval_fun = eval_subgroup_cate_err,
+  .name = "Subgroup CATE Errors",
+  summary_funs = NULL
+)
+
+#### Stability Diagnostic Evaluators ####
+subgroup_stability_eval <- create_evaluator(
+  .eval_fun = eval_stability_diagnostics,
+  .name = "Subgroup Stability Diagnostics"
+)

### 2024-09-10 causalDT-manuscript/meals/shared_experiments.R

@@ -4,11 +4,79 @@ experiment <- create_experiment(
   ### distillation methods
   add_method(distilled_causal_forest_stability_method) |>
   add_method(distilled_rboost_stability_method) |>
+  add_method(distilled_rboost_no_crossfit_stability_method) |>
   add_method(distilled_rlasso_stability_method) |>
+  add_method(distilled_rlasso_no_crossfit_stability_method) |>
   ### baseline causal tree methods
   add_method(causal_tree_stability_method) |>
   add_method(causal_tree_unpruned_stability_method) |>
   ### other existing methods
   add_method(virtual_twins_method) |>
   add_method(lm_method) |>
-  add_method(lasso_method)
+  add_method(lasso_method) |>
+  ### evaluators
+  add_evaluator(subgroup_feature_selection_errors_summary) |>
+  add_evaluator(subgroup_thresholds_summary) |>
+  add_evaluator(subgroup_cate_err_summary) |>
+  ### visualizers
+  add_visualizer(subgroup_feature_selection_err_plot) |>
+  add_visualizer(subgroup_thresholds_plot) |>
+  add_visualizer(subgroup_nsplits_plot) |>
+  add_visualizer(subgroup_ntrees_plot) |>
+  add_visualizer(subgroup_cates_plot) |>
+  add_visualizer(subgroup_cates_err_plot) |>
+  add_visualizer(subgroup_stability_plot)
+
+crossfit_experiment <- create_experiment(
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
+) |>
+  ### distillation methods without crossfit
+  add_method(distilled_causal_forest_no_crossfit_method) |>
+  add_method(distilled_rboost_no_crossfit_method) |>
+  add_method(distilled_rlasso_no_crossfit_method) |>
+  ### distillation methods with crossfitting
+  add_method(distilled_causal_forest_crossfit_method) |>
+  add_method(distilled_rboost_crossfit_method) |>
+  add_method(distilled_rlasso_crossfit_method) |>
+  add_vary_across(
+    .method = c(
+      distilled_causal_forest_crossfit_method$name,
+      distilled_rboost_crossfit_method$name,
+      distilled_rlasso_crossfit_method$name
+    ),
+    nreps_crossfit = c(1, 5, 10, 20, 50, 100)
+  )
+
+rwd_experiment <- create_experiment(
[…]

### 2024-09-10 causalDT-manuscript/meals/shared_methods.R

@@ -1,4 +1,4 @@
-### Distillation methods ####
+### Main Distillation Methods ####
 NREPS_CROSSFIT <- 50
 
 # without stability diagnostics
@@ -42,7 +42,25 @@ distilled_rlasso_stability_method <- create_method(
   B_stability = 100
 )
 
-#### Causal tree methods ####
+distilled_rboost_no_crossfit_stability_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Rboost (no crossfit)",
+  teacher_model = causalDT::rboost,
+  B_stability = 100,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1
+)
+
+distilled_rlasso_no_crossfit_stability_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Rlasso (no crossfit)",
+  teacher_model = causalDT::rlasso,
+  B_stability = 100,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1
+)
+
+#### Causal Tree Methods ####
 causal_tree_method <- create_method(
   .method_fun = causal_tree,
   .name = "Causal Tree (pruned)"
@@ -81,4 +99,79 @@ lm_method <- create_method(
 lasso_method <- create_method(
   .method_fun = lasso_reg_subgroups,
   .name = "Lasso"
+)
+
+#### Distillation Methods with varying # crossfits ####
+distilled_causal_forest_no_crossfit_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (no crossfit)",
+  teacher_model = "causal_forest",
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1
+)
+
+distilled_rboost_no_crossfit_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Rboost (no crossfit)",
+  teacher_model = causalDT::rboost,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1
+)
+
+distilled_rlasso_no_crossfit_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Rlasso (no crossfit)",
+  teacher_model = causalDT::rlasso,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1
+)
+
+
+distilled_causal_forest_crossfit_method <- create_method(
+  .method_fun = causalDT_method,
[…]

### 2024-09-10 causalDT-manuscript/meals/shared_visualizers.R

@@ -1,0 +1,65 @@
+subgroup_feature_selection_err_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_feature_selection_err,
+  .name = "Subgroup Feature Selection Errors Plot",
+  show = c("point", "line", "ribbon"),
+  err_sd_str = "se_feature_selection_err",
+  ribbon_args = list(
+    alpha = 0.2
+  ),
+  line_args = list(
+    size = 0.7
+  )
+)
+
+subgroup_thresholds_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_thresholds,
+  .name = "Subgroup Thresholds Distribution Plot",
+  size_preset = "medium"
+)
+
+subgroup_thresholds_errorbar_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_thresholds,
+  .name = "Subgroup Thresholds Distribution Plot (errorbar)",
+  show = c("point", "errorbar"),
+  size_preset = "medium"
+)
+
+subgroup_nsplits_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_nsplits,
+  .name = "Number of Splits Plot",
+  type = "n_splits_per_tree",
+  size_preset = "medium"
+)
+
+subgroup_ntrees_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_nsplits,
+  .name = "Number of Trees Plot",
+  type = "n_trees",
+  size_preset = "medium"
+)
+
+subgroup_cates_plot <- create_visualizer(
+  .viz_fun = plot_subgroup_cates,
+  .name = "Subgroup CATEs Plot"
+)
+
+subgroup_cates_err_plot <- create_visualizer(
+  .viz_fun = plot_pred_err,
+  .name = "Subgroup CATE Errors Plot",
+  eval_name = "Subgroup CATE Errors Summary",
+  eval_id = "cate_err",
+  show = c("point", "line", "ribbon"),
+  metrics = yardstick::metric_set(yardstick::rmse),
+  err_sd_str = "se_cate_err",
+  ribbon_args = list(
+    alpha = 0.2
+  ),
+  line_args = list(
+    size = 0.7
+  )
+)
+
+subgroup_stability_plot <- create_visualizer(
+  .viz_fun = plot_stability_diagnostics,
+  .name = "Subgroup Stability Diagnostics Plot"
+)

### 2024-09-10 causalDT-manuscript/R/eval/evaluators.R
bug fix and add feature stability to diagnostics

@@ -90,7 +90,7 @@ eval_subgroup_thresholds <- function(fit_results,
 
   subgroup_thresholds <- function(data) {
     model_info <- data[["model_info"]][[1]]
-    if (length(purrr::flatten(data[["true_thresholds"]])) == 1) {
+    if (length(unlist(data[["true_thresholds"]])) == 1) {
       true_vars <- names(data[["true_thresholds"]])
     } else {
       true_vars <- names(data[["true_thresholds"]][[1]])

### 2024-09-10 causalDT/R/diagnostics-stability.R

@@ -159,10 +159,24 @@ evaluate_subgroup_stability <- function(estimator, fit, X, y, Z = NULL,
       apply(1, var)
   }
 
+  feature_dist <- purrr::map(
+    bootstrap_fits, ~ get_party_node_depths(.x, return_features = TRUE)
+  ) |>
+    dplyr::bind_rows(.id = "bootstrap_idx") |>
+    dplyr::filter(
+      !is.na(feature)
+    ) |>
+    dplyr::group_by(depth, feature) |>
+    dplyr::summarise(
+      freq = dplyr::n()
+    ) |>
+    dplyr::ungroup()
+
   leaf_ids_orig <- predict(fit_orig, data.frame(X), type = "node")
   out <- list(
     "jaccard_mean" = sapply(Js, mean),
     "jaccard_distribution" = Js,
+    "feature_distribution" = feature_dist,
     "bootstrap_predictions_mean" = preds_mean,
     "bootstrap_predictions_var" = preds_var,
     "leaf_ids" = leaf_ids_orig

### 2024-09-10 causalDT/R/utils-student.R

@@ -211,16 +211,34 @@ get_party_paths <- function(party_fit) {
 #' @inheritParams shared_args
 #'
 #' @keywords internal
-get_party_node_depths <- function(party_fit) {
+get_party_node_depths <- function(party_fit, return_features = FALSE) {
   printed_tree <- capture.output(party_fit)
   id_counter <- 1
   depths <- rep(NA, length(party_fit))
   names(depths) <- 1:length(party_fit)
+  features <- rep(NA, length(party_fit))
+  names(features) <- 1:length(party_fit)
   for (idx in seq_along(printed_tree)) {
     if (grepl("\\[[0-9]+\\]", printed_tree[idx])) {
       depths[id_counter] <- stringr::str_count(printed_tree[idx], "\\|")
+      if (return_features) {
+        features[id_counter] <- stringr::str_extract(
+          printed_tree[idx],
+          "(?<=\\]).*?(?=<|>)"
+        ) |>
+          stringr::str_trim()
+      }
       id_counter <- id_counter + 1
     }
   }
-  return(depths)
+  if (return_features) {
+    return(
+      tibble::tibble(
+        depth = depths,
+        feature = features
+      )
+    )
+  } else {
+    return(depths)
+  }
 }

### 2024-09-10 causalDT/R/utils-student.R
update R package docs

@@ -209,6 +209,8 @@ get_party_paths <- function(party_fit) {
 #' Get depth of each node in a party model.
 #'
 #' @inheritParams shared_args
+#' @param return_features Logical indicating whether to return the feature
+#'   associated with each node.
 #'
 #' @keywords internal
 get_party_node_depths <- function(party_fit, return_features = FALSE) {

### 2024-09-10 causalDT-manuscript/R/method/methods.R
add CATE for linear methods

@@ -272,14 +272,31 @@ linear_reg_subgroups <- function(X, Y, Z, max_int = 1,
 
   # Step 1: Fit a linear regression
   df <- data.frame(X, Z, Y)
+  df1 <- df |>
+    dplyr::mutate(Z = 1)
+  df0 <- df |>
+    dplyr::mutate(Z = 0)
   formula <- get_interaction_formula(df, max_int)
   fit <- lm(formula, data = df)
-  tauhat <- predict(fit)
+  tauhat <- predict(fit, df1) - predict(fit, df0)
 
   # Step 2: Extract subgroups from linear regression
   tidy_fit <- tidy_lm(fit)
   model_info <- get_lm_info(tidy_fit)
   subgroups <- get_lm_subgroups(tidy_fit)
+
+  # evaluate CATE
+  group_cates <- tibble::tibble(
+    estimate = tauhat,
+    Z = Z
+  ) |>
+    dplyr::group_by(estimate) |>
+    dplyr::summarise(
+      .n1 = sum(Z == 1),
+      .n0 = sum(Z == 0),
+      .sample_idxs = list(dplyr::cur_group_rows()),
+      .groups = "drop"
+    )
   end_time <- Sys.time()
 
   out <- c(
@@ -287,6 +304,7 @@ linear_reg_subgroups <- function(X, Y, Z, max_int = 1,
       fit = fit,
       model_info = model_info,
       subgroups = subgroups,
+      group_cates = group_cates,
       teacher_predictions = tauhat,
       student_predictions = rep(NA_real_, length(tauhat)),  # dummy placeholder for now
       time_elapsed = as.numeric(difftime(end_time, start_time, units = "secs")),
@@ -307,18 +325,37 @@ lasso_reg_subgroups <- function(X, Y, Z, max_int = 1,
 
   # Step 1: Fit Lasso
   df <- data.frame(X, Z, Y)
+  df1 <- df |>
+    dplyr::mutate(Z = 1)
+  df0 <- df |>
+    dplyr::mutate(Z = 0)
   formula <- get_interaction_formula(df, max_int)
   Xmat <- model.matrix(formula, df)[, -1] # remove intercept
+  Xmat1 <- model.matrix(formula, df1)[, -1]
+  Xmat0 <- model.matrix(formula, df0)[, -1]
   fit <- do.call(
     glmnet::cv.glmnet,
[…]

### 2024-09-10 causalDT-manuscript/notebooks/paper_figures.Rmd
adjust heatmap color palette

@@
     viridis::scale_fill_viridis(
-      begin = 0.15, end = 0.95, option = "magma", limits = c(0., 7)
+      begin = 0.05, end = 1, option = "magma", limits = c(0., 7)
     )
@@
     viridis::scale_fill_viridis(
-      begin = 0.15, end = 0.95, option = "magma", limits = c(0, 100)
+      begin = 0.05, end = 1, option = "magma", limits = c(0, 100)
     )
@@
 ```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2024-09-10 causalDT-manuscript/R/method/methods.R
bug fix in lasso CATE

@@ -363,6 +363,7 @@ lasso_reg_subgroups <- function(X, Y, Z, max_int = 1,
       fit = fit,
       model_info = model_info,
       subgroups = subgroups,
+      group_cates = group_cates,
       teacher_predictions = tauhat,
       student_predictions = rep(NA_real_, length(tauhat)),  # dummy placeholder for now
       time_elapsed = as.numeric(difftime(end_time, start_time, units = "secs")),

### 2024-12-03 causalDT/R/causalDT.R
update causalDT docs

@@ -17,6 +17,13 @@
 #'   largest complexity threshold which yields a cross-vaidation error within
 #'   one standard error of the minimum. If \code{"none"}, the tree is not
 #'   pruned.
+#' @param rpart_prune Method for pruning the tree. Default is \code{"none"}.
+#'   Options are \code{"none"}, \code{"min"}, and \code{"1se"}. If \code{"min"},
+#'   the tree is pruned using the complexity threshold which minimizes the
+#'   cross-validation error. If \code{"1se"}, the tree is pruned using the
+#'   largest complexity threshold which yields a cross-vaidation error within
+#'   one standard error of the minimum. If \code{"none"}, the tree is not
+#'   pruned.
 #'
 #' @keywords internal
 NULL
@@ -141,6 +148,8 @@ causalDT <- function(X, Y, Z,
                      B_stability = 100,
                      max_depth_stability = NULL,
                      ...) {
+
+  rpart_prune <- match.arg(rpart_prune)
 
   # initialize output and helper variables
   n <- nrow(X)

### 2024-12-03 causalDT-manuscript/R/eval/evaluators.R
add pruning to simulations

@@ -16,10 +16,7 @@ eval_subgroup_feature_selection_err <- function(fit_results,
     ".dgp_name", ".method_name", vary_params, group_cols, ".metric"
   )
 
-  fit_results <- add_best_distilled_method(
-    fit_results = fit_results,
-    vary_params = vary_params
-  )
+  fit_results <- unnest_fit_results(fit_results = fit_results)
 
   subgroup_feature_selection_err <- function(data) {
     true_vars <- names(data[["true_thresholds"]][[1]])
@@ -27,9 +24,6 @@ eval_subgroup_feature_selection_err <- function(fit_results,
     nsubgroups <- length(data[["subgroups"]][[1]])
     if (("node" %in% colnames(model_info)) && !is.null(max_depth)) {
       model_info <- model_info |>
-        dplyr::mutate(
-          depth = trunc(log(node, base = 2)) + 1
-        ) |>
         dplyr::filter(
           depth <= !!max_depth
         )
@@ -103,20 +97,13 @@ eval_subgroup_thresholds <- function(fit_results,
     ".dgp_name", ".method_name", vary_params, group_cols,
     ".var", "categorical", "true_var"
   )
-  nreps <- length(unique(fit_results$.rep))
 
-  fit_results <- add_best_distilled_method(
-    fit_results = fit_results,
-    vary_params = vary_params
-  )
+  fit_results <- unnest_fit_results(fit_results = fit_results)
 
   subgroup_thresholds <- function(data) {
     model_info <- data[["model_info"]][[1]]
     if (("node" %in% colnames(model_info)) && !is.null(max_depth)) {
       model_info <- model_info |>
-        dplyr::mutate(
-          depth = trunc(log(node, base = 2)) + 1
-        ) |>
         dplyr::filter(
           depth <= !!max_depth
         )
@@ -239,20 +226,13 @@ eval_subgroup_threshold_dist <- function(fit_results,
   group_vars <- c(
     ".dgp_name", ".method_name", vary_params, group_cols, ".var", ".metric"
   )
-  nreps <- length(unique(fit_results$.rep))
 
-  fit_results <- add_best_distilled_method(
-    fit_results = fit_results,
-    vary_params = vary_params
-  )
+  fit_results <- unnest_fit_results(fit_results = fit_results)
 
   subgroup_thresholds <- function(data) {
     model_info <- data[["model_info"]][[1]]
[…]

### 2024-12-03 causalDT-manuscript/R/method/method-utils.R

@@ -167,7 +167,7 @@ add_pruned_fits <- function(fit_results,
     dplyr::rowwise() |>
     dplyr::mutate(
       .method_name = paste0(.method_name, " (min-pruned)"),
-      pruned_results = list(prune_tree(fit, prune = "min"))
+      pruned_results = list(prune_tree(fit[[1]], prune = "min"))
     ) |>
     dplyr::select(tidyselect::all_of(keep_cols), pruned_results) |>
     tidyr::unnest(pruned_results, keep_empty = TRUE) |>
@@ -180,7 +180,7 @@ add_pruned_fits <- function(fit_results,
     dplyr::rowwise() |>
     dplyr::mutate(
       .method_name = paste0(.method_name, " (1se-pruned)"),
-      pruned_results = list(prune_tree(fit, prune = "1se"))
+      pruned_results = list(prune_tree(fit[[1]], prune = "1se"))
     ) |>
     dplyr::select(tidyselect::all_of(keep_cols), pruned_results) |>
     tidyr::unnest(pruned_results, keep_empty = TRUE) |>
@@ -194,27 +194,66 @@ add_pruned_fits <- function(fit_results,
 }
 
 
-add_best_distilled_method <- function(fit_results,
-                                      vary_params = NULL,
-                                      max_depths = 1:4) {
-  id_cols <- c(".rep", ".dgp_name", ".method_name", vary_params)
-  return(fit_results)
-
-  best_methods_df <- get_best_distilled_method_info(
-    fit_results,
-    vary_params = vary_params,
-    max_depths = max_depths
-  ) |>
-    dplyr::select(-jaccard, -cum_jaccard) |>
-    dplyr::left_join(fit_results, by = id_cols) |>
+unnest_fit_results <- function(fit_results) {
+  is_nested <- sapply(
+    fit_results$fit,
+    function(x) any(c("none", "min", "1se") %in% names(x))
+  )
+  if (!any(is_nested)) {
+    return(fit_results)
+  }
+  nontree_fit_results <- fit_results |>
+    dplyr::filter(
+      !stringr::str_detect(.method_name, "Distilled") &
+        !stringr::str_detect(.method_name, "Causal Tree")
+    )
+  tree_fit_results <- fit_results |>
+    dplyr::filter(
+      stringr::str_detect(.method_name, "Distilled") |
+        stringr::str_detect(.method_name, "Causal Tree")
+    ) |>
     dplyr::mutate(
[…]

### 2024-12-03 causalDT-manuscript/R/method/methods.R

@@ -5,6 +5,7 @@ causalDT_method <- function(X, Y, Z,
                             teacher_predict = NULL,
                             student_model = "rpart",
                             rpart_control = NULL,
+                            rpart_prune = c("none", "min", "1se"),
                             nfolds_crossfit = NULL,
                             nreps_crossfit = NULL,
                             B_stability = 0,
@@ -13,6 +14,13 @@ causalDT_method <- function(X, Y, Z,
                             return_details = FALSE,
                             return_permuted_results = FALSE,
                             ...) {
+
+  rpart_prune <- match.arg(rpart_prune, several.ok = TRUE)
+  if (length(rpart_prune) > 1) {
+    rpart_prune0 <- "none"
+  } else {
+    rpart_prune0 <- rpart_prune
+  }
 
   start_time <- Sys.time()
   X_dummy <- dummy_code(X)
@@ -29,6 +37,7 @@ causalDT_method <- function(X, Y, Z,
         teacher_predict = teacher_predict,
         student_model = student_model,
         rpart_control = rpart_control,
+        rpart_prune = rpart_prune0,
         nfolds_crossfit = nfolds_crossfit,
         nreps_crossfit = nreps_crossfit,
         B_stability = B_stability,
@@ -37,6 +46,50 @@ causalDT_method <- function(X, Y, Z,
       causalDT_args
     )
   )
+
+  X_est <- X_dummy[results$holdout_idxs, , drop = FALSE]
+  Y_est <- Y[results$holdout_idxs]
+  Z_est <- Z[results$holdout_idxs]
+
+  fit_ls <- list()
+  predictions_ls <- list()
+  group_cates_ls <- list()
+  tree_info_ls <- list()
+  subgroups_ls <- list()
+  if ((length(rpart_prune) > 1) && (identical(student_model, "rpart"))) {
+    for (rpart_prune_mode in rpart_prune) {
+      fit <- results$student_fit$fit
+      if (is.null(fit)) {
+        return(NULL)
+      } else if (rpart_prune_mode != "none") {
+        best_cp <- as.data.frame(fit$cptable) |>
+          dplyr::filter(xerror == min(xerror, na.rm = TRUE)) |>
+          dplyr::slice(1)
+        if (rpart_prune_mode == "min") {
[…]

### 2024-12-03 causalDT-manuscript/R/viz/visualizers.R

@@ -85,6 +85,7 @@ plot_subgroup_thresholds <- function(fit_results = NULL,
                                      eval_name = "Thresholds Summary",
                                      feature_col = ".var",
                                      rm_methods = c("Linear Regression", "Lasso"),
+                                     method_levels = NULL,
                                      show = c("violin", "boxplot"),
                                      show_true_vars_only = TRUE,
                                      show_true_threshold = TRUE,
@@ -98,22 +99,15 @@ plot_subgroup_thresholds <- function(fit_results = NULL,
     eval_results[[eval_name]] <- eval_results[[eval_name]] |>
       dplyr::filter(true_var)
   }
+  if (is.null(method_levels)) {
+    method_levels <- unique(eval_results[[eval_name]]$.method_name)
+  }
 
   plt_df <- eval_results[[eval_name]] |>
     tidyr::unnest_longer(raw_threshold) |>
     dplyr::mutate(
       .method_name = factor(
-        .method_name,
-        levels = c(
-          "Distilled Causal Forest",
-          "Distilled Rboost",
-          "Distilled Rlasso",
-          "Virtual Twins",
-          "Causal Tree (pruned)",
-          "Causal Tree (unpruned)",
-          "Linear Regression",
-          "Lasso"
-        )
+        .method_name, levels = method_levels
       )
     )
 
@@ -267,6 +261,7 @@ plot_subgroup_nsplits <- function(fit_results = NULL,
                                   vary_params = NULL,
                                   eval_name = "Thresholds Summary",
                                   rm_methods = NULL,
+                                  method_levels = NULL,
                                   type = c("n_splits_per_tree", "n_trees"),
                                   ...) {
 
@@ -277,6 +272,9 @@ plot_subgroup_nsplits <- function(fit_results = NULL,
   if (!is.null(rm_methods)) {
     eval_results[[eval_name]] <- eval_results[[eval_name]] |>
       dplyr::filter(!(.method_name %in% !!rm_methods))
+  }
+  if (is.null(method_levels)) {
+    method_levels <- unique(eval_results[[eval_name]]$.method_name)
   }
 
   plt_df <- eval_results[[eval_name]] |>
@@ -297,19 +295,7 @@ plot_subgroup_nsplits <- function(fit_results = NULL,
[…]

### 2024-12-03 causalDT-manuscript/meals/shared_evaluators.R

@@ -86,6 +86,15 @@ subgroup_cate_err_summary <- create_evaluator(
   )
 )
 
+subgroup_cate_err_max_depth2_summary <- create_evaluator(
+  .eval_fun = eval_subgroup_cate_err,
+  .name = "Subgroup CATE Errors Summary (max depth = 2)",
+  max_depth = 2,
+  custom_summary_funs = list(
+    "se_cate_err" = function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))
+  )
+)
+
 subgroup_cate_err_eval <- create_evaluator(
   .eval_fun = eval_subgroup_cate_err,
   .name = "Subgroup CATE Errors",
@@ -93,7 +102,7 @@ subgroup_cate_err_eval <- create_evaluator(
 )
 
 #### Stability Diagnostic Evaluators ####
-subgroup_stability_eval <- create_evaluator(
-  .eval_fun = eval_stability_diagnostics,
-  .name = "Subgroup Stability Diagnostics"
-)
+# subgroup_stability_eval <- create_evaluator(
+#   .eval_fun = eval_stability_diagnostics,
+#   .name = "Subgroup Stability Diagnostics"
+# )

### 2024-12-03 causalDT-manuscript/meals/shared_experiments.R

@@ -2,6 +2,44 @@ experiment <- create_experiment(
   name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods
+  add_method(distilled_causal_forest_stability_pruned_method) |>
+  add_method(distilled_rboost_stability_pruned_method) |>
+  # add_method(distilled_rlasso_stability_pruned_method) |>
+  ### baseline causal tree methods
+  add_method(causal_tree_stability_pruned_method) |>
+  ### other existing methods
+  add_method(virtual_twins_method) |>
+  add_method(lm_method) |>
+  add_method(lasso_method) |>
+  ### evaluators
+  add_evaluator(subgroup_feature_selection_errors_summary) |>
+  add_evaluator(subgroup_feature_selection_errors_max_depth2_summary) |>
+  add_evaluator(subgroup_thresholds_summary) |>
+  add_evaluator(subgroup_thresholds_max_depth2_summary) |>
+  add_evaluator(subgroup_threshold_dist_summary) |>
+  add_evaluator(subgroup_threshold_dist_max_depth2_summary) |>
+  add_evaluator(subgroup_cate_err_summary) |>
+  add_evaluator(subgroup_cate_err_max_depth2_summary) |>
+  ### visualizers
+  add_visualizer(subgroup_feature_selection_err_plot) |>
+  add_visualizer(subgroup_feature_selection_err_max_depth2_plot) |>
+  add_visualizer(subgroup_thresholds_plot) |>
+  add_visualizer(subgroup_thresholds_max_depth2_plot) |>
+  add_visualizer(subgroup_threshold_dist_plot) |>
+  add_visualizer(subgroup_threshold_dist_max_depth2_plot) |>
+  add_visualizer(subgroup_nsplits_plot) |>
+  add_visualizer(subgroup_nsplits_max_depth2_plot) |>
+  add_visualizer(subgroup_ntrees_plot) |>
+  add_visualizer(subgroup_ntrees_max_depth2_plot) |>
+  # add_visualizer(subgroup_cates_plot) |>
+  add_visualizer(subgroup_cates_err_plot) |>
+  add_visualizer(subgroup_cates_err_max_depth2_plot) |>
+  add_visualizer(subgroup_stability_plot)
+
+old_experiment <- create_experiment(
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
+) |>
+  ### distillation methods
[…]

### 2024-12-03 causalDT-manuscript/meals/shared_methods.R

@@ -5,19 +5,22 @@ NREPS_CROSSFIT <- 50
 distilled_causal_forest_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Causal Forest",
-  teacher_model = "causal_forest"
+  teacher_model = "causal_forest",
+  rpart_prune = "min"
 )
 
 distilled_rboost_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Rboost",
-  teacher_model = causalDT::rboost
+  teacher_model = causalDT::rboost,
+  rpart_prune = "min"
 )
 
 distilled_rlasso_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Rlasso",
-  teacher_model = causalDT::rlasso
+  teacher_model = causalDT::rlasso,
+  rpart_prune = "min"
 )
 
 # with stability diagnostics
@@ -25,21 +28,24 @@ distilled_causal_forest_stability_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Causal Forest",
   teacher_model = "causal_forest",
-  B_stability = 100
+  B_stability = 100,
+  rpart_prune = "min"
 )
 
 distilled_rboost_stability_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Rboost",
   teacher_model = causalDT::rboost,
-  B_stability = 100
+  B_stability = 100,
+  rpart_prune = "min"
 )
 
 distilled_rlasso_stability_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Rlasso",
   teacher_model = causalDT::rlasso,
-  B_stability = 100
+  B_stability = 100,
+  rpart_prune = "min"
 )
 
 distilled_rboost_no_crossfit_stability_method <- create_method(
@@ -48,7 +54,8 @@ distilled_rboost_no_crossfit_stability_method <- create_method(
   teacher_model = causalDT::rboost,
   B_stability = 100,
   nfolds_crossfit = 1,
-  nreps_crossfit = 1
+  nreps_crossfit = 1,
+  rpart_prune = "min"
 )
 
 distilled_rlasso_no_crossfit_stability_method <- create_method(
@@ -57,37 +64,105 @@ distilled_rlasso_no_crossfit_stability_method <- create_method(
   teacher_model = causalDT::rlasso,
   B_stability = 100,
[…]

### 2024-12-03 causalDT-manuscript/meals/shared_visualizers.R

@@ -1,3 +1,17 @@
+method_levels <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Distilled Rlasso",
+  "Distilled Rlasso (unpruned)",
+  "Virtual Twins",
+  "Causal Tree",
+  "Causal Tree (unpruned)",
+  "Linear Regression",
+  "Lasso"
+)
+
 num_subgroups_plot <- create_visualizer(
   .viz_fun = plot_subgroup_feature_selection_err,
   .name = "Number of Subgroups Plot",
@@ -8,7 +22,7 @@ num_subgroups_plot <- create_visualizer(
     alpha = 0.2
   ),
   line_args = list(
-    size = 0.7
+    size = 1.1
   )
 )
 
@@ -68,6 +82,7 @@ subgroup_feature_selection_err_max_depth4_plot <- create_visualizer(
 subgroup_thresholds_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
   .name = "Subgroup Thresholds Distribution Plot",
+  method_levels = method_levels,
   size_preset = "medium"
 )
 
@@ -75,24 +90,28 @@ subgroup_thresholds_max_depth2_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
   .name = "Subgroup Thresholds Distribution Plot (max depth = 2)",
   eval_name = "Thresholds Summary (max depth = 2)",
+  method_levels = method_levels,
   size_preset = "medium"
 )
 subgroup_thresholds_max_depth3_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
   .name = "Subgroup Thresholds Distribution Plot (max depth = 3)",
   eval_name = "Thresholds Summary (max depth = 3)",
+  method_levels = method_levels,
   size_preset = "medium"
 )
 subgroup_thresholds_max_depth4_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
   .name = "Subgroup Thresholds Distribution Plot (max depth = 4)",
   eval_name = "Thresholds Summary (max depth = 4)",
+  method_levels = method_levels,
   size_preset = "medium"
 )
 
 subgroup_thresholds_errorbar_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
[…]

### 2024-12-03 causalDT-manuscript/R/method/methods.R
add rulefit

@@ -6,6 +6,7 @@ causalDT_method <- function(X, Y, Z,
                             student_model = "rpart",
                             rpart_control = NULL,
                             rpart_prune = c("none", "min", "1se"),
+                            rulefit_args = list(seed = 1),
                             nfolds_crossfit = NULL,
                             nreps_crossfit = NULL,
                             B_stability = 0,
@@ -20,6 +21,14 @@ causalDT_method <- function(X, Y, Z,
     rpart_prune0 <- "none"
   } else {
     rpart_prune0 <- rpart_prune
+  }
+
+  if (identical(student_model, "rulefit")) {
+    student_model <- purrr::partial(
+      student_rulefit,
+      rulefit_args = rulefit_args
+    )
+    # h2o::h2o.init()
   }
 
   start_time <- Sys.time()
@@ -111,6 +120,10 @@ causalDT_method <- function(X, Y, Z,
       max_depth_stability = max_depth_stability,
       causalDT_args = causalDT_args
     )
+  }
+
+  if (identical(student_model, "rulefit")) {
+    # h2o::h2o.shutdown(prompt = FALSE)
   }
 
   detailed_out <- NULL

### 2024-12-03 causalDT-manuscript/R/method/rulefit-utils.R

@@ -1,0 +1,91 @@
+#' fit rulefit as the student model in CDT
+student_rulefit <- function(X, y, rulefit_args = list(seed = 1)) {
+  # return "null" values if y is the constant vector
+  if (length(unique(y)) == 1) {
+    out <- list(
+      fit = NULL,
+      tree_info = NULL,
+      subgroups = list(),
+      predictions = rep(unique(y), nrow(X))
+    )
+  } else {
+    # h2o::h2o.init()
+
+    df <- h2o::as.h2o(data.frame(X, y))
+
+    # Set the predictors and response; set the factors:
+    response <- "y"
+    predictors <- colnames(data.frame(X))
+
+    fit <- do.call(
+      h2o::h2o.rulefit,
+      args = c(
+        list(
+          y = response,
+          x = predictors,
+          training_frame = df
+        ),
+        rulefit_args
+      )
+    )
+
+    tree_info <- get_rulefit_str(fit)
+    subgroups <- get_rulefit_subgroups(fit)
+    predictions <- as.vector(predict(fit, df))
+    out <- list(
+      fit = fit,
+      tree_info = tree_info,
+      subgroups = subgroups,
+      predictions = predictions
+    )
+    # h2o::h2o.shutdown(prompt = FALSE)
+  }
+  return(out)
+}
+
+
+#' Get model structure from rulefit fit
+get_rulefit_str <- function(fit) {
+  rulefit_imp_df <- h2o::h2o.rule_importance(fit)
+
+  # columns: variable, coefficient, support, rule
+  # columns in model_str:
+  # var type node ix left count ncat improve thr adj
+  splits_list <- unlist(stringr::str_split(rulefit_imp_df$rule, "[[or]]|&")) |>
+    stringr::str_trim() |>
+    stringr::str_remove_all("^\\(|\\)$")
+  splits_df <- data.frame(rule = splits_list) |>
+    dplyr::filter(rule != "") |>
+    dplyr::mutate(
+      rule_split = stringr::str_split(rule, " "),
+      var = purrr::map_chr(rule_split, ~ .x[1]),
+      thr = purrr::map_dbl(rule_split, ~ suppressWarnings(as.numeric(.x[3]))),
+      left = purrr::map_chr(rule_split, ~ paste(.x[2], .x[3]))
+    ) |>
+    dplyr::filter(!is.na(thr))
+
+  return(splits_df)
[…]

### 2024-12-03 causalDT-manuscript/meals/04a_and_subgroup_rulefit.R

@@ -1,0 +1,139 @@
+rm(list = ls())
+EXP_NAME <- "Rulefit Simulations"
+N_REPS <- 100
+SAVE <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
+CHECKPOINT_N_REPS <- 10
+set.seed(331)
+
+source(here::here(file.path("meals", "setup.R")))
+N_REPS <- 100
+
+#### DGPs ####
+
+source(here::here(file.path("meals", "shared_dgps.R")))
+
+#### Methods ####
+
+source(here::here(file.path("meals", "shared_methods.R")))
+
+#### Evaluators and Visualizers ####
+
+source(here::here(file.path("meals", "shared_evaluators.R")))
+source(here::here(file.path("meals", "shared_visualizers.R")))
+
+#### Run Experiment ####
+dgp <- gaussian_X_unbiased_Z_and
+print(dgp$name)
+
+source(here::here(file.path("meals", "shared_experiments.R")))
+rulefit_experiment <- rulefit_experiment |>
+  add_dgp(dgp) |>
+  add_vary_across(
+    .dgp = dgp$name,
+    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+  )
+# out <- run_experiment(rulefit_experiment)
+out <- run_experiment(
+  rulefit_experiment, n_reps = N_REPS, save = SAVE,
+  use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
+  future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
+)
+
+
+dgps <- list(
+  gaussian_X_unbiased_Z_and,
+  gaussian_X_unbiased_Z_or,
+  gaussian_X_unbiased_Z_additive,
+  gaussian_X_unbiased_Z_and_cov,
+  gaussian_X_unbiased_Z_or_cov,
+  gaussian_X_unbiased_Z_additive_cov
+)
+
+for (dgp in dgps) {
+  print(dgp$name)
+
+  source(here::here(file.path("meals", "shared_experiments.R")))
+  rulefit_experiment <- rulefit_experiment |>
+    add_dgp(dgp) |>
+    add_vary_across(
+      .dgp = dgp$name,
+      tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+    )
+  h2o::h2o.init()
+  fit_results <- fit_experiment(
[…]

### 2024-12-03 causalDT-manuscript/meals/shared_experiments.R

@@ -36,6 +36,30 @@ experiment <- create_experiment(
   add_visualizer(subgroup_cates_err_max_depth2_plot) |>
   add_visualizer(subgroup_stability_plot)
 
+rulefit_experiment <- create_experiment(
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
+) |>
+  ### distillation methods
+  add_method(distilled_causal_forest_method) |>
+  add_method(distilled_causal_forest_rulefit_v1_method) |>
+  add_method(distilled_causal_forest_rulefit_v2_method) |>
+  add_method(distilled_causal_forest_rulefit_v3_method) |>
+  add_method(distilled_causal_forest_rulefit_v4_method) |>
+  add_method(distilled_causal_forest_rulefit_v5_method) |>
+  add_method(distilled_causal_forest_rulefit_v6_method) |>
+  ### evaluators
+  add_evaluator(subgroup_feature_selection_errors_summary) |>
+  add_evaluator(subgroup_thresholds_summary) |>
+  add_evaluator(subgroup_threshold_dist_summary) |>
+  add_evaluator(subgroup_cate_err_summary) |>
+  ### visualizers
+  add_visualizer(subgroup_feature_selection_err_plot) |>
+  add_visualizer(subgroup_thresholds_plot) |>
+  add_visualizer(subgroup_threshold_dist_plot) |>
+  add_visualizer(subgroup_nsplits_plot) |>
+  add_visualizer(subgroup_ntrees_plot) |>
+  add_visualizer(subgroup_cates_err_plot)
+
 old_experiment <- create_experiment(
   name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>

### 2024-12-03 causalDT-manuscript/meals/shared_methods.R

@@ -23,6 +23,64 @@ distilled_rlasso_method <- create_method(
   rpart_prune = "min"
 )
 
+# rulefit methods without stability diagnostics
+distilled_causal_forest_rulefit_v1_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v1)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(seed = 1)
+)
+
+distilled_causal_forest_rulefit_v2_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v2)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(
+    seed = 1, min_rule_length = 2, max_rule_length = 2
+  )
+)
+
+distilled_causal_forest_rulefit_v3_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v3)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(
+    seed = 1, min_rule_length = 2, max_rule_length = 2, max_num_rules = 4
+  )
+)
+
+distilled_causal_forest_rulefit_v4_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v4)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(seed = 1, model_type = "rules")
+)
+
+distilled_causal_forest_rulefit_v5_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v5)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(
+    seed = 1, min_rule_length = 2, max_rule_length = 2, model_type = "rules"
+  )
+)
+
+distilled_causal_forest_rulefit_v6_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled Causal Forest (rulefit v6)",
+  teacher_model = "causal_forest",
+  student_model = "rulefit",
+  rulefit_args = list(
+    seed = 1, min_rule_length = 2, max_rule_length = 2, max_num_rules = 4,
+    model_type = "rules"
+  )
+)
+
 # with stability diagnostics
 distilled_causal_forest_stability_method <- create_method(
   .method_fun = causalDT_method,

### 2024-12-03 causalDT/R/student.R

@@ -132,7 +132,12 @@ estimate_group_cates <- function(fit, X, Y, Z) {
     if ("rpart" %in% class(fit)) {
       fit <- partykit::as.party(fit)
     }
-    leaf_ids <- predict(fit, data.frame(X), type = 'node')
+    if ("H2ORegressionModel" %in% class(fit)) {
+      leaf_ids <- predict(fit, h2o::as.h2o(data.frame(X)), type = 'node') |>
+        as.vector()
+    } else {
+      leaf_ids <- predict(fit, data.frame(X), type = 'node')
+    }
   } else {
     leaf_ids <- NULL
   }

### 2024-12-03 causalDT-manuscript/R/method/rulefit-utils.R
add rulefit using pre

@@ -1,5 +1,8 @@
 #' fit rulefit as the student model in CDT
-student_rulefit <- function(X, y, rulefit_args = list(seed = 1)) {
+student_rulefit <- function(X, y, rulefit_args = list(seed = 1),
+                            package = "pre") {
+  package <- match.arg(package)
+
   # return "null" values if y is the constant vector
   if (length(unique(y)) == 1) {
     out <- list(
@@ -9,83 +12,169 @@ student_rulefit <- function(X, y, rulefit_args = list(seed = 1)) {
       predictions = rep(unique(y), nrow(X))
     )
   } else {
-    # h2o::h2o.init()
+    if (package == "h2o") {
+      # h2o::h2o.init()
+      df <- h2o::as.h2o(data.frame(X, y))
 
-    df <- h2o::as.h2o(data.frame(X, y))
+      # Set the predictors and response; set the factors:
+      response <- "y"
+      predictors <- colnames(data.frame(X))
 
-    # Set the predictors and response; set the factors:
-    response <- "y"
-    predictors <- colnames(data.frame(X))
-
-    fit <- do.call(
-      h2o::h2o.rulefit,
-      args = c(
-        list(
-          y = response,
-          x = predictors,
-          training_frame = df
-        ),
-        rulefit_args
+      fit <- do.call(
+        h2o::h2o.rulefit,
+        args = c(
+          list(
+            y = response,
+            x = predictors,
+            training_frame = df
+          ),
+          rulefit_args
+        )
       )
-    )
 
-    tree_info <- get_rulefit_str(fit)
-    subgroups <- get_rulefit_subgroups(fit)
-    predictions <- as.vector(predict(fit, df))
-    out <- list(
-      fit = fit,
-      tree_info = tree_info,
-      subgroups = subgroups,
-      predictions = predictions
-    )
-    # h2o::h2o.shutdown(prompt = FALSE)
+      tree_info <- get_rulefit_str(fit)
+      subgroups <- get_rulefit_subgroups(fit)
+      predictions <- as.vector(predict(fit, df))
+      out <- list(
+        fit = fit,
+        tree_info = tree_info,
+        subgroups = subgroups,
+        predictions = predictions
+      )
+      # h2o::h2o.shutdown(prompt = FALSE)
+    } else if (package == "pre") {
[…]

### 2024-12-03 causalDT/R/student.R

@@ -136,7 +136,10 @@ estimate_group_cates <- function(fit, X, Y, Z) {
       leaf_ids <- predict(fit, h2o::as.h2o(data.frame(X)), type = 'node') |>
         as.vector()
     } else {
-      leaf_ids <- predict(fit, data.frame(X), type = 'node')
+      leaf_ids <- tryCatch(
+        predict(fit, data.frame(X), type = 'node'),
+        error = function(e) as.numeric(as.factor(predict(fit, data.frame(X))))
+      )
     }
   } else {
     leaf_ids <- NULL

### 2024-12-03 causalDT/R/student.R
remove h2o from causalDT package

@@ -94,7 +94,9 @@ student_rpart <- function(X, y, method = "anova", rpart_control = NULL,
 #' @param fit Fitted subgroup model used to determine subgroup membership of
 #'   individuals. Typically, this is a `party` or `rpart` object, but any model
 #'   object that can be used to determine subgroup membership via
-#'   `predict(fit, x, type = 'node')` can be used.
+#'   `predict(fit, x, type = 'node')` can be used. If
+#'   `predict(fit, x, type = 'node')` returns an error, then subgroups are
+#'   determined based upon the unique values of `predict(fit, x)`.
 #'
 #' @returns
 #' Estimated subgroup average treatment effects tibble with the following columns:
@@ -132,15 +134,10 @@ estimate_group_cates <- function(fit, X, Y, Z) {
     if ("rpart" %in% class(fit)) {
       fit <- partykit::as.party(fit)
     }
-    if ("H2ORegressionModel" %in% class(fit)) {
-      leaf_ids <- predict(fit, h2o::as.h2o(data.frame(X)), type = 'node') |>
-        as.vector()
-    } else {
-      leaf_ids <- tryCatch(
-        predict(fit, data.frame(X), type = 'node'),
-        error = function(e) as.numeric(as.factor(predict(fit, data.frame(X))))
-      )
-    }
+    leaf_ids <- tryCatch(
+      predict(fit, data.frame(X), type = 'node'),
+      error = function(e) as.numeric(as.factor(predict(fit, data.frame(X))))
+    )
   } else {
     leaf_ids <- NULL
   }

### 2024-12-03 causalDT-manuscript/R/method/methods.R
remove h2o rulefit

@@ -6,7 +6,7 @@ causalDT_method <- function(X, Y, Z,
                             student_model = "rpart",
                             rpart_control = NULL,
                             rpart_prune = c("none", "min", "1se"),
-                            rulefit_args = list(seed = 1),
+                            rulefit_args = NULL,
                             nfolds_crossfit = NULL,
                             nreps_crossfit = NULL,
                             B_stability = 0,
@@ -24,11 +24,10 @@ causalDT_method <- function(X, Y, Z,
   }
 
   if (identical(student_model, "rulefit")) {
-    student_model <- purrr::partial(
-      student_rulefit,
-      rulefit_args = rulefit_args
+    student_model <- do.call(
+      purrr::partial,
+      args = c(list(.f = student_rulefit), rulefit_args)
     )
-    # h2o::h2o.init()
   }
 
   start_time <- Sys.time()
@@ -120,10 +119,6 @@ causalDT_method <- function(X, Y, Z,
       max_depth_stability = max_depth_stability,
       causalDT_args = causalDT_args
     )
-  }
-
-  if (identical(student_model, "rulefit")) {
-    # h2o::h2o.shutdown(prompt = FALSE)
   }
 
   detailed_out <- NULL

### 2024-12-03 causalDT-manuscript/R/method/rulefit-utils.R

@@ -1,8 +1,5 @@
 #' fit rulefit as the student model in CDT
-student_rulefit <- function(X, y, rulefit_args = list(seed = 1),
-                            package = "pre") {
-  package <- match.arg(package)
-
+student_rulefit <- function(X, y, ...) {
   # return "null" values if y is the constant vector
   if (length(unique(y)) == 1) {
     out <- list(
@@ -12,135 +9,59 @@ student_rulefit <- function(X, y, rulefit_args = list(seed = 1),
       predictions = rep(unique(y), nrow(X))
     )
   } else {
-    if (package == "h2o") {
-      # h2o::h2o.init()
-      df <- h2o::as.h2o(data.frame(X, y))
-
-      # Set the predictors and response; set the factors:
-      response <- "y"
-      predictors <- colnames(data.frame(X))
-
-      fit <- do.call(
-        h2o::h2o.rulefit,
-        args = c(
-          list(
-            y = response,
-            x = predictors,
-            training_frame = df
-          ),
-          rulefit_args
-        )
-      )
-
-      tree_info <- get_rulefit_str(fit)
-      subgroups <- get_rulefit_subgroups(fit)
-      predictions <- as.vector(predict(fit, df))
-      out <- list(
-        fit = fit,
-        tree_info = tree_info,
-        subgroups = subgroups,
-        predictions = predictions
-      )
-      # h2o::h2o.shutdown(prompt = FALSE)
-    } else if (package == "pre") {
-
-      df <- data.frame(X, y)
-      fit <- do.call(
-        pre::pre,
-        args = c(
-          list(
-            formula = y ~ .,
-            data = df
-          ),
-          rulefit_args
-        )
-      )
-
-      tree_info <- get_rulefit_str(fit, package = package)
-      subgroups <- get_rulefit_subgroups(fit, package = package)
-      predictions <- as.vector(predict(fit, df))
-      out <- list(
-        fit = fit,
-        tree_info = tree_info,
-        subgroups = subgroups,
-        predictions = predictions
-      )
-    }
+    df <- data.frame(X, y)
+    fit <- pre::pre(y ~ ., data = df, ...)
+    tree_info <- get_rulefit_str(fit)
+    subgroups <- get_rulefit_subgroups(fit)
[…]

### 2024-12-03 causalDT-manuscript/meals/04_rulefit_simulations.R

@@ -1,0 +1,63 @@
+rm(list = ls())
+EXP_NAME <- "Rulefit Simulations"
+N_REPS <- 100
+SAVE <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
+CHECKPOINT_N_REPS <- 10
+set.seed(331)
+
+source(here::here(file.path("meals", "setup.R")))
+N_REPS <- 100
+
+#### Cluster setup for parallelization (or comment out) ####
+# n_workers <- min(N_REPS, availableCores() - 1)
+n_workers <- 8
+# n_workers <- 2
+plan(multisession, workers = n_workers)
+
+#### DGPs ####
+
+source(here::here(file.path("meals", "shared_dgps.R")))
+
+#### Methods ####
+
+source(here::here(file.path("meals", "shared_methods.R")))
+
+#### Evaluators and Visualizers ####
+
+source(here::here(file.path("meals", "shared_evaluators.R")))
+source(here::here(file.path("meals", "shared_visualizers.R")))
+
+#### Run Experiment ####
+dgps <- list(
+  gaussian_X_unbiased_Z_and,
+  gaussian_X_unbiased_Z_or,
+  gaussian_X_unbiased_Z_additive,
+  gaussian_X_unbiased_Z_and_cov,
+  gaussian_X_unbiased_Z_or_cov,
+  gaussian_X_unbiased_Z_additive_cov
+)
+
+for (dgp in dgps) {
+  print(dgp$name)
+
+  source(here::here(file.path("meals", "shared_experiments.R")))
+  rulefit_experiment <- rulefit_experiment |>
+    add_dgp(dgp) |>
+    add_vary_across(
+      .dgp = dgp$name,
+      tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+    )
+  fit_results <- fit_experiment(
+    rulefit_experiment, n_reps = N_REPS, save = SAVE,
+    use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
+    future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
+  )
+  eval_results <- evaluate_experiment(
+    rulefit_experiment, fit_results, save = SAVE, use_cached = USE_CACHED
+  )
+}
+
+render_docs(save_dir = file.path(rulefit_experiment$get_save_dir(), dgp$name))
+

### 2024-12-03 causalDT-manuscript/meals/shared_experiments.R

@@ -45,8 +45,6 @@ rulefit_experiment <- create_experiment(
   add_method(distilled_causal_forest_rulefit_v2_method) |>
   add_method(distilled_causal_forest_rulefit_v3_method) |>
   add_method(distilled_causal_forest_rulefit_v4_method) |>
-  add_method(distilled_causal_forest_rulefit_v5_method) |>
-  add_method(distilled_causal_forest_rulefit_v6_method) |>
   ### evaluators
   add_evaluator(subgroup_feature_selection_errors_summary) |>
   add_evaluator(subgroup_thresholds_summary) |>

### 2024-12-03 causalDT-manuscript/meals/shared_methods.R

@@ -29,7 +29,7 @@ distilled_causal_forest_rulefit_v1_method <- create_method(
   .name = "Distilled Causal Forest (rulefit v1)",
   teacher_model = "causal_forest",
   student_model = "rulefit",
-  rulefit_args = list(seed = 1)
+  rulefit_args = NULL
 )
 
 distilled_causal_forest_rulefit_v2_method <- create_method(
@@ -37,9 +37,7 @@ distilled_causal_forest_rulefit_v2_method <- create_method(
   .name = "Distilled Causal Forest (rulefit v2)",
   teacher_model = "causal_forest",
   student_model = "rulefit",
-  rulefit_args = list(
-    seed = 1, min_rule_length = 2, max_rule_length = 2
-  )
+  rulefit_args = list(maxdepth = 2)
 )
 
 distilled_causal_forest_rulefit_v3_method <- create_method(
@@ -47,9 +45,7 @@ distilled_causal_forest_rulefit_v3_method <- create_method(
   .name = "Distilled Causal Forest (rulefit v3)",
   teacher_model = "causal_forest",
   student_model = "rulefit",
-  rulefit_args = list(
-    seed = 1, min_rule_length = 2, max_rule_length = 2, max_num_rules = 4
-  )
+  rulefit_args = list(type = "rules")
 )
 
 distilled_causal_forest_rulefit_v4_method <- create_method(
@@ -57,28 +53,7 @@ distilled_causal_forest_rulefit_v4_method <- create_method(
   .name = "Distilled Causal Forest (rulefit v4)",
   teacher_model = "causal_forest",
   student_model = "rulefit",
-  rulefit_args = list(seed = 1, model_type = "rules")
-)
-
-distilled_causal_forest_rulefit_v5_method <- create_method(
-  .method_fun = causalDT_method,
-  .name = "Distilled Causal Forest (rulefit v5)",
-  teacher_model = "causal_forest",
-  student_model = "rulefit",
-  rulefit_args = list(
-    seed = 1, min_rule_length = 2, max_rule_length = 2, model_type = "rules"
-  )
-)
-
-distilled_causal_forest_rulefit_v6_method <- create_method(
-  .method_fun = causalDT_method,
-  .name = "Distilled Causal Forest (rulefit v6)",
-  teacher_model = "causal_forest",
-  student_model = "rulefit",
-  rulefit_args = list(
[…]

### 2024-12-03 causalDT-manuscript/meals/04_rulefit_simulations.R
update rulefit simulations

@@ -4,7 +4,7 @@ N_REPS <- 100
 SAVE <- TRUE
 # USE_CACHED <- FALSE
 USE_CACHED <- TRUE
-CHECKPOINT_N_REPS <- 10
+CHECKPOINT_N_REPS <- 0
 set.seed(331)
 
 source(here::here(file.path("meals", "setup.R")))

### 2024-12-03 causalDT-manuscript/meals/04a_and_subgroup_rulefit.R

@@ -1,139 +1,0 @@
-rm(list = ls())
-EXP_NAME <- "Rulefit Simulations"
-N_REPS <- 100
-SAVE <- TRUE
-# USE_CACHED <- FALSE
-USE_CACHED <- TRUE
-CHECKPOINT_N_REPS <- 10
-set.seed(331)
-
-source(here::here(file.path("meals", "setup.R")))
-N_REPS <- 100
-
-#### DGPs ####
-
-source(here::here(file.path("meals", "shared_dgps.R")))
-
-#### Methods ####
-
-source(here::here(file.path("meals", "shared_methods.R")))
-
-#### Evaluators and Visualizers ####
-
-source(here::here(file.path("meals", "shared_evaluators.R")))
-source(here::here(file.path("meals", "shared_visualizers.R")))
-
-#### Run Experiment ####
-dgp <- gaussian_X_unbiased_Z_and
-print(dgp$name)
-
-source(here::here(file.path("meals", "shared_experiments.R")))
-rulefit_experiment <- rulefit_experiment |>
-  add_dgp(dgp) |>
-  add_vary_across(
-    .dgp = dgp$name,
-    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
-  )
-# out <- run_experiment(rulefit_experiment)
-out <- run_experiment(
-  rulefit_experiment, n_reps = N_REPS, save = SAVE,
-  use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
-  future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
-)
-
-
-dgps <- list(
-  gaussian_X_unbiased_Z_and,
-  gaussian_X_unbiased_Z_or,
-  gaussian_X_unbiased_Z_additive,
-  gaussian_X_unbiased_Z_and_cov,
-  gaussian_X_unbiased_Z_or_cov,
-  gaussian_X_unbiased_Z_additive_cov
-)
-
-for (dgp in dgps) {
-  print(dgp$name)
-
-  source(here::here(file.path("meals", "shared_experiments.R")))
-  rulefit_experiment <- rulefit_experiment |>
-    add_dgp(dgp) |>
-    add_vary_across(
-      .dgp = dgp$name,
-      tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
-    )
-  h2o::h2o.init()
-  fit_results <- fit_experiment(
[…]

### 2024-12-03 causalDT-manuscript/meals/setup.R

@@ -28,6 +28,8 @@ cat(sprintf("Saving results to: %s\n", SAVE_DIR))
 
 FUTURE_GLOBALS <- c(
   "dummy_code", "causaltree_wrapper", "get_interaction_formula",
-  "tidy_lm", "tidy_glmnet", "get_lm_info", "get_lm_subgroups"
+  "tidy_lm", "tidy_glmnet", "get_lm_info", "get_lm_subgroups",
+  "student_rulefit", "get_rulefit_str", "get_rulefit_subgroups",
+  "clean_pre_rules"
 )
 FUTURE_PACKAGES <- c("causalDT", "causalTree")

### 2024-12-05 causalDT-manuscript/notebooks/paper_figures.Rmd
add nreps_crossfit simulations + bug fixes

@@
 
-KEEP_METHODS <- c(
-  "Distilled Causal Forest",
-  "Distilled Rboost",
-  "Distilled Rlasso",
-  "Virtual Twins",
-  "Causal Tree (pruned)",
-  "Causal Tree (unpruned)",
-  "Linear Regression",
-  "Lasso"
-)
 COLORS <- c(
-  # "Distilled Causal Forest" = "#3153A5",
   "Distilled Causal Forest" = "#1f5d8f",
-  # "Distilled Causal Forest" = "#5d8cae",
-  # "Distilled Rboost" = "#94B1c9",
-  # "Distilled Rboost" = "#678096",
-  ## "Distilled Rboost" = "#79b2dd",
   "Distilled Rboost" = "#6aafe4",
-  # "Distilled Rboost" = "#6DA7D3",
-  # "Distilled Rboost" = "#6DA7D3",
-  # "Distilled Rlasso" = "#ACC2D0",
-  "Distilled Rlasso" = "#9ab6c8",
-  # "Distilled Rlasso" = "#B8CEDD",
   "Virtual Twins" = "#768c50",
-  # "Virtual Twins" = "#6F9940",
-  "Causal Tree (pruned)" = "#953a2f",
-  "Causal Tree (unpruned)" = "#DB9685",
-  # "Linear Regression" = "#DAA520",
+  "Causal Tree" = "#953a2f",
   "Linear Regression" = "#b2954a",
   "Lasso" = "#D2BE90"
-  # "Lasso" = "#e4d2a4"
+)
+CROSSFIT_COLORS <- c(
+  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
+)
+RULEFIT_COLORS <- c(
+  "CART" = "#1f5d8f",
+  "Rulefit (both, max depth = 3)" = "#FF9300",
+  "Rulefit (both, max depth = 2)" = "#E7298A",
+  "Rulefit (rules only, max depth = 3)" = "#66A61E",
+  "Rulefit (rules only, max depth = 2)" = "#7570B3"
+)
+LINETYPES <- c(
+  "Pruned" = "solid",
+  "Unpruned" = "dashed"
 )
@@
 FACET_LABS <- list(
-  "0.2" = "Weak",
-  "0.6" = "Moderate",
-  "1" = "High"
+  "0.2" = "Weak (0.2)",
+  "0.6" = "Moderate (0.6)",
+  "1" = "Strong (1)"
 )
@@
     return(FACET_LABS[as.character(value)])
+  } else if (variable == "metric") {
+    return(METRIC_LABS[as.character(value)])
   } else {
@@
   }
+}
+
+add_pruned_column <- function(data) {
+  data |> 
+    dplyr::mutate(
+      .is_pruned = dplyr::case_when(
+        stringr::str_detect(.method_name, "unpruned") ~ "Unpruned",
+        TRUE ~ "Pruned"
+      ),
+      .method_name = stringr::str_remove(.method_name, " \\(unpruned\\)")
+    )
+}
+
+rename_rulefit_methods <- function(data) {
+  data <- data |> 
+    dplyr::mutate(
+      .method_name = dplyr::case_when(
+        .method_name == "Distilled Causal Forest" ~ "CART",
+        .method_name == "Distilled Causal Forest (rulefit v1)" ~ "Rulefit (both, max depth = 3)",
+        .method_name == "Distilled Causal Forest (rulefit v2)" ~ "Rulefit (both, max depth = 2)",
+        .method_name == "Distilled Causal Forest (rulefit v3)" ~ "Rulefit (rules only, max depth = 3)",
+        .method_name == "Distilled Causal Forest (rulefit v4)" ~ "Rulefit (rules only, max depth = 2)",
+      )
+    )
+  return(data)
 }
@@
   )
+
+example_experiment <- example_experiment |>
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    n = c(100, 500, 1000, 2000)
+  )
+
+crossfit_experiment <- crossfit_experiment |>
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+  )
+
+rulefit_experiment <- rulefit_experiment |> 
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+  )
 ```
 
+## Toy Example {.tabset .tabset-pills .tabset-pills-square}
+
 ```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Main Simulations")
+)
 sim_names <- c(
@@
 )
+
+keep_methods_ls <- list(
+  "causal_tree_only" = c("Causal Tree"),
+  "all_methods" = c("Distilled Causal Forest", "Causal Tree")
+)
+
+for (keep_methods_idx in 1:length(keep_methods_ls)) {
+  keep_methods <- keep_methods_ls[[keep_methods_idx]]
+  keep_methods_name <- names(keep_methods_ls)[keep_methods_idx]
+  for (sim_name in sim_names) {
+    fit_results <- readRDS(
+      file.path(
+        sim_results_dir, sim_name, "Varying n", "fit_results.rds"
+      )
+    )
+    eval_results <- readRDS(
+      file.path(
+        sim_results_dir, sim_name, "Varying n", "eval_results.rds"
+      )
+    )
+    viz_results <- visualize_experiment(
+      example_experiment, fit_results, eval_results
+    )
+
+    plt <- viz_results$`Number of Subgroups Plot`
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% !!keep_methods
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = keep_methods,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = keep_methods,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        x = "Sample Size"
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98")
+      )
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR, 
+        sprintf("sim_example_nsubgroup_%s.pdf", keep_methods_name)
+      ),
+      height = 3.1,
+      width = 11.5
+    )
+  }
+}
+```
+
+## Main Simulations {.tabset .tabset-pills .tabset-pills-square}
+
+```{r results = "asis"}
 sim_results_dir <- here::here(
-  file.path("results", "Unbiased W")
-)
-
-plt_subgroup_ls <- list()
-plt_subgroup2_ls <- list()
-plt_thresholds_ls <- list()
-plt_stability_ls <- list()
-plt_freq_ls <- list()
-for (sim_name in sim_names) {
-  cat(sprintf("\n\n## %s {.tabset .tabset-pills .tabset-square}\n\n", sim_name))
-
-  # fit_results <- readRDS(
-  #   file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
-  # ) |>
-  #   dplyr::filter(
-  #     .method_name %in% !!KEEP_METHODS
-  #   )
-  # eval_results <- evaluate_experiment(experiment, fit_results)
-  # viz_results <- visualize_experiment(experiment, fit_results, eval_results)
-  # 
-  # plt_selection <- viz_results$`Subgroup Feature Selection Errors Plot` +
-  #   ggplot2::scale_color_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::scale_fill_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   )
-  # 
-  # plt_cate <- viz_results$`Subgroup CATE Errors Plot` +
-  #   ggplot2::scale_color_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::scale_fill_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::labs(
-  #     y = "CATE RMSE"
-  #   ) +
-  #   vthemes::theme_vmodern(
-  #     axis_title_size = 16,
-  #     axis_text_size = 12,
-  #     legend_title_size = 16,
-  #     legend_text_size = 12
-  #   ) +
-  #   ggplot2::theme(
-  #     strip.background = ggplot2::element_blank(),
-  #     strip.placement = "outside"
-  #     # strip.background = ggplot2::element_rect(
-  #     #   color = "transparent", fill = "transparent"
-  #     # ),
-  #     # strip.text = ggplot2::element_text(
-  #     #   color = "black", face = "bold", size = 16
-  #     # )
-  #   ) +
-  #   ggplot2::guides(
-  #     color = "none", fill = "none"
-  #   )
-  # 
-  # pplt <- patchwork::wrap_plots(
-  #   plt_selection, plt_cate, nrow = 1, guides = "collect",
-  #   widths = c(3.5, 1)
-  # ) &
-  #   ggplot2::labs(x = NULL)
-  # plt_subgroup_ls[[sim_name]] <- pplt
-  # plt <- patchwork::wrap_elements(pplt) +
-  #   ggplot2::labs(
-  #     tag = expression(
-  #       bold(paste("Proportion of Variance Explained in ", tau))
-  #     )
-  #   ) +
-  #   ggplot2::theme(
-  #     plot.tag = ggplot2::element_text(
-  #       size = 16
-  #     ),
-  #     plot.tag.position = c(0.45, 0),
-  #     plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
-  #   )
-  # plt_subgroup2_ls[[sim_name]] <- plt
-
+  file.path("results", "Main Simulations")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP",
+  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
+  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
+  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
   fit_results <- readRDS(
-    file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
-  ) |>
-    dplyr::filter(
-      .method_name %in% !!KEEP_METHODS,
-      tau_heritability %in% c(0.2, 0.6, 1)
-    )
-  eval_results <- evaluate_experiment(experiment, fit_results)
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds"
+    )
+  )
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
+    )
+  )
   viz_results <- visualize_experiment(experiment, fit_results, eval_results)
-
-  plt_thresholds <- viz_results$`Subgroup Thresholds Distribution Plot` +
-    ggplot2::scale_color_manual(
-      breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::scale_fill_manual(
-      breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller)
-  plt_thresholds_ls[[sim_name]] <- plt_thresholds
-
-  plt_stability <- viz_results$`Subgroup Stability Diagnostics Plot`[[1]] +
-    ggplot2::scale_color_manual(
-      breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::scale_fill_manual(
-      breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::facet_grid(~ tau_heritability, labeller = signal_labeller) +
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Estimated Subgroup CATEs
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.03, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.5, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
+  height = 9, 
+  width = 14
+)
+
+## with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.06, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.75), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.45, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
+  height = 9, 
+  width = 14
+)
+```
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Causal Tree",
+  "Causal Tree (unpruned)"
+)
+
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_feature_selection_err - se_feature_selection_err,
+      ymax = mean_feature_selection_err + se_feature_selection_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_feature_selection_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_linetype_manual(
+        values = LINETYPES
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_cate_err - se_cate_err,
+      ymax = mean_cate_err + se_cate_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_cate_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_linetype_manual(
+        values = LINETYPES
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL, linetype = "Pruning Mode")
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none", linetype = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.03, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        ),
+        legend.key.width = ggplot2::unit(0.9, "cm")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.5, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_with_pruning.pdf"),
+  height = 9, 
+  width = 14
+)
+
+## with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_feature_selection_err - se_feature_selection_err,
+      ymax = mean_feature_selection_err + se_feature_selection_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_feature_selection_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_linetype_manual(
+        values = LINETYPES
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_cate_err - se_cate_err,
+      ymax = mean_cate_err + se_cate_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_cate_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_linetype_manual(
+        values = LINETYPES
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL, linetype = "Pruning Mode")
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none", linetype = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.06, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.75), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        ),
+        legend.key.width = ggplot2::unit(0.9, "cm")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.45, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov_with_pruning.pdf"),
+  height = 9, 
+  width = 14
+)
+```
+
+### Selected Subgroup Features + Estimated Subgroup CATEs (max depth = 2)
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features\n(max depth = 2)"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs\n(max depth = 2)"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.03, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.5, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_max_depth2.pdf"),
+  height = 9.2, 
+  width = 14
+)
+
+## with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features\n(max depth = 2)"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs\n(max depth = 2)"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.06, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.75), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
+    plot.tag.position = c(0.45, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov_max_depth2.pdf"),
+  height = 9.2, 
+  width = 14
+)
+```
+
+### Thresholds Distances
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name),
+        y = "Average  | Estimated Threshold - True Threshold |",
+        x = expression(
+          bold(
+            paste("Proportion of Variance Explained in ", tau, " by Covariates")
+          )
+        )
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        axis.title = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(size = 16),
+        strip.text = ggplot2::element_text(size = 14)
+      )
+    if (sim_name != sim_names[5]) {
+      plt <- plt +
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    if (stringr::str_detect(sim_name, "Linear")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.y = ggplot2::element_blank(),
+          plot.margin = ggplot2::unit(c(0, 0, 0.1, 0.2), units = "in")
+        )
+    } else {
+      plt <- plt +
+        ggplot2::theme(
+          plot.margin = ggplot2::unit(c(0, 0.2, 0.1, 0), units = "in")
+        )
+    }
+    if (!stringr::str_detect(sim_name, "OR")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_blank()
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, byrow = FALSE
+  ) +
+  patchwork::plot_layout(
+    axis_titles = "collect_y"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(
+    FIG_DIR, sprintf("sim_threshold_distances.pdf")
+  ),
+  height = 9, 
+  width = 14
+)
+```
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Causal Tree",
+  "Causal Tree (unpruned)"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_threshold_dist - se_threshold_dist,
+      ymax = mean_threshold_dist + se_threshold_dist,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_threshold_dist,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_linetype_manual(
+        values = LINETYPES
+      ) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name),
+        y = "Average  | Estimated Threshold - True Threshold |",
+        x = expression(
+          bold(
+            paste("Proportion of Variance Explained in ", tau, " by Covariates")
+          )
+        ),
+        linetype = "Pruning Mode"
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        axis.title = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(size = 16),
+        strip.text = ggplot2::element_text(size = 14)
+      )
+    if (sim_name != sim_names[5]) {
+      plt <- plt +
+        ggplot2::guides(
+          color = "none", fill = "none", linetype = "none"
+        )
+    }
+    if (stringr::str_detect(sim_name, "Linear")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.y = ggplot2::element_blank(),
+          plot.margin = ggplot2::unit(c(0, 0, 0.1, 0.2), units = "in")
+        )
+    } else {
+      plt <- plt +
+        ggplot2::theme(
+          plot.margin = ggplot2::unit(c(0, 0.2, 0.1, 0), units = "in")
+        )
+    }
+    if (!stringr::str_detect(sim_name, "OR")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_blank()
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, byrow = FALSE
+  ) +
+  patchwork::plot_layout(
+    axis_titles = "collect_y"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(
+    FIG_DIR, sprintf("sim_threshold_distances_with_pruning.pdf")
+  ),
+  height = 9, 
+  width = 14
+)
+```
+
+### Thresholds Distances (max depth = 2)
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s\n", tag, sim_name),
+        y = "Average  | Estimated Threshold - True Threshold |\n(max depth = 2)",
+        x = expression(
+          bold(
+            paste("Proportion of Variance Explained in ", tau, " by Covariates")
+          )
+        )
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        axis.title = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(size = 16),
+        strip.text = ggplot2::element_text(size = 14)
+      )
+    if (sim_name != sim_names[5]) {
+      plt <- plt +
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    if (stringr::str_detect(sim_name, "Linear")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.y = ggplot2::element_blank(),
+          plot.margin = ggplot2::unit(c(0, 0, 0.1, 0.2), units = "in")
+        )
+    } else {
+      plt <- plt +
+        ggplot2::theme(
+          plot.margin = ggplot2::unit(c(0, 0.2, 0.1, 0), units = "in")
+        )
+    }
+    if (!stringr::str_detect(sim_name, "OR")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_blank()
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, byrow = FALSE
+  ) +
+  patchwork::plot_layout(
+    axis_titles = "collect_y"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(
+    FIG_DIR, sprintf("sim_threshold_distances_max_depth2.pdf")
+  ),
+  height = 9, 
+  width = 14.2
+)
+```
+
+### Threshold Distributions
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, guides = "collect"
+  ) +
+  patchwork::plot_layout(
+    axes = "collect"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds.pdf"),
+  height = 10, 
+  width = 11
+)
+
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, guides = "collect"
+  ) +
+  patchwork::plot_layout(
+    axes = "collect"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_cov.pdf"),
+  height = 10, 
+  width = 11
+)
+```
+
+### Threshold Distributions (max depth = 2)
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        y = "Threshold (max depth = 2)",
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, guides = "collect"
+  ) +
+  patchwork::plot_layout(
+    axes = "collect"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_max_depth2.pdf"),
+  height = 10, 
+  width = 11
+)
+
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        y = "Threshold (max depth = 2)",
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, guides = "collect"
+  ) +
+  patchwork::plot_layout(
+    axes = "collect"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_cov_max_depth2.pdf"),
+  height = 10, 
+  width = 11
+)
+```
+
+### Subgroup Stability
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Causal Tree"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    f1_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "F1"
+      ) |> 
+      dplyr::mutate(
+        .value = mean_feature_selection_err
+      )
+    cate_df <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "rmse"
+      ) |> 
+      dplyr::mutate(
+        .metric = "CATE RMSE",
+        .value = mean_cate_err
+      )
+
+    plt_err <- dplyr::bind_rows(f1_df, cate_df) |> 
+      dplyr::mutate(
+        .metric = forcats::fct_inorder(.metric)
+      ) |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = .value, 
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(
+        stat = "identity", size = 1, width = 0.75
+      ) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        .metric ~ tau_heritability, labeller = signal_labeller, 
+        scales = "free_y", switch = "y"
+      ) +
+      ggplot2::scale_x_discrete(
+        breaks = KEEP_METHODS,
+        labels = stringr::str_replace_all(KEEP_METHODS, " ", "\n")
+      ) +
+      ggplot2::labs(y = "", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background.y = ggplot2::element_blank(),
+        strip.text.y = ggplot2::element_text(
+          color = "black", size = 16
+        ),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_blank(),
+        axis.text.y = ggplot2::element_text(size = 9)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      dplyr::mutate(
+        .metric = "Jaccard SSI"
+      )
+    plt_jaccard <- plt +
+      ggplot2::geom_line(size = 0.75) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        ~ tau_heritability, labeller = signal_labeller, switch = "y"
+      ) +
       ggplot2::coord_cartesian(xlim = c(1, 4)) +
@@
       ) +
+      ggplot2::scale_y_continuous(
+        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
+      ) +
       ggplot2::labs(
         x = "Tree Depth",
-      y = "Mean Jaccard Stability",
+        y = "Jaccard SSI",
         color = "Method",
@@
       ) +
+      vthemes::theme_vmodern(size_preset = "medium") +
+      ggplot2::theme(
+        strip.background.y = ggplot2::element_blank(),
+        strip.text.y = ggplot2::element_text(
+          color = "black", size = 16
+        ),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_blank(),
+        axis.text.y = ggplot2::element_text(size = 9)
+      )
+
+    plt <- patchwork::wrap_plots(
+      plt_jaccard, plt_err,
+      ncol = 1, heights = c(1.2, 2), guides = "collect"
+    ) +
+      patchwork::plot_layout(
+        axis_titles = "collect_x"
+      ) +
+      patchwork::plot_annotation(
+        title = sim_name, 
+        tag_levels = "A", 
+        tag_prefix = "(",
+        tag_suffix = ")",
+        theme = ggplot2::theme(
+          plot.title = ggplot2::element_text(
+            size = 18, face = "italic", hjust = 0.42
+          )
+        )
+      ) &
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(size = 16)#,
+        # legend.position = "bottom"  # for slides
+      )
+    # ggplot2::ggsave(
+    #   plt, 
+    #   filename = file.path(
+    #     FIG_DIR, 
+    #     sprintf("sim_stability_%s_slides.pdf", sim_name)
+    #   ),
+    #   width = 11.5,
+    #   height = 9
+    # )
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR,
+        sprintf("sim_stability_%s.pdf", sim_name)
+      ),
+      width = 10.5,
+      height = 7.5
+    )
+  }
+)
+```
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Causal Tree"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "F1"
+      )
+    plt_f1 <- plt_df |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = mean_feature_selection_err,
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(stat = "identity", size = 1) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
+      ) +
+      ggplot2::labs(y = "F1", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt_df <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "rmse"
+      )
+    plt_cate <- plt_df |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = mean_cate_err,
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(stat = "identity", size = 1) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
+      ) +
+      ggplot2::labs(y = "CATE RMSE", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_jaccard <- plt +
+      ggplot2::geom_line(size = 0.75) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      ggplot2::coord_cartesian(xlim = c(1, 4)) +
+      ggplot2::scale_x_continuous(
+        breaks = 1:4
+      ) +
+      ggplot2::scale_y_continuous(
+        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
+      ) +
+      ggplot2::labs(
+        x = "Tree Depth",
+        y = "Jaccard SSI",
+        color = "Method",
+        fill = "Method"
+      ) +
       vthemes::theme_vmodern(size_preset = "medium")
-  plt_stability_ls[[sim_name]] <- plt_stability
-
-  plt_nsplits <- viz_results$`Number of Splits Plot` +
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[2]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    if (stringr::str_detect(sim_name, "Covariates")) {
+      FT_COLORS <- c(
+        "#d3831b", "#eeb062",# "#e19e49"
+        "#CCCCCC", "#B5B5B5", "#9E9E9E", "#888888",
+        "#717171", "#5A5A5A", "#434343", "#2D2D2D"
+      )
+      # FT_COLORS <- c(
+      #   "#d07d13", "#eeb062",
+      #   # "#FFa59B", "#FFD2CC",
+      #   "#B34363", "#cb8c9d",
+      #   "#9E9E9E", "#888888",
+      #   "#717171", "#5A5A5A", "#434343", "#2D2D2D"
+      # )
+    } else {
+      FT_COLORS <- c(
+        "#d3831b", "#eeb062",# "#e19e49"
+        "#CCCCCC", "#B5B5B5", "#9E9E9E", "#888888",
+        "#717171", "#5A5A5A", "#434343", "#2D2D2D"
+      )
+    }
+    plt_stability_feature <- plt +
+      ggplot2::scale_fill_manual(values = FT_COLORS) +
+      ggplot2::facet_grid(tau_heritability ~ depth, labeller = signal_labeller) +
+      ggplot2::labs(
+        x = "Method",
+        y = "Proportion of Splits",
+        fill = "Variable"
+      ) +
+      vthemes::theme_vmodern(size_preset = "medium") +
+      ggplot2::theme(
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt <- patchwork::wrap_plots(
+      plt_f1, plt_cate, plt_jaccard, plt_stability_feature,
+      nrow = 1, widths = c(0.5, 0.5, 1.25, 3.25), guides = "collect"
+    ) |> 
+      patchwork::wrap_elements() +
+      ggplot2::labs(
+        title = "   (A) Subgroup Estimation       (B) Jaccard Stability                              (C) Feature Stability",
+        tag = sim_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 20, face = "bold", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.32, 0, 0, 0.2), units = "in"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0, vjust = -0.3
+        )
+      )
+
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR, 
+        sprintf("sim_stability_feature_%s.pdf", sim_name)
+      ),
+      height = 8, 
+      width = 14
+    )
+  }
+)
+```
+
+### Number of Feature Splits Heatmap
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Virtual Twins",
+  "Causal Tree",
+  "Causal Tree (unpruned)",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_nsplits <- plt +
       ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
       viridis::scale_fill_viridis(
-      begin = 0.05, end = 1, option = "magma", limits = c(0., 7)
-    )
-  plt_ntrees <- viz_results$`Number of Trees Plot` +
+        begin = 0.1, end = 1, option = "magma", limits = c(0., 4.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_ntrees <- plt +
       ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
       viridis::scale_fill_viridis(
-      begin = 0.05, end = 1, option = "magma", limits = c(0, 100)
-    )
-  plt <- patchwork::wrap_plots(
-    plt_ntrees, plt_nsplits, nrow = 1
-  ) +
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      )
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
       patchwork::plot_layout(
@@
       ) &
-    ggplot2::labs(
-      x = "Variable"
-    )
-
-  plt_freq_ls[[sim_name]] <- plt
-}
+      ggplot2::labs(x = "Variable")
+    plt <- patchwork::wrap_elements(plt) +
+      ggplot2::labs(
+        tag = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq.pdf"),
+  height = 17.5, 
+  width = 15
+)
+
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_nsplits <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0., 4.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_ntrees <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      )
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
+      patchwork::plot_layout(
+        axis_titles = "collect_y"
+      ) &
+      ggplot2::labs(x = "Variable")
+    plt <- patchwork::wrap_elements(plt) +
+      ggplot2::labs(
+        tag = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq_cov.pdf"),
+  height = 17.5, 
+  width = 15
+)
 ```
 
+### Number of Feature Splits Heatmap (max depth = 2)
+
 ```{r}
-plt_subgroup <- purrr::map2(
-  plt_subgroup_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_subgroup_ls[idx])
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
     tag <- LETTERS[idx]
-    if (sim_name != names(plt_subgroup_ls[2])) {
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_nsplits <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0., 4.5)
+      ) +
+      ggplot2::labs(fill = "Average #\nSplits per Tree\n(max depth = 2)")
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_ntrees <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      ) +
+      ggplot2::labs(fill = "# Trees\n(max depth = 2)")
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
+      patchwork::plot_layout(
+        axis_titles = "collect_y"
+      ) &
+      ggplot2::labs(x = "Variable")
+    plt <- patchwork::wrap_elements(plt) +
+      ggplot2::labs(
+        tag = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq_max_depth2.pdf"),
+  height = 17.5, 
+  width = 15
+)
+
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_nsplits <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0., 4.5)
+      ) +
+      ggplot2::labs(fill = "Average #\nSplits per Tree\n(max depth = 2)")
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_ntrees <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      ) +
+      ggplot2::labs(fill = "# Trees\n(max depth = 2)")
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
+      patchwork::plot_layout(
+        axis_titles = "collect_y"
+      ) &
+      ggplot2::labs(x = "Variable")
+    plt <- patchwork::wrap_elements(plt) +
+      ggplot2::labs(
+        tag = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq_cov_max_depth2.pdf"),
+  height = 17.5, 
+  width = 15
+)
+```
+
+## Varying \# Repeated Crossfits Simulations {.tabset .tabset-pills .tabset-pills-square}
+
+```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Varying nrep crossfits")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
+  fit_results <- readRDS(
+    file.path(
+      sim_results_dir, 
+      paste0(sim_name, "-Distilled Causal Forest (crossfit)-Distilled Rboost (crossfit)"), 
+      "Varying tau_heritability-nreps_crossfit", "fit_results.rds"
+    )
+  )
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, 
+      paste0(sim_name, "-Distilled Causal Forest (crossfit)-Distilled Rboost (crossfit)"), 
+      "Varying tau_heritability-nreps_crossfit", "eval_results.rds"
+    )
+  )
+  eval_results <- purrr::map(
+    eval_results,
+    ~ .x |>
+      dplyr::filter(
+        !stringr::str_detect(.method_name, "unpruned"),
+        !stringr::str_detect(.method_name, "Causal Forest")
+      ) |>
+      dplyr::mutate(
+        .method_name = stringr::str_remove_all(.method_name, " \\(.*\\)"),
+        nreps_crossfit = tidyr::replace_na(nreps_crossfit, 0) |>
+          as.factor() |>
+          forcats::fct_inseq()
+      )
+  )
+
+  viz_results <- visualize_experiment(
+    crossfit_experiment, fit_results, eval_results
+  )
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Estimated Subgroup CATEs
+
+```{r}
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::labs(
+        color = "# of Repeated\nCrossfits",
+        fill = "# of Repeated\nCrossfits"
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE",
+        color = "# of Repeated\nCrossfits",
+        fill = "# of Repeated\nCrossfits"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
       plt <- plt &
@@
     }
+    if (sim_name == sim_names[1]) {
       plt[[1]] <- plt[[1]] +
         ggplot2::labs(
-        tag = sprintf("(%s) %s", tag, sim_name)
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
       ) +
@@
         plot.tag.position = c(-.03, 0.48),
-        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.5), units = "in")
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
       )
@@
       ggplot2::theme(
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
-        ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
-        )
-      )
-      # ggplot2::theme(
-      #   plot.title = ggplot2::element_text(
-      #     size = 16, face = "bold", hjust = hjust
-      #   ),
-      #   plot.title.position = "plot"
-      # )
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
     return(plt)
@@
     tag = expression(
-      bold(paste("Proportion of Variance Explained in ", tau))
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
     )
@@
     ),
-    plot.tag.position = c(0.45, 0),
+    plot.tag.position = c(0.5, 0),
     plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
@@
 ggplot2::ggsave(
-  plt_subgroup, 
-  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_nreps_crossfit.pdf"),
   height = 9, 
@@
 )
-
-plt_subgroup_cov <- purrr::map2(
-  plt_subgroup_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name_orig <- names(plt_subgroup_ls[idx])
-    sim_name <- stringr::str_replace(
-      sim_name_orig, "with", "DGP with\n"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
-    if (sim_name_orig != names(plt_subgroup_ls[5])) {
+```
+
+### Thresholds Distances
+
+```{r}
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name),
+        y = "Average  | Estimated Threshold - True Threshold |",
+        x = expression(
+          bold(
+            paste("Proportion of Variance Explained in ", tau, " by Covariates")
+          )
+        ),
+        color = "# of Repeated\nCrossfits",
+        fill = "# of Repeated\nCrossfits"
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        ),
+        axis.title = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(size = 16),
+        strip.text = ggplot2::element_text(size = 14)
+      )
+    if (sim_name != sim_names[2]) {
+      plt <- plt +
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    if (stringr::str_detect(sim_name, "Linear")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.y = ggplot2::element_blank(),
+          plot.margin = ggplot2::unit(c(0, 0, 0.1, 0.2), units = "in")
+        )
+    } else {
+      plt <- plt +
+        ggplot2::theme(
+          plot.margin = ggplot2::unit(c(0, 0.2, 0.1, 0), units = "in")
+        )
+    }
+    if (!stringr::str_detect(sim_name, "OR")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_blank()
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, byrow = FALSE
+  ) +
+  patchwork::plot_layout(
+    axis_titles = "collect_y"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(
+    FIG_DIR, sprintf("sim_threshold_distances_nreps_crossfit.pdf")
+  ),
+  height = 9, 
+  width = 8 #14
+)
+```
+
+### Threshold Distributions
+
+```{r}
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = nreps_crossfit, 
+      y = raw_threshold,
+      fill = nreps_crossfit
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = nreps_crossfit, 
+      y = raw_threshold,
+      color = nreps_crossfit
+    )
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = CROSSFIT_COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name),
+        x = "# of Repeated Crossfits",
+        color = "# of Repeated\nCrossfits",
+        fill = "# of Repeated\nCrossfits"
+      ) +
+      ggplot2::theme(
+        axis.ticks.x = ggplot2::element_line(),
+        axis.title.x = ggplot2::element_text(size = 14, face = "bold"),
+        axis.text.x = ggplot2::element_text(size = 10),
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      ) +
+      ggplot2::guides(color = "none", fill = "none")
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1, guides = "collect"
+  ) +
+  patchwork::plot_layout(
+    axes = "collect"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_nreps_crossfit.pdf"),
+  height = 10, 
+  width = 10
+)
+```
+
+## Rulefit Simulations
+
+```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Rulefit Simulations")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP",
+  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
+  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
+  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
+  # fit_results <- readRDS(
+  #   file.path(
+  #     sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds"
+  #   )
+  # )
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
+    )
+  )
+  viz_results <- visualize_experiment(
+    rulefit_experiment, NULL, eval_results
+  )
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Estimated Subgroup CATEs
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (rulefit v1)",
+  "Distilled Causal Forest (rulefit v2)",
+  "Distilled Causal Forest (rulefit v3)",
+  "Distilled Causal Forest (rulefit v4)"
+)
+
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      rename_rulefit_methods()
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      rename_rulefit_methods()
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
       plt <- plt &
@@
         ),
-        plot.tag.position = c(-.06, 0.48),
-        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.75), units = "in")
+        plot.tag.position = c(-.03, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
       )
@@
     ),
+    plot.tag.position = c(0.5, 0),
+    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_rulefit.pdf"),
+  height = 9, 
+  width = 14
+)
+
+## with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      rename_rulefit_methods()
+    plt_selection <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup CATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      rename_rulefit_methods()
+    plt_cate <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::labs(
+        y = "CATE RMSE"
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_cate, nrow = 1, guides = "collect", widths = c(3.5, 1)
+    ) &
+      ggplot2::labs(x = NULL)
+
+    if (sim_name != sim_names[2]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+      hjust <- 0.78
+    } else {
+      hjust <- 0.82
+    }
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Selected Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Estimated Subgroup CATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.06, 0.48),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.75), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  ) |>
+  patchwork::wrap_elements() +
+  ggplot2::labs(
+    tag = expression(
+      bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+    )
+  ) +
+  ggplot2::theme(
+    plot.tag = ggplot2::element_text(
+      size = 16
+    ),
     plot.tag.position = c(0.45, 0),
@@
 ggplot2::ggsave(
-  plt_subgroup_cov, 
-  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov_rulefit.pdf"),
   height = 9, 
@@
 
+### Thresholds Distances
+
 ```{r}
-plt_thresholds <- purrr::map2(
-  plt_thresholds_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_thresholds_ls[idx])
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (rulefit v1)",
+  "Distilled Causal Forest (rulefit v2)",
+  "Distilled Causal Forest (rulefit v3)",
+  "Distilled Causal Forest (rulefit v4)"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
     tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      rename_rulefit_methods()
     plt <- plt +
-      ggplot2::labs(
-        title = sprintf("(%s) %s", tag, sim_name)
-      ) +
-      ggplot2::theme(
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name),
+        y = "Average  | Estimated Threshold - True Threshold |",
+        x = expression(
+          bold(
+            paste("Proportion of Variance Explained in ", tau, " by Covariates")
+          )
+        )
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
         plot.title = ggplot2::element_text(
@@
         ),
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
-        ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
+        axis.title = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(size = 16),
+        strip.text = ggplot2::element_text(size = 14)
+      )
+    if (sim_name != sim_names[5]) {
+      plt <- plt +
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    if (stringr::str_detect(sim_name, "Linear")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.y = ggplot2::element_blank(),
+          plot.margin = ggplot2::unit(c(0, 0, 0.1, 0.2), units = "in")
+        )
+    } else {
+      plt <- plt +
+        ggplot2::theme(
+          plot.margin = ggplot2::unit(c(0, 0.2, 0.1, 0), units = "in")
+        )
+    }
+    if (!stringr::str_detect(sim_name, "OR")) {
+      plt <- plt + 
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_blank()
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, byrow = FALSE
+  ) +
+  patchwork::plot_layout(
+    axis_titles = "collect_y"
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(
+    FIG_DIR, sprintf("sim_threshold_distances_rulefit.pdf")
+  ),
+  height = 9, 
+  width = 14
+)
+```
+
+### Threshold Distributions
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (rulefit v1)",
+  "Distilled Causal Forest (rulefit v2)",
+  "Distilled Causal Forest (rulefit v3)",
+  "Distilled Causal Forest (rulefit v4)"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
+    plt <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
         )
@@
 ggplot2::ggsave(
-  plt_thresholds, 
-  filename = file.path(FIG_DIR, "sim_thresholds.pdf"),
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_rulefit.pdf"),
   height = 10, 
@@
 
-plt_thresholds_cov <- purrr::map2(
-  plt_thresholds_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name <- stringr::str_replace(
-      names(plt_thresholds_ls[idx]), "with", "DGP with\n"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
     plt <- plt +
+      ggplot2::scale_color_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        values = RULEFIT_COLORS
+      ) +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
       ggplot2::labs(
@@
       ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
         plot.title = ggplot2::element_text(
           size = 18, face = "italic", hjust = 0.5
-        ),
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
-        ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
         )
@@
 ggplot2::ggsave(
-  plt_thresholds_cov, 
-  filename = file.path(FIG_DIR, "sim_thresholds_cov.pdf"),
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_cov_rulefit.pdf"),
   height = 10, 
@@
 
+### Number of Feature Splits Heatmap
+
 ```{r}
-# plt_ntrees_ls <- purrr::map(
-#   plt_freq_ls[1:3], ~ .x[[1]]
-# )
-# plt_nsplits_ls <- purrr::map(
-#   plt_freq_ls[1:3], ~ .x[[2]]
-# )
-# plt_ntrees <- patchwork::wrap_plots(
-#   plt_ntrees_ls, nrow = 1, guides = "collect"
-# ) +
-#   patchwork::plot_layout(
-#     axes = "collect"
-#   )
-
-plt_freq <- purrr::map2(
-  plt_freq_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_freq_ls[idx])
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (rulefit v1)",
+  "Distilled Causal Forest (rulefit v2)",
+  "Distilled Causal Forest (rulefit v3)",
+  "Distilled Causal Forest (rulefit v4)"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
     tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
+    plt_nsplits <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma"#, limits = c(0., 4.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
+    plt_ntrees <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      )
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
+      patchwork::plot_layout(
+        axis_titles = "collect_y"
+      ) &
+      ggplot2::labs(x = "Variable")
     plt <- patchwork::wrap_elements(plt) +
@@
 ggplot2::ggsave(
-  plt_freq, 
-  filename = file.path(FIG_DIR, "sim_freq.pdf"),
-  height = 16, 
-  width = 14
-)
-
-plt_freq_cov <- purrr::map2(
-  plt_freq_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name <- stringr::str_replace(
-      names(plt_freq_ls[idx]), "with", "DGP with"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq_rulefit.pdf"),
+  height = 17.5, 
+  width = 15
+)
+
+# with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Number of Splits Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
+    plt_nsplits <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma"#, limits = c(0., 4.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Number of Trees Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      rename_rulefit_methods()
+    plt_ntrees <- plt +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      viridis::scale_fill_viridis(
+        begin = 0.1, end = 1, option = "magma", limits = c(0, 100)
+      )
+
+    plt <- patchwork::wrap_plots(plt_ntrees, plt_nsplits, nrow = 1) +
+      patchwork::plot_layout(
+        axis_titles = "collect_y"
+      ) &
+      ggplot2::labs(x = "Variable")
     plt <- patchwork::wrap_elements(plt) +
@@
 ggplot2::ggsave(
-  plt_freq_cov, 
-  filename = file.path(FIG_DIR, "sim_freq_cov.pdf"),
-  height = 16, 
-  width = 14
+  plt, 
+  filename = file.path(FIG_DIR, "sim_freq_cov_rulefit.pdf"),
+  height = 17.5, 
+  width = 15
 )
 ```
-
-```{r}
-plt_stability <- purrr::map2(
-  plt_stability_ls, 1:length(plt_stability_ls),
-  function(plt, idx) {
-    plt_names <- names(plt_stability_ls)
-    sim_name <- dplyr::case_when(
-      stringr::str_detect(plt_names, "with") ~ 
-        stringr::str_replace(
-          plt_names, "with", "DGP with\n"
-        ) |> 
-        stringr::str_remove(" DGP$"),
-      TRUE ~ plt_names
-    )[idx]
-    tag <- LETTERS[idx]
-    plt_df <- plt$data |>
-      dplyr::mutate(
-        sim_name = sprintf("(%s) %s", tag, sim_name)
-      )
-    return(plt_df)
-  }
-) |>
-  purrr::list_rbind() |> 
-  dplyr::filter(
-    depth <= 4
-  )
-  ggplot2::ggplot() +
-  ggplot2::geom_line(
-    ggplot2::aes(
-      x = depth, y = mean_jaccard, color = .method_name
-    )
-  ) +
-  ggplot2::geom_ribbon(
-    ggplot2::aes(
-      x = depth,
-      ymin = mean_jaccard - se_jaccard,
-      ymax = mean_jaccard + se_jaccard,
-      fill = .method_name
-    ),
-    alpha = 0.2
-  ) +
-  ggplot2::facet_grid(sim_name ~ tau_heritability, labeller = signal_labeller) +
-  ggplot2::scale_color_manual(
-    breaks = KEEP_METHODS,
-    values = COLORS,
-    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-  ) +
-  ggplot2::scale_fill_manual(
-    breaks = KEEP_METHODS,
-    values = COLORS,
-    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-  ) +
-  ggplot2::coord_cartesian(xlim = c(1, 4)) +
-  ggplot2::scale_x_continuous(
-    breaks = 1:4
-  ) +
-  ggplot2::labs(
-    x = "Tree Depth",
-    y = "Mean Jaccard Stability",
-    color = "Method",
-    fill = "Method"
-  ) +
-  vthemes::theme_vmodern(
-    size_preset = "medium", grid_color = "grey98"
-  )
-ggplot2::ggsave(
-  plt_stability, 
-  filename = file.path(FIG_DIR, "sim_stability.pdf"),
-  height = 12, 
-  width = 11
-)
-```

### 2024-12-05 causalDT-manuscript/R/viz/visualizers.R

@@ -64,17 +64,6 @@ plot_subgroup_feature_selection_err <- function(fit_results = NULL,
       axis.title.y = ggplot2::element_blank()
     )
 
-  # if (!is.null(vary_params)) {
-  #   if (identical(vary_params, "tau_heritability")) {
-  #     plt <- plt +
-  #       ggplot2::labs(
-  #         x = expression(
-  #           bold(paste("Proportion of Variance Explained in ", tau))
-  #         )
-  #       )
-  #   }
-  # }
-
   return(plt)
 }
 
@@ -84,6 +73,7 @@ plot_subgroup_thresholds <- function(fit_results = NULL,
                                      vary_params = NULL,
                                      eval_name = "Thresholds Summary",
                                      feature_col = ".var",
+                                     x_str = ".method_name",
                                      rm_methods = c("Linear Regression", "Lasso"),
                                      method_levels = NULL,
                                      show = c("violin", "boxplot"),
@@ -112,6 +102,21 @@ plot_subgroup_thresholds <- function(fit_results = NULL,
     )
 
   if (identical(show, "dotplot")) {
+    if (length(vary_params) == 1) {
+      facet_layer <- ggplot2::facet_grid(
+        rows = ggplot2::vars(!!rlang::sym(vary_params)),
+        cols = ggplot2::vars(!!rlang::sym(feature_col))
+      )
+    } else if (length(vary_params) > 1) {
+      facet_layer <- ggplot2::facet_grid(
+        rows = ggplot2::vars(!!!rlang::syms(vary_params)),
+        cols = ggplot2::vars(!!rlang::sym(feature_col))
+      )
+    } else {
+      facet_layer <- ggplot2::facet_wrap(
+        ggplot2::vars(!!rlang::sym(feature_col))
+      )
+    }
     plt <- plt_df |>
       ggplot2::ggplot() +
       ggplot2::aes(
@@ -119,10 +124,7 @@ plot_subgroup_thresholds <- function(fit_results = NULL,
         y = raw_threshold,
         fill = .method_name
       ) +
-      ggplot2::facet_grid(
-        rows = ggplot2::vars(!!rlang::sym(vary_params)),
[…]

### 2024-12-05 causalDT-manuscript/meals/shared_experiments.R

@@ -103,20 +103,27 @@ crossfit_experiment <- create_experiment(
       # distilled_rlasso_crossfit_method$name
     ),
     nreps_crossfit = c(1, 5, 10, 20, 50, 100)
-  )
+  ) |>
+  ### evaluators
+  add_evaluator(subgroup_feature_selection_errors_summary) |>
+  add_evaluator(subgroup_thresholds_summary) |>
+  add_evaluator(subgroup_threshold_dist_summary) |>
+  add_evaluator(subgroup_cate_err_summary) |>
+  ### visualizers
+  add_visualizer(subgroup_feature_selection_err_crossfit_plot) |>
+  add_visualizer(subgroup_thresholds_crossfit_plot) |>
+  add_visualizer(subgroup_threshold_dist_crossfit_plot) |>
+  add_visualizer(subgroup_cates_err_crossfit_plot)
 
 rwd_experiment <- create_experiment(
   name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods
-  add_method(distilled_causal_forest_stability_method) |>
-  add_method(distilled_rboost_stability_method) |>
-  add_method(distilled_rboost_no_crossfit_stability_method) |>
-  add_method(distilled_rlasso_stability_method) |>
-  add_method(distilled_rlasso_no_crossfit_stability_method) |>
+  add_method(distilled_causal_forest_stability_pruned_method) |>
+  add_method(distilled_rboost_stability_pruned_method) |>
+  # add_method(distilled_rlasso_stability_method) |>
   ### baseline causal tree methods
-  add_method(causal_tree_stability_method) |>
-  add_method(causal_tree_unpruned_stability_method) |>
+  add_method(causal_tree_stability_pruned_method) |>
   ### other existing methods
   add_method(virtual_twins_method) |>
   add_method(lm_method) |>
@@ -127,7 +134,7 @@ rwd_experiment <- create_experiment(
   add_visualizer(subgroup_thresholds_plot) |>
   add_visualizer(subgroup_nsplits_plot) |>
   add_visualizer(subgroup_ntrees_plot) |>
-  add_visualizer(subgroup_cates_plot) |>
+  # add_visualizer(subgroup_cates_plot) |>
   add_visualizer(subgroup_stability_plot)
 
 theory_experiment <- create_experiment(

### 2024-12-05 causalDT-manuscript/meals/shared_visualizers.R

@@ -52,12 +52,15 @@ subgroup_feature_selection_err_max_depth2_plot <- create_visualizer(
     size = 0.7
   )
 )
-subgroup_feature_selection_err_max_depth3_plot <- create_visualizer(
+
+subgroup_feature_selection_err_crossfit_plot <- create_visualizer(
   .viz_fun = plot_subgroup_feature_selection_err,
-  .name = "Subgroup Feature Selection Errors Plot (max depth = 3)",
-  eval_name = "Subgroup Feature Selection Errors Summary (max depth = 3)",
-  show = c("point", "line", "ribbon"),
+  .name = "Subgroup Feature Selection Errors Plot",
+  show = c("point", "line"),#, "ribbon"),
   err_sd_str = "se_feature_selection_err",
+  x_str = "tau_heritability",
+  color_str = "nreps_crossfit",
+  plot_by = NULL,
   ribbon_args = list(
     alpha = 0.2
   ),
@@ -65,19 +68,7 @@ subgroup_feature_selection_err_max_depth3_plot <- create_visualizer(
     size = 0.7
   )
 )
-subgroup_feature_selection_err_max_depth4_plot <- create_visualizer(
-  .viz_fun = plot_subgroup_feature_selection_err,
-  .name = "Subgroup Feature Selection Errors Plot (max depth = 4)",
-  eval_name = "Subgroup Feature Selection Errors Summary (max depth = 4)",
-  show = c("point", "line", "ribbon"),
-  err_sd_str = "se_feature_selection_err",
-  ribbon_args = list(
-    alpha = 0.2
-  ),
-  line_args = list(
-    size = 0.7
-  )
-)
+
 
 subgroup_thresholds_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
@@ -93,17 +84,10 @@ subgroup_thresholds_max_depth2_plot <- create_visualizer(
   method_levels = method_levels,
   size_preset = "medium"
 )
-subgroup_thresholds_max_depth3_plot <- create_visualizer(
+
+subgroup_thresholds_crossfit_plot <- create_visualizer(
   .viz_fun = plot_subgroup_thresholds,
-  .name = "Subgroup Thresholds Distribution Plot (max depth = 3)",
-  eval_name = "Thresholds Summary (max depth = 3)",
-  method_levels = method_levels,
-  size_preset = "medium"
-)
[…]

### 2024-12-05 causalDT-manuscript/meals/01b_or_subgroup.R
update simulation scripts

@@ -1,5 +1,5 @@
 rm(list = ls())
-EXP_NAME <- "Unbiased W"
+EXP_NAME <- "Main Simulations"
 N_REPS <- 100
 SAVE <- TRUE
 # USE_CACHED <- FALSE
@@ -10,11 +10,11 @@ set.seed(331)
 source(here::here(file.path("meals", "setup.R")))
 N_REPS <- 100
 
-# #### Cluster setup for parallelization (or comment out) ####
-# # n_workers <- min(N_REPS, availableCores() - 1)
-# n_workers <- 8
-# # n_workers <- 2
-# plan(multisession, workers = n_workers)
+#### Cluster setup for parallelization (or comment out) ####
+# n_workers <- min(N_REPS, availableCores() - 1)
+n_workers <- 8
+# n_workers <- 2
+plan(multisession, workers = n_workers)
 
 #### DGPs ####
 
@@ -47,16 +47,4 @@ out <- run_experiment(
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
 
-# fit_results <- get_cached_results(experiment, "fit")
-# eval_results <- get_cached_results(experiment, "eval")
-# viz_results <- visualize_experiment(experiment, fit_results, eval_results)
-# plotly::ggplotly(viz_results$`Subgroup Feature Selection Errors Plot`)
-# plotly::ggplotly(viz_results$`Subgroup CATE Errors Plot`)
-# viz_results$`Subgroup Thresholds Distribution Plot`
-# viz_results$`Number of Splits Plot`
-# viz_results$`Number of Trees Plot`
-# viz_results$`Subgroup CATEs Plot`
-# viz_results$`Subgroup Stability Diagnostics Plot`
-
 render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
-

### 2024-12-05 causalDT-manuscript/meals/02a_and_subgroup_vary_crossfit.R

@@ -1,5 +1,5 @@
 rm(list = ls())
-EXP_NAME <- "Main Simulations"
+EXP_NAME <- "Varying nrep crossfits"
 N_REPS <- 100
 SAVE <- TRUE
 # USE_CACHED <- FALSE
@@ -33,18 +33,18 @@ dgp <- gaussian_X_unbiased_Z_and
 print(dgp$name)
 
 source(here::here(file.path("meals", "shared_experiments.R")))
-experiment <- experiment |>
+crossfit_experiment <- crossfit_experiment |>
   add_dgp(dgp) |>
   add_vary_across(
     .dgp = dgp$name,
     tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
   )
-# out <- run_experiment(experiment)
+# out <- run_experiment(crossfit_experiment)
 out <- run_experiment(
-  experiment, n_reps = N_REPS, save = SAVE,
+  crossfit_experiment, n_reps = N_REPS, save = SAVE,
   use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
 
-render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
+render_docs(save_dir = file.path(crossfit_experiment$get_save_dir(), dgp$name))
 

### 2024-12-05 causalDT-manuscript/meals/02b_or_subgroup_vary_crossfit.R

@@ -1,5 +1,5 @@
 rm(list = ls())
-EXP_NAME <- "Main Simulations"
+EXP_NAME <- "Varying nrep crossfits"
 N_REPS <- 100
 SAVE <- TRUE
 # USE_CACHED <- FALSE
@@ -29,22 +29,22 @@ source(here::here(file.path("meals", "shared_evaluators.R")))
 source(here::here(file.path("meals", "shared_visualizers.R")))
 
 #### Run Experiment ####
-dgp <- gaussian_X_unbiased_Z_and
+dgp <- gaussian_X_unbiased_Z_or
 print(dgp$name)
 
 source(here::here(file.path("meals", "shared_experiments.R")))
-experiment <- experiment |>
+crossfit_experiment <- crossfit_experiment |>
   add_dgp(dgp) |>
   add_vary_across(
     .dgp = dgp$name,
     tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
   )
-# out <- run_experiment(experiment)
+# out <- run_experiment(crossfit_experiment)
 out <- run_experiment(
-  experiment, n_reps = N_REPS, save = SAVE,
+  crossfit_experiment, n_reps = N_REPS, save = SAVE,
   use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
 
-render_docs(save_dir = file.path(experiment$get_save_dir(), dgp$name))
+render_docs(save_dir = file.path(crossfit_experiment$get_save_dir(), dgp$name))
 

### 2024-12-05 causalDT-manuscript/meals/03_varying_n.R

@@ -1,0 +1,58 @@
+rm(list = ls())
+EXP_NAME <- "Main Simulations"
+N_REPS <- 100
+SAVE <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
+CHECKPOINT_N_REPS <- 0
+set.seed(331)
+
+source(here::here(file.path("meals", "setup.R")))
+N_REPS <- 100
+
+#### Cluster setup for parallelization (or comment out) ####
+# n_workers <- min(N_REPS, availableCores() - 1)
+n_workers <- 8
+plan(multisession, workers = n_workers)
+
+#### DGPs ####
+
+source(here::here(file.path("meals", "shared_dgps.R")))
+
+#### Methods ####
+
+source(here::here(file.path("meals", "shared_methods.R")))
+
+#### Evaluators and Visualizers ####
+
+source(here::here(file.path("meals", "shared_evaluators.R")))
+source(here::here(file.path("meals", "shared_visualizers.R")))
+
+#### Run Experiment ####
+dgps <- list(
+  gaussian_X_unbiased_Z_and,
+  gaussian_X_unbiased_Z_or,
+  gaussian_X_unbiased_Z_additive,
+  gaussian_X_unbiased_Z_and_cov,
+  gaussian_X_unbiased_Z_or_cov,
+  gaussian_X_unbiased_Z_additive_cov
+)
+for (dgp in dgps) {
+  print(dgp$name)
+  source(here::here(file.path("meals", "shared_experiments.R")))
+  example_experiment <- example_experiment |>
+    add_dgp(dgp) |>
+    add_vary_across(
+      .dgp = dgp$name,
+      n = c(100, 500, 1000, 2000)
+    )
+  # out <- run_experiment(example_experiment)
+  out <- run_experiment(
+    example_experiment, n_reps = N_REPS, save = SAVE,
+    use_cached = USE_CACHED, checkpoint_n_reps = CHECKPOINT_N_REPS,
+    future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
+  )
+}
+
+render_docs(save_dir = example_experiment$get_save_dir())
+

### 2024-12-05 causalDT-manuscript/meals/05_case_study_aids.R

@@ -2,18 +2,18 @@ rm(list = ls())
 EXP_NAME <- "AIDS"
 N_REPS <- 100
 SAVE <- TRUE
-USE_CACHED <- FALSE
-# USE_CACHED <- TRUE
+# USE_CACHED <- FALSE
+USE_CACHED <- TRUE
 CHECKPOINT_N_REPS <- 0
 set.seed(331)
 
 source(here::here(file.path("meals", "setup.R")))
 N_REPS <- 100
 
-# #### Cluster setup for parallelization (or comment out) ####
-# # n_workers <- min(N_REPS, availableCores() - 1)
-# n_workers <- 8
-# plan(multisession, workers = n_workers)
+#### Cluster setup for parallelization (or comment out) ####
+# n_workers <- min(N_REPS, availableCores() - 1)
+n_workers <- 8
+plan(multisession, workers = n_workers)
 
 #### DGPs ####
 
@@ -33,12 +33,9 @@ dgp <- aids_dgp
 print(dgp$name)
 
 source(here::here(file.path("meals", "shared_experiments.R")))
+
 rwd_experiment <- rwd_experiment |>
-  add_dgp(dgp) #|>
-  # add_vary_across(
-  #   .dgp = dgp$name,
-  #   subsample = c(100, 200, 300, 400, 500, 600, 792) / 792
-  # )
+  add_dgp(dgp)
 # out <- run_experiment(rwd_experiment)
 out <- run_experiment(
   rwd_experiment, n_reps = N_REPS, save = SAVE,
@@ -46,98 +43,18 @@ out <- run_experiment(
   future.globals = FUTURE_GLOBALS, future.packages = FUTURE_PACKAGES
 )
 
-keep_methods <- c(
-  "Causal Tree (pruned)",
-  "Causal Tree (unpruned)",
-  "Distilled Causal Forest",
-  "Distilled Rboost",
-  "Distilled Rlasso",
-  "Lasso",
-  "Linear Regression",
-  "Virtual Twins"
-)
-fit_results <- get_cached_results(rwd_experiment, "fit") |>
-  dplyr::filter(
-    .method_name %in% !!keep_methods
-  )
-# eval_results <- get_cached_results(rwd_experiment, "eval")
-eval_results <- evaluate_experiment(rwd_experiment, fit_results)
-# eval_results <- evaluate_experiment(rwd_experiment, fit_results, save = TRUE)
-viz_results <- visualize_experiment(rwd_experiment, fit_results, eval_results)
[…]

### 2024-12-05 causalDT-manuscript/R/method/methods.R
bug fix in group cates

@@ -96,7 +96,15 @@ causalDT_method <- function(X, Y, Z,
     subgroups_ls[[rpart_prune[1]]] <- results$student_fit$subgroups
     tree_info_ls[[rpart_prune[1]]] <- results$student_fit$tree_info
     predictions_ls[[rpart_prune[1]]] <- results$student_fit$predictions
-    group_cates_ls[[rpart_prune[1]]] <- results$estimate
+    if (!(identical(student_model, "rpart"))) {
+      group_cates_ls[[rpart_prune[1]]] <- tibble::tibble(
+        leaf_id = 1:nrow(X_est),
+        estimate = predict(results$student_fit$fit, data.frame(X_est)),
+        .sample_idxs = purrr::map(1:nrow(X_est), ~ .x)
+      )
+    } else {
+      group_cates_ls[[rpart_prune[1]]] <- results$estimate
+    }
   }
   end_time <- Sys.time()
 

### 2024-12-05 causalDT-manuscript/meals/shared_experiments.R
update shared experiments

@@ -36,55 +36,6 @@ experiment <- create_experiment(
   add_visualizer(subgroup_cates_err_max_depth2_plot) |>
   add_visualizer(subgroup_stability_plot)
 
-old_experiment <- create_experiment(
-  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
-) |>
-  ### distillation methods
-  add_method(distilled_causal_forest_stability_method) |>
-  add_method(distilled_rboost_stability_method) |>
-  add_method(distilled_rboost_no_crossfit_stability_method) |>
-  add_method(distilled_rlasso_stability_method) |>
-  add_method(distilled_rlasso_no_crossfit_stability_method) |>
-  ### baseline causal tree methods
-  add_method(causal_tree_stability_method) |>
-  add_method(causal_tree_unpruned_stability_method) |>
-  ### other existing methods
-  add_method(virtual_twins_method) |>
-  add_method(lm_method) |>
-  add_method(lasso_method) |>
-  ### evaluators
-  add_evaluator(subgroup_feature_selection_errors_summary) |>
-  add_evaluator(subgroup_feature_selection_errors_max_depth2_summary) |>
-  add_evaluator(subgroup_feature_selection_errors_max_depth3_summary) |>
-  add_evaluator(subgroup_feature_selection_errors_max_depth4_summary) |>
-  add_evaluator(subgroup_thresholds_summary) |>
-  add_evaluator(subgroup_thresholds_max_depth2_summary) |>
-  add_evaluator(subgroup_thresholds_max_depth3_summary) |>
-  add_evaluator(subgroup_thresholds_max_depth4_summary) |>
-  add_evaluator(subgroup_threshold_dist_summary) |>
-  add_evaluator(subgroup_threshold_dist_max_depth2_summary) |>
-  add_evaluator(subgroup_threshold_dist_max_depth3_summary) |>
-  add_evaluator(subgroup_threshold_dist_max_depth4_summary) |>
-  add_evaluator(subgroup_cate_err_summary) |>
-  ### visualizers
-  add_visualizer(subgroup_feature_selection_err_plot) |>
-  add_visualizer(subgroup_feature_selection_err_max_depth2_plot) |>
-  add_visualizer(subgroup_feature_selection_err_max_depth3_plot) |>
[…]

### 2025-02-12 causalDT/R/RcppExports.R
clean up jaccard ssi code

@@ -1,11 +1,7 @@
 # Generated by using Rcpp::compileAttributes() -> do not edit by hand
 # Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
 
-jaccardCPP <- function(x, y) {
-    .Call(`_causalDT_jaccardCPP`, x, y)
-}
-
-jaccardScaledCPP <- function(x, y) {
-    .Call(`_causalDT_jaccardScaledCPP`, x, y)
+jaccardSSI <- function(x, y) {
+    .Call(`_causalDT_jaccardSSI`, x, y)
 }
 

### 2025-02-12 causalDT/R/diagnostics-stability.R

@@ -106,7 +106,6 @@ evaluate_subgroup_stability <- function(estimator, fit, X, y, Z = NULL,
   node_depths <- purrr::map(bootstrap_out, "node_depths")
 
   Js <- list()
-  Js_scaled <- list()
   preds_mean <- list()
   preds_var <- list()
   for (n_depth in 1:max_depth) {
@@ -152,21 +151,12 @@ evaluate_subgroup_stability <- function(estimator, fit, X, y, Z = NULL,
 
     J <- purrr::map_dbl(
       1:floor(length(bootstrap_fits) / 2),
-      ~ jaccardCPP(
-        bootstrap_leaf_ids[[.x * 2 - 1]],
-        bootstrap_leaf_ids[[.x * 2]]
-      )
-    )
-    Js[[n_depth]] <- J
-
-    J_scaled <- purrr::map_dbl(
-      1:floor(length(bootstrap_fits) / 2),
-      ~ jaccardScaledCPP(
+      ~ jaccardSSI(
         as.numeric(as.factor(bootstrap_leaf_ids[[.x * 2 - 1]])) - 1,
         as.numeric(as.factor(bootstrap_leaf_ids[[.x * 2]])) - 1
       )
     )
-    Js_scaled[[n_depth]] <- J_scaled
+    Js[[n_depth]] <- J
 
     preds_mean[[n_depth]] <- do.call(cbind, bootstrap_leaf_preds) |>
       rowMeans()
@@ -190,8 +180,6 @@ evaluate_subgroup_stability <- function(estimator, fit, X, y, Z = NULL,
   out <- list(
     "jaccard_mean" = sapply(Js, mean),
     "jaccard_distribution" = Js,
-    "jaccard_scaled_mean" = sapply(Js_scaled, mean),
-    "jaccard_scaled_distribution" = Js_scaled,
     "feature_distribution" = feature_dist,
     "bootstrap_predictions_mean" = preds_mean,
     "bootstrap_predictions_var" = preds_var,

### 2025-02-12 causalDT/src/RcppExports.cpp

@@ -11,34 +11,21 @@ Rcpp::Rostream<true>&  Rcpp::Rcout = Rcpp::Rcpp_cout_get();
 Rcpp::Rostream<false>& Rcpp::Rcerr = Rcpp::Rcpp_cerr_get();
 #endif
 
-// jaccardCPP
-double jaccardCPP(NumericVector x, NumericVector y);
-RcppExport SEXP _causalDT_jaccardCPP(SEXP xSEXP, SEXP ySEXP) {
+// jaccardSSI
+double jaccardSSI(NumericVector x, NumericVector y);
+RcppExport SEXP _causalDT_jaccardSSI(SEXP xSEXP, SEXP ySEXP) {
 BEGIN_RCPP
     Rcpp::RObject rcpp_result_gen;
     Rcpp::RNGScope rcpp_rngScope_gen;
     Rcpp::traits::input_parameter< NumericVector >::type x(xSEXP);
     Rcpp::traits::input_parameter< NumericVector >::type y(ySEXP);
-    rcpp_result_gen = Rcpp::wrap(jaccardCPP(x, y));
-    return rcpp_result_gen;
-END_RCPP
-}
-// jaccardScaledCPP
-double jaccardScaledCPP(NumericVector x, NumericVector y);
-RcppExport SEXP _causalDT_jaccardScaledCPP(SEXP xSEXP, SEXP ySEXP) {
-BEGIN_RCPP
-    Rcpp::RObject rcpp_result_gen;
-    Rcpp::RNGScope rcpp_rngScope_gen;
-    Rcpp::traits::input_parameter< NumericVector >::type x(xSEXP);
-    Rcpp::traits::input_parameter< NumericVector >::type y(ySEXP);
-    rcpp_result_gen = Rcpp::wrap(jaccardScaledCPP(x, y));
+    rcpp_result_gen = Rcpp::wrap(jaccardSSI(x, y));
     return rcpp_result_gen;
 END_RCPP
 }
 
 static const R_CallMethodDef CallEntries[] = {
-    {"_causalDT_jaccardCPP", (DL_FUNC) &_causalDT_jaccardCPP, 2},
-    {"_causalDT_jaccardScaledCPP", (DL_FUNC) &_causalDT_jaccardScaledCPP, 2},
+    {"_causalDT_jaccardSSI", (DL_FUNC) &_causalDT_jaccardSSI, 2},
     {NULL, NULL, 0}
 };
 

### 2025-02-12 causalDT/src/stability.cpp

@@ -1,63 +1,22 @@
 #include <Rcpp.h>
 using namespace Rcpp;
 
-//' Jaccard similarity index
+//' Jaccard subgroup similarity index
 //'
 //' @description
 //' This function computes the Jaccard similarity index between two vectors of
-//' cluster membership labels.
-//'
-//' @param x Numeric vector of cluster memberships (encoded as integers).
-//' @param y Numeric vector of cluster memberships (encoded as integers).
-//'
-//' @return Computed Jaccard similarity metric according to Ben-Hur (2001).
-//'
-//' @export
-// [[Rcpp::depends(RcppArmadillo)]]
-// [[Rcpp::export]]
-double jaccardCPP(NumericVector x, NumericVector y) {
-  // length of x vector; number of samples
-  int n = x.size();
-
-  // initialize jaccard output
-  double jaccard = 0.0;
-
-  // initialize 2x2 N matrix where N = [N_00, N_01; N_10, N_11]
-  NumericMatrix N(2);
-  N(0, 0) = n; // accounting for diagonal elements being 0's a priori
-  // compute N matrix (for details see Ben-Hur 2001)
-  for (int i = 0; i < n; i++) {   // for each row of sim_mat
-    for (int j = i+1; j < n; j++) { // for each column, but for efficiency,
-      // use symmetry & no need to check diagonals
-      int Cx_ij = x[i] == x[j];
-      int Cy_ij = y[i] == y[j];
-      N(Cx_ij, Cy_ij) += 2; // because of symmetry
-    }
-  }
-
-  jaccard = N(1, 1) / (N(0, 1) + N(1, 0) + N(1, 1));
-  return jaccard;
-}
-
-
-//' Scaled Jaccard similarity index
-//'
-//' @description
-//' This function computes the Jaccard similarity index between two vectors of
-//' cluster membership labels, scaling it such that each leaf node contributes
+//' subgroup membership labels, scaling it such that each leaf node contributes
 //' equal weight to the overall similarity.
 //'
-//' @param x Numeric vector of cluster memberships (encoded as integers).
-//' @param y Numeric vector of cluster memberships (encoded as integers).
+//' @param x Numeric vector of subgroup memberships (encoded as integers).
+//' @param y Numeric vector of subgroup memberships (encoded as integers).
 //'
-//' @return Computed Jaccard similarity metric according to Ben-Hur (2001),
[…]

### 2025-02-12 causalDT-manuscript/notebooks/paper_figures.Rmd
clean up figures

--- 2024-09-10 causalDT-manuscript/notebooks/paper_figures.Rmd
@@
 
-KEEP_METHODS <- c(
-  "Distilled Causal Forest",
-  "Distilled Rboost",
-  "Distilled Rlasso",
-  "Virtual Twins",
-  "Causal Tree (pruned)",
-  "Causal Tree (unpruned)",
-  "Linear Regression",
-  "Lasso"
-)
 COLORS <- c(
-  # "Distilled Causal Forest" = "#3153A5",
   "Distilled Causal Forest" = "#1f5d8f",
-  # "Distilled Causal Forest" = "#5d8cae",
-  # "Distilled Rboost" = "#94B1c9",
-  # "Distilled Rboost" = "#678096",
-  ## "Distilled Rboost" = "#79b2dd",
   "Distilled Rboost" = "#6aafe4",
-  # "Distilled Rboost" = "#6DA7D3",
-  # "Distilled Rboost" = "#6DA7D3",
-  # "Distilled Rlasso" = "#ACC2D0",
-  "Distilled Rlasso" = "#9ab6c8",
-  # "Distilled Rlasso" = "#B8CEDD",
   "Virtual Twins" = "#768c50",
-  # "Virtual Twins" = "#6F9940",
-  "Causal Tree (pruned)" = "#953a2f",
-  "Causal Tree (unpruned)" = "#DB9685",
-  # "Linear Regression" = "#DAA520",
+  "Causal Tree" = "#953a2f",
   "Linear Regression" = "#b2954a",
   "Lasso" = "#D2BE90"
-  # "Lasso" = "#e4d2a4"
+)
+CROSSFIT_COLORS <- c(
+  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
+)
+RULEFIT_COLORS <- c(
+  "CART" = "#1f5d8f",
+  "Rulefit (linear + rules, max depth = 3)" = "#FF9300",
+  "Rulefit (linear + rules, max depth = 2)" = "#E7298A",
+  "Rulefit (rules only, max depth = 3)" = "#66A61E",
+  "Rulefit (rules only, max depth = 2)" = "#7570B3"
+)
+LINE_TYPES <- c(
+  "Pruned" = "solid",
+  "Unpruned" = "dashed"
 )
@@
   }
+}
+
+add_pruned_column <- function(data) {
+  data |> 
+    dplyr::mutate(
+      .is_pruned = dplyr::case_when(
+        stringr::str_detect(.method_name, "unpruned") ~ "Unpruned",
+        TRUE ~ "Pruned"
+      ),
+      .method_name = stringr::str_remove(.method_name, " \\(unpruned\\)")
+    )
 }
@@
   )
+
+example_experiment <- example_experiment |>
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    n = c(100, 500, 1000, 2000)
+  )
+
+crossfit_experiment <- crossfit_experiment |>
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+  )
+
+rulefit_experiment <- rulefit_experiment |> 
+  add_dgp(gaussian_X_unbiased_Z_and) |>
+  add_vary_across(
+    .dgp = gaussian_X_unbiased_Z_and$name,
+    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
+  )
 ```
 
+## Example {.tabset .tabset-pills .tabset-pills-square}
+
 ```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Main Simulations")
+)
 sim_names <- c(
@@
 )
+
+keep_methods_ls <- list(
+  "causal_tree_only" = c("Causal Tree"),
+  "all_methods" = c("Distilled Causal Forest", "Causal Tree")
+)
+
+for (keep_methods_idx in 1:length(keep_methods_ls)) {
+  keep_methods <- keep_methods_ls[[keep_methods_idx]]
+  keep_methods_name <- names(keep_methods_ls)[keep_methods_idx]
+  for (sim_name in sim_names) {
+    fit_results <- readRDS(
+      file.path(
+        sim_results_dir, sim_name, "Varying n", "fit_results.rds"
+      )
+    )
+    eval_results <- readRDS(
+      file.path(
+        sim_results_dir, sim_name, "Varying n", "eval_results.rds"
+      )
+    )
+    viz_results <- visualize_experiment(
+      example_experiment, fit_results, eval_results
+    )
+
+    plt <- viz_results$`Number of Subgroups Plot`
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% !!keep_methods
+      )
+    plt <- plt +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98")
+      )
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR, 
+        sprintf("sim_example_nsubgroup_%s.pdf", keep_methods_name)
+      ),
+      height = 3.1,
+      width = 11.5
+    )
+  }
+}
+```
+
+## Main Simulations {.tabset .tabset-pills .tabset-pills-square}
+
+```{r results = "asis"}
 sim_results_dir <- here::here(
-  file.path("results", "Unbiased W")
-)
-
-plt_subgroup_ls <- list()
-plt_subgroup2_ls <- list()
-plt_thresholds_ls <- list()
-plt_stability_ls <- list()
-plt_freq_ls <- list()
-for (sim_name in sim_names) {
-  cat(sprintf("\n\n## %s {.tabset .tabset-pills .tabset-square}\n\n", sim_name))
-
-  # fit_results <- readRDS(
-  #   file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
-  # ) |>
-  #   dplyr::filter(
-  #     .method_name %in% !!KEEP_METHODS
-  #   )
-  # eval_results <- evaluate_experiment(experiment, fit_results)
-  # viz_results <- visualize_experiment(experiment, fit_results, eval_results)
-  # 
-  # plt_selection <- viz_results$`Subgroup Feature Selection Errors Plot` +
-  #   ggplot2::scale_color_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::scale_fill_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   )
-  # 
-  # plt_cate <- viz_results$`Subgroup CATE Errors Plot` +
-  #   ggplot2::scale_color_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::scale_fill_manual(
-  #     breaks = KEEP_METHODS,
-  #     values = COLORS
-  #   ) +
-  #   ggplot2::labs(
-  #     y = "CATE RMSE"
-  #   ) +
-  #   vthemes::theme_vmodern(
-  #     axis_title_size = 16,
-  #     axis_text_size = 12,
-  #     legend_title_size = 16,
-  #     legend_text_size = 12
-  #   ) +
-  #   ggplot2::theme(
-  #     strip.background = ggplot2::element_blank(),
-  #     strip.placement = "outside"
-  #     # strip.background = ggplot2::element_rect(
-  #     #   color = "transparent", fill = "transparent"
-  #     # ),
-  #     # strip.text = ggplot2::element_text(
-  #     #   color = "black", face = "bold", size = 16
-  #     # )
-  #   ) +
-  #   ggplot2::guides(
-  #     color = "none", fill = "none"
-  #   )
-  # 
-  # pplt <- patchwork::wrap_plots(
-  #   plt_selection, plt_cate, nrow = 1, guides = "collect",
-  #   widths = c(3.5, 1)
-  # ) &
-  #   ggplot2::labs(x = NULL)
-  # plt_subgroup_ls[[sim_name]] <- pplt
-  # plt <- patchwork::wrap_elements(pplt) +
-  #   ggplot2::labs(
-  #     tag = expression(
-  #       bold(paste("Proportion of Variance Explained in ", tau))
-  #     )
-  #   ) +
-  #   ggplot2::theme(
-  #     plot.tag = ggplot2::element_text(
-  #       size = 16
-  #     ),
-  #     plot.tag.position = c(0.45, 0),
-  #     plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
-  #   )
-  # plt_subgroup2_ls[[sim_name]] <- plt
-
+  file.path("results", "Main Simulations")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP",
+  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
+  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
+  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
   fit_results <- readRDS(
-    file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds"
+    )
+  )
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
+    )
+  )
+  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+## without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X1"
+      )
+    plt_thr1 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X2"
+      )
+    plt_thr2 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
+    ) &
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[3]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[3] ~ 0.66
+    )
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.03, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
+        ),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[3]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
+        )
+    }
+    return(plt)
+  }
 ) |>
-    dplyr::filter(
-      .method_name %in% !!KEEP_METHODS,
-      tau_heritability %in% c(0.2, 0.6, 1)
-    )
-  eval_results <- evaluate_experiment(experiment, fit_results)
-  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
-
-  plt_thresholds <- viz_results$`Subgroup Thresholds Distribution Plot` +
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
+  height = 9.5, 
+  width = 15
+)
+
+## with covariates
+sim_names <- c(
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X1"
+      )
+    plt_thr1 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X2"
+      )
+    plt_thr2 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
+    ) &
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[3]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[3] ~ 0.66
+    )
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(-.08, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
+        ),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[3]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
+  height = 9.5, 
+  width = 15
+)
+```
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Causal Tree",
+  "Causal Tree (unpruned)"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_feature_selection_err - se_feature_selection_err,
+      ymax = mean_feature_selection_err + se_feature_selection_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_feature_selection_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt_selection <- plt +
+      ggplot2::scale_linetype_manual(
+        values = LINE_TYPES
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_ate_err - se_ate_err,
+      ymax = mean_ate_err + se_ate_err,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_ate_err,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt_cate <- plt +
+      ggplot2::scale_linetype_manual(
+        values = LINE_TYPES
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X1"
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_threshold_dist - se_threshold_dist,
+      ymax = mean_threshold_dist + se_threshold_dist,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_threshold_dist,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt_thr1 <- plt +
+      ggplot2::scale_linetype_manual(
+        values = LINE_TYPES
+      ) +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X2"
+      ) |> 
+      add_pruned_column()
+    plt$layers[[1]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      ymin = mean_threshold_dist - se_threshold_dist,
+      ymax = mean_threshold_dist + se_threshold_dist,
+      fill = .method_name,
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt$layers[[2]]$mapping <- ggplot2::aes(
+      x = tau_heritability, 
+      y = mean_threshold_dist,
+      color = .method_name,
+      linetype = .is_pruned, 
+      group = interaction(.method_name, .is_pruned)
+    )
+    plt_thr2 <- plt +
+      ggplot2::scale_linetype_manual(
+        values = LINE_TYPES
+      ) +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
+    ) &
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[length(sim_names)]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none", linetype = "none"
+        )
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[6] ~ 0.6,
+      TRUE ~ 0.5
+    )
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs"
+        )
+    }
+    if (stringr::str_detect(sim_name, "with")) {
+      tag_x_pos <- -.08
+    } else {
+      tag_x_pos <- -.03
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(tag_x_pos, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      ) &
+      ggplot2::labs(linetype = "Pruning Mode")
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
+        ),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[length(sim_names)]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.9, vjust = -1.25)
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_with_pruning.pdf"),
+  height = 17, 
+  width = 14
+)
+```
+
+### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs (max depth = 2)
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot (max depth = 2)`
+    linear_data <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |> 
+      dplyr::filter(
+        .method_name %in% c("Linear Regression", "Lasso")
+      )
+    plt$data <- plt$data |>
+      dplyr::bind_rows(linear_data) |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X1"
+      )
+    plt_thr1 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot (max depth = 2)`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X2"
+      )
+    plt_thr2 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none", linetype = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
+    ) &
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[length(sim_names)]) {
+      plt <- plt &
+        ggplot2::guides(
+          color = "none", fill = "none"
+        )
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[6] ~ 0.6,
+      TRUE ~ 0.5
+    )
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Subgroup Features\n(max depth = 2)"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds\n(max depth = 2)"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs\n(max depth = 2)"
+        )
+    }
+    if (stringr::str_detect(sim_name, "with")) {
+      tag_x_pos <- -.08
+    } else {
+      tag_x_pos <- -.03
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
+        ),
+        plot.tag.position = c(tag_x_pos, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
+      )
+    plt <- plt &
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
+        ),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[length(sim_names)]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
+        )
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 1
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_max_depth2.pdf"),
+  height = 17, 
+  width = 14
+)
+```
+
+### Threshold Distributions
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Virtual Twins",
+  "Causal Tree",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Thresholds Distribution Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
+      ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller) +
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    if (stringr::str_detect(sim_name, "with")) {
+      plt <- plt +
+        ggplot2::labs(y = "")
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, guides = "collect", byrow = FALSE
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_thresholds_all.pdf"),
+  height = 10, 
+  width = 13
+)
+```
+
+### Subgroup Stability
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Causal Tree"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    f1_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "F1"
+      ) |> 
+      dplyr::mutate(
+        .value = mean_feature_selection_err
+      )
+    cate_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "rmse"
+      ) |> 
+      dplyr::mutate(
+        .metric = "Subgroup ATE RMSE",
+        .value = mean_ate_err
+      )
+
+    plt_err <- dplyr::bind_rows(f1_df, cate_df) |> 
+      dplyr::mutate(
+        .metric = forcats::fct_inorder(.metric)
+      ) |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = .value, 
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(
+        stat = "identity", size = 1, width = 0.75
+      ) +
       ggplot2::scale_color_manual(
         breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
+        values = COLORS
       ) +
@@
         breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller)
-  plt_thresholds_ls[[sim_name]] <- plt_thresholds
-
-  plt_stability <- viz_results$`Subgroup Stability Diagnostics Plot`[[1]] +
-    ggplot2::scale_color_manual(
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        .metric ~ tau_heritability, labeller = signal_labeller, 
+        scales = "free_y", switch = "y"
+      ) +
+      ggplot2::scale_x_discrete(
         breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::scale_fill_manual(
-      breaks = KEEP_METHODS,
-      values = COLORS,
-      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-    ) +
-    ggplot2::facet_grid(~ tau_heritability, labeller = signal_labeller) +
+        labels = stringr::str_replace_all(KEEP_METHODS, " ", "\n")
+      ) +
+      ggplot2::labs(y = "", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background.y = ggplot2::element_blank(),
+        strip.text.y = ggplot2::element_text(
+          color = "black", size = 16
+        ),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_blank(),
+        axis.text.y = ggplot2::element_text(size = 9)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      ) |> 
+      dplyr::mutate(
+        .metric = "Jaccard SSI"
+      )
+    plt_jaccard <- plt +
+      ggplot2::geom_line(size = 0.75) +
+      ggplot2::facet_grid(
+        ~ tau_heritability, labeller = signal_labeller, switch = "y"
+      ) +
       ggplot2::coord_cartesian(xlim = c(1, 4)) +
@@
       ) +
-    ggplot2::labs(
-      x = "Tree Depth",
-      y = "Mean Jaccard Stability",
-      color = "Method",
-      fill = "Method"
+      ggplot2::scale_y_continuous(
+        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
+      ) +
+      vthemes::theme_vmodern(size_preset = "medium") +
+      ggplot2::theme(
+        strip.background.y = ggplot2::element_blank(),
+        strip.text.y = ggplot2::element_text(
+          color = "black", size = 16
+        ),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_blank(),
+        axis.text.y = ggplot2::element_text(size = 9)
+      )
+
+    plt <- patchwork::wrap_plots(
+      plt_jaccard, plt_err,
+      ncol = 1, heights = c(1.2, 2), guides = "collect"
+    ) +
+      patchwork::plot_layout(
+        axis_titles = "collect_x"
+      ) +
+      patchwork::plot_annotation(
+        title = sim_name, 
+        tag_levels = "A", 
+        tag_prefix = "(",
+        tag_suffix = ")",
+        theme = ggplot2::theme(
+          plot.title = ggplot2::element_text(
+            size = 18, face = "italic", hjust = 0.42
+          )
+        )
+      ) &
+      ggplot2::theme(
+        # legend.position = "bottom",  # for slides
+        plot.tag = ggplot2::element_text(size = 16)
+      )
+    # ggplot2::ggsave(
+    #   plt, 
+    #   filename = file.path(
+    #     FIG_DIR, 
+    #     sprintf("sim_stability_%s_slides.pdf", sim_name)
+    #   ),
+    #   width = 11.5,
+    #   height = 9
+    # )
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR,
+        sprintf("sim_stability_%s.pdf", sim_name)
+      ),
+      width = 10.5,
+      height = 7.5
+    )
+  }
+)
+```
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Rboost",
+  "Causal Tree"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_df <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "F1"
+      )
+    plt_f1 <- plt_df |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = mean_feature_selection_err,
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(stat = "identity", size = 1) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
+      ) +
+      ggplot2::labs(y = "F1", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt_df <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY,
+        .metric == "rmse"
+      )
+    plt_cate <- plt_df |> 
+      ggplot2::ggplot() +
+      ggplot2::aes(
+        x = .method_name,
+        y = mean_ate_err,
+        fill = .method_name
+      ) +
+      ggplot2::geom_bar(stat = "identity", size = 1) +
+      ggplot2::scale_color_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::scale_fill_manual(
+        breaks = KEEP_METHODS,
+        values = COLORS
+      ) +
+      ggplot2::facet_grid(
+        tau_heritability ~ ., labeller = signal_labeller, scales = "free_y"
+      ) +
+      ggplot2::labs(y = "Subgroup ATE RMSE", x = "Method") +
+      ggplot2::guides(color = "none", fill = "none") +
+      vthemes::theme_vmodern(size_preset = "medium", grid_color = "grey98") +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[1]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt_jaccard <- plt +
+      ggplot2::geom_line(size = 0.75) +
+      ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
+      ggplot2::coord_cartesian(xlim = c(1, 4)) +
+      ggplot2::scale_x_continuous(
+        breaks = 1:4
+      ) +
+      ggplot2::scale_y_continuous(
+        limits = c(0, 1), breaks = seq(0, 1, by = 0.2)
       ) +
       vthemes::theme_vmodern(size_preset = "medium")
-  plt_stability_ls[[sim_name]] <- plt_stability
-
-  plt_nsplits <- viz_results$`Number of Splits Plot` +
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Stability Diagnostics Plot`[[2]]
+    plt$data <- plt$data |> 
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    FT_COLORS <- c(
+      "#d3831b", "#eeb062",
+      "#CCCCCC", "#B5B5B5", "#9E9E9E", "#888888",
+      "#717171", "#5A5A5A", "#434343", "#2D2D2D"
+    )
+    plt_stability_feature <- plt +
+      ggplot2::scale_fill_manual(values = FT_COLORS) +
+      ggplot2::facet_grid(tau_heritability ~ depth, labeller = signal_labeller) +
+      vthemes::theme_vmodern(size_preset = "medium") +
+      ggplot2::theme(
+        axis.text.x = ggplot2::element_text(angle = 90, hjust = 1, vjust = 0.5)
+      )
+
+    plt <- patchwork::wrap_plots(
+      plt_f1, plt_cate, plt_jaccard, plt_stability_feature,
+      nrow = 1, widths = c(0.5, 0.5, 1.25, 3.25), guides = "collect"
+    ) |> 
+      patchwork::wrap_elements() +
+      ggplot2::labs(
+        title = "   (A) Subgroup Estimation       (B) Jaccard Stability                              (C) Feature Stability",
+        tag = sim_name
+      ) +
+      ggplot2::theme(
+        plot.tag = ggplot2::element_text(
+          size = 20, face = "bold", hjust = 0.5
+        ),
+        plot.tag.position = c(0.47, 1.02),
+        plot.margin = ggplot2::unit(c(0.32, 0, 0, 0.2), units = "in"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0, vjust = -0.3
+        )
+      )
+
+    ggplot2::ggsave(
+      plt, 
+      filename = file.path(
+        FIG_DIR, 
+        sprintf("sim_stability_feature_%s.pdf", sim_name)
+      ),
+      height = 8, 
+      width = 14
+    )
+  }
+)
+```
+
+### Number of Trees/Replicates Heatmap
+
+```{r}
+KEEP_METHODS <- c(
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
+  "Virtual Twins",
+  "Causal Tree",
+  "Causal Tree (unpruned)",
+  "Linear Regression",
+  "Lasso"
+)
+KEEP_HERITABILITY <- c(0.2, 0.6, 1)
+
+# without covariates
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::imap(
+  sim_names,
+  function(sim_name, idx) {
+    tag <- LETTERS[idx]
+    plt <- viz_results_ls[[sim_name]]$`Feature and Split Frequency Plots`[[1]]
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        tau_heritability %in% KEEP_HERITABILITY
+      )
+    plt <- plt +
       ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
-    viridis::scale_fill_viridis(
-      begin = 0.05, end = 1, option = "magma", limits = c(0., 7)
-    )
-  plt_ntrees <- viz_results$`Number of Trees Plot` +
-    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
-    viridis::scale_fill_viridis(
-      begin = 0.05, end = 1, option = "magma", limits = c(0, 100)
-    )
+      ggplot2::labs(
+        title = sprintf("(%s) %s", tag, sim_name)
+      ) +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5
+        )
+      )
+    if (stringr::str_detect(sim_name, "with")) {
+      plt <- plt + 
+        ggplot2::labs(y = "")
+    }
+    return(plt)
+  }
+) |>
+  patchwork::wrap_plots(
+    ncol = 2, guides = "collect", byrow = FALSE
+  )
+ggplot2::ggsave(
+  plt, 
+  filename = file.path(FIG_DIR, "sim_ntrees.pdf"),
+  height = 15.5, 
+  width = 13
+)
+```
+
+## Varying \# Repeated Crossfits Simulations {.tabset .tabset-pills .tabset-pills-square}
+
+```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Varying nrep crossfits")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
+  fit_results <- readRDS(
+    file.path(
+      sim_results_dir, 
+      paste0(sim_name, "-Distilled Rboost (crossfit)"), 
+      "Varying tau_heritability-nreps_crossfit", "fit_results.rds"
+    )
+  )
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, 
+      paste0(sim_name, "-Distilled Rboost (crossfit)"), 
+      "Varying tau_heritability-nreps_crossfit", "eval_results.rds"
+    )
+  )
+  eval_results <- purrr::map(
+    eval_results,
+    ~ .x |>
+      dplyr::filter(
+        !stringr::str_detect(.method_name, "unpruned"),
+        !stringr::str_detect(.method_name, "Causal Forest")
+      ) |>
+      dplyr::mutate(
+        .method_name = stringr::str_remove_all(.method_name, " \\(.*\\)"),
+        nreps_crossfit = tidyr::replace_na(nreps_crossfit, 0) |>
+          as.factor() |>
+          forcats::fct_inseq()
+      )
+  )
+
+  viz_results <- visualize_experiment(
+    crossfit_experiment, fit_results, eval_results
+  )
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Estimated Thresholds + Estimated Subgroup ATEs
+
+```{r}
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt_selection <- plt +
+      ggplot2::guides(
+        color = ggplot2::guide_legend(nrow = 1),
+        fill = ggplot2::guide_legend(nrow = 1)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
+    plt_cate <- plt +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(
+        color = ggplot2::guide_legend(nrow = 1),
+        fill = ggplot2::guide_legend(nrow = 1)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .var == "X1"
+      )
+    plt_thr1 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .var == "X2"
+      )
+    plt_thr2 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
     plt <- patchwork::wrap_plots(
-    plt_ntrees, plt_nsplits, nrow = 1
-  ) +
-    patchwork::plot_layout(
-      axis_titles = "collect_y"
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
     ) &
-    ggplot2::labs(
-      x = "Variable"
-    )
-
-  plt_freq_ls[[sim_name]] <- plt
-}
-```
-
-```{r}
-plt_subgroup <- purrr::map2(
-  plt_subgroup_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_subgroup_ls[idx])
-    tag <- LETTERS[idx]
-    if (sim_name != names(plt_subgroup_ls[2])) {
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[3]) {
       plt <- plt &
@@
         )
-      hjust <- 0.78
-    } else {
-      hjust <- 0.82
-    }
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[3] ~ 0.66
+    )
+    if (sim_name == sim_names[1]) {
       plt[[1]] <- plt[[1]] +
         ggplot2::labs(
-        tag = sprintf("(%s) %s", tag, sim_name)
+          title = "(A) Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs"
+        )
+    }
+    plt[[1]] <- plt[[1]] +
+      ggplot2::labs(
+        tag = plt_name
       ) +
@@
         ),
-        plot.tag.position = c(-.03, 0.48),
-        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.5), units = "in")
+        plot.tag.position = c(-.03, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
       )
@@
       ggplot2::theme(
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
         ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
-        )
-      )
-      # ggplot2::theme(
-      #   plot.title = ggplot2::element_text(
-      #     size = 16, face = "bold", hjust = hjust
-      #   ),
-      #   plot.title.position = "plot"
-      # )
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[3]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
+        )
+    }
     return(plt)
@@
     ncol = 1
-  ) |>
-  patchwork::wrap_elements() +
-  ggplot2::labs(
-    tag = expression(
-      bold(paste("Proportion of Variance Explained in ", tau))
-    )
-  ) +
-  ggplot2::theme(
-    plot.tag = ggplot2::element_text(
-      size = 16
-    ),
-    plot.tag.position = c(0.45, 0),
-    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
   )
 ggplot2::ggsave(
-  plt_subgroup, 
-  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
-  height = 9, 
-  width = 14
-)
-
-plt_subgroup_cov <- purrr::map2(
-  plt_subgroup_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name_orig <- names(plt_subgroup_ls[idx])
-    sim_name <- stringr::str_replace(
-      sim_name_orig, "with", "DGP with\n"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
-    if (sim_name_orig != names(plt_subgroup_ls[5])) {
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_nreps_crossfit.pdf"),
+  height = 9.5, 
+  width = 15
+)
+```
+
+## Rulefit Simulations
+
+```{r results = "asis"}
+sim_results_dir <- here::here(
+  file.path("results", "Rulefit Simulations")
+)
+SIM_NAMES <- c(
+  "AND DGP" = "AND DGP",
+  "Additive DGP" = "Additive DGP",
+  "OR DGP" = "OR DGP",
+  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
+  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
+  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
+)
+
+# load in results
+eval_results_ls <- list()
+viz_results_ls <- list()
+for (sim_name in names(SIM_NAMES)) {
+  eval_results <- readRDS(
+    file.path(
+      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
+    )
+  )
+  viz_results <- visualize_experiment(
+    rulefit_experiment, NULL, eval_results
+  )
+  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
+  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
+}
+```
+
+### Selected Subgroup Features + Estimated Thresholds + Estimated Subgroup ATEs
+
+```{r}
+KEEP_METHODS <-  c(
+  "CART",
+  "Rulefit (linear + rules, max depth = 3)",
+  "Rulefit (linear + rules, max depth = 2)",
+  "Rulefit (rules only, max depth = 3)",
+  "Rulefit (rules only, max depth = 2)"
+)
+
+sim_names <- c(
+  "AND DGP",
+  "Additive DGP",
+  "OR DGP",
+  "AND DGP with Linear Covariates",
+  "Additive DGP with Linear Covariates",
+  "OR DGP with Linear Covariates"
+)
+plt <- purrr::map(
+  sim_names,
+  function(sim_name) {
+    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
+    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_selection <- plt
+
+    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS
+      )
+    plt_cate <- plt +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12),
+        legend.title = ggplot2::element_text(face = "bold", size = 16),
+        legend.text = ggplot2::element_text(size = 12)
+      )
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X1"
+      )
+    plt_thr1 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(1), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none")
+
+    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
+    plt$data <- plt$data |>
+      dplyr::filter(
+        .method_name %in% KEEP_METHODS,
+        .var == "X2"
+      )
+    plt_thr2 <- plt +
+      ggplot2::labs(
+        y = expression(
+          bold(paste(X^(2), " Threshold RMSE"))
+        )
+      ) +
+      ggplot2::theme(
+        strip.background = ggplot2::element_blank(),
+        strip.text = ggplot2::element_blank(),
+        strip.placement = "outside",
+        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
+        axis.text = ggplot2::element_text(size = 12)
+      ) +
+      ggplot2::guides(color = "none", fill = "none")
+    plt_thr <- plt_thr1 + plt_thr2
+
+    plt <- patchwork::wrap_plots(
+      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
+      widths = c(3.5, 2.35, 1)
+    ) &
+      ggplot2::labs(x = NULL) &
+      ggplot2::theme(legend.position = "bottom")
+
+    if (sim_name != sim_names[length(sim_names)]) {
       plt <- plt &
@@
         )
-      hjust <- 0.78
+    }
+    tag_pos <- dplyr::case_when(
+      sim_name == sim_names[1] ~ 0.45,
+      sim_name == sim_names[2] ~ 0.53,
+      sim_name == sim_names[6] ~ 0.6,
+      TRUE ~ 0.5
+    )
+    if (sim_name == sim_names[1]) {
+      plt[[1]] <- plt[[1]] +
+        ggplot2::labs(
+          title = "(A) Subgroup Features"
+        )
+      plt[[2]] <- plt[[2]] +
+        ggplot2::labs(
+          title = "(B) Subgroup Thresholds"
+        )
+      plt[[3]] <- plt[[3]] +
+        ggplot2::labs(
+          title = "(C) Subgroup ATEs"
+        )
+    }
+    if (stringr::str_detect(sim_name, "with")) {
+      tag_x_pos <- -.08
     } else {
-      hjust <- 0.82
+      tag_x_pos <- -.03
     }
@@
       ggplot2::labs(
-        tag = sprintf("(%s) %s", tag, sim_name)
+        tag = plt_name
       ) +
@@
         ),
-        plot.tag.position = c(-.06, 0.48),
-        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.75), units = "in")
+        plot.tag.position = c(tag_x_pos, tag_pos),
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
       )
@@
       ggplot2::theme(
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
+        panel.background = ggplot2::element_rect(fill = "grey98"),
+        panel.grid.major = ggplot2::element_line(color = "grey98"),
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.5, vjust = -1
+        )
+      )
+    plt[[2]] <- plt[[2]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 1.5, vjust = -1
         ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
-        )
-      )
-      # ggplot2::theme(
-      #   plot.title = ggplot2::element_text(
-      #     size = 16, face = "bold", hjust = hjust
-      #   ),
-      #   plot.title.position = "plot"
-      # )
+        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
+      )
+    plt[[3]] <- plt[[3]] +
+      ggplot2::theme(
+        plot.title = ggplot2::element_text(
+          size = 18, face = "italic", hjust = 0.75, vjust = -1
+        )
+      )
+    if (sim_name == sim_names[length(sim_names)]) {
+      plt <- plt +
+        ggplot2::labs(
+          x = expression(
+            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
+          )
+        ) +
+        ggplot2::theme(
+          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 1.95, vjust = -1.25)
+        )
+    }
     return(plt)
@@
     ncol = 1
-  ) |>
-  patchwork::wrap_elements() +
-  ggplot2::labs(
-    tag = expression(
-      bold(paste("Proportion of Variance Explained in ", tau))
-    )
-  ) +
-  ggplot2::theme(
-    plot.tag = ggplot2::element_text(
-      size = 16
-    ),
-    plot.tag.position = c(0.45, 0),
-    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
   )
 ggplot2::ggsave(
-  plt_subgroup_cov, 
-  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
-  height = 9, 
+  plt, 
+  filename = file.path(FIG_DIR, "sim_subgroup_errors_all_rulefit.pdf"),
+  height = 17, 
   width = 14
@@
 ```
-
-```{r}
-plt_thresholds <- purrr::map2(
-  plt_thresholds_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_thresholds_ls[idx])
-    tag <- LETTERS[idx]
-    plt <- plt +
-      ggplot2::labs(
-        title = sprintf("(%s) %s", tag, sim_name)
-      ) +
-      ggplot2::theme(
-        plot.title = ggplot2::element_text(
-          size = 18, face = "italic", hjust = 0.5
-        ),
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
-        ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
-        )
-      )
-    return(plt)
-  }
-) |>
-  patchwork::wrap_plots(
-    ncol = 1, guides = "collect"
-  ) +
-  patchwork::plot_layout(
-    axes = "collect"
-  )
-ggplot2::ggsave(
-  plt_thresholds, 
-  filename = file.path(FIG_DIR, "sim_thresholds.pdf"),
-  height = 10, 
-  width = 11
-)
-
-plt_thresholds_cov <- purrr::map2(
-  plt_thresholds_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name <- stringr::str_replace(
-      names(plt_thresholds_ls[idx]), "with", "DGP with\n"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
-    plt <- plt +
-      ggplot2::labs(
-        title = sprintf("(%s) %s", tag, sim_name)
-      ) +
-      ggplot2::theme(
-        plot.title = ggplot2::element_text(
-          size = 18, face = "italic", hjust = 0.5
-        ),
-        panel.background = ggplot2::element_rect(
-          fill = "grey98"
-        ),
-        panel.grid.major = ggplot2::element_line(
-          color = "grey98"
-        )
-      )
-    return(plt)
-  }
-) |>
-  patchwork::wrap_plots(
-    ncol = 1, guides = "collect"
-  ) +
-  patchwork::plot_layout(
-    axes = "collect"
-  )
-ggplot2::ggsave(
-  plt_thresholds_cov, 
-  filename = file.path(FIG_DIR, "sim_thresholds_cov.pdf"),
-  height = 10, 
-  width = 11
-)
-```
-
-```{r}
-# plt_ntrees_ls <- purrr::map(
-#   plt_freq_ls[1:3], ~ .x[[1]]
-# )
-# plt_nsplits_ls <- purrr::map(
-#   plt_freq_ls[1:3], ~ .x[[2]]
-# )
-# plt_ntrees <- patchwork::wrap_plots(
-#   plt_ntrees_ls, nrow = 1, guides = "collect"
-# ) +
-#   patchwork::plot_layout(
-#     axes = "collect"
-#   )
-
-plt_freq <- purrr::map2(
-  plt_freq_ls[1:3], 1:3,
-  function(plt, idx) {
-    sim_name <- names(plt_freq_ls[idx])
-    tag <- LETTERS[idx]
-    plt <- patchwork::wrap_elements(plt) +
-      ggplot2::labs(
-        tag = sprintf("(%s) %s", tag, sim_name)
-      ) +
-      ggplot2::theme(
-        plot.tag = ggplot2::element_text(
-          size = 18, face = "italic", hjust = 0.5
-        ),
-        plot.tag.position = c(0.47, 1.02),
-        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
-      )
-    return(plt)
-  }
-) |>
-  patchwork::wrap_plots(
-    ncol = 1
-  )
-ggplot2::ggsave(
-  plt_freq, 
-  filename = file.path(FIG_DIR, "sim_freq.pdf"),
-  height = 16, 
-  width = 14
-)
-
-plt_freq_cov <- purrr::map2(
-  plt_freq_ls[4:6], 4:6,
-  function(plt, idx) {
-    sim_name <- stringr::str_replace(
-      names(plt_freq_ls[idx]), "with", "DGP with"
-    ) |>
-      stringr::str_remove(" DGP$")
-    tag <- LETTERS[idx - 3]
-    plt <- patchwork::wrap_elements(plt) +
-      ggplot2::labs(
-        tag = sprintf("(%s) %s", tag, sim_name)
-      ) +
-      ggplot2::theme(
-        plot.tag = ggplot2::element_text(
-          size = 18, face = "italic", hjust = 0.5
-        ),
-        plot.tag.position = c(0.47, 1.02),
-        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
-      )
-    return(plt)
-  }
-) |>
-  patchwork::wrap_plots(
-    ncol = 1
-  )
-ggplot2::ggsave(
-  plt_freq_cov, 
-  filename = file.path(FIG_DIR, "sim_freq_cov.pdf"),
-  height = 16, 
-  width = 14
-)
-```
-
-```{r}
-plt_stability <- purrr::map2(
-  plt_stability_ls, 1:length(plt_stability_ls),
-  function(plt, idx) {
-    plt_names <- names(plt_stability_ls)
-    sim_name <- dplyr::case_when(
-      stringr::str_detect(plt_names, "with") ~ 
-        stringr::str_replace(
-          plt_names, "with", "DGP with\n"
-        ) |> 
-        stringr::str_remove(" DGP$"),
-      TRUE ~ plt_names
-    )[idx]
-    tag <- LETTERS[idx]
-    plt_df <- plt$data |>
-      dplyr::mutate(
-        sim_name = sprintf("(%s) %s", tag, sim_name)
-      )
-    return(plt_df)
-  }
-) |>
-  purrr::list_rbind() |> 
-  dplyr::filter(
-    depth <= 4
-  )
-  ggplot2::ggplot() +
-  ggplot2::geom_line(
-    ggplot2::aes(
-      x = depth, y = mean_jaccard, color = .method_name
-    )
-  ) +
-  ggplot2::geom_ribbon(
-    ggplot2::aes(
-      x = depth,
-      ymin = mean_jaccard - se_jaccard,
-      ymax = mean_jaccard + se_jaccard,
-      fill = .method_name
-    ),
-    alpha = 0.2
-  ) +
-  ggplot2::facet_grid(sim_name ~ tau_heritability, labeller = signal_labeller) +
-  ggplot2::scale_color_manual(
-    breaks = KEEP_METHODS,
-    values = COLORS,
-    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-  ) +
-  ggplot2::scale_fill_manual(
-    breaks = KEEP_METHODS,
-    values = COLORS,
-    labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
-  ) +
-  ggplot2::coord_cartesian(xlim = c(1, 4)) +
-  ggplot2::scale_x_continuous(
-    breaks = 1:4
-  ) +
-  ggplot2::labs(
-    x = "Tree Depth",
-    y = "Mean Jaccard Stability",
-    color = "Method",
-    fill = "Method"
-  ) +
-  vthemes::theme_vmodern(
-    size_preset = "medium", grid_color = "grey98"
-  )
-ggplot2::ggsave(
-  plt_stability, 
-  filename = file.path(FIG_DIR, "sim_stability.pdf"),
-  height = 12, 
-  width = 11
-)
-```

### 2025-02-13 causalDT-manuscript/R/viz/visualizers.R
update sim code with jaccard renaming

@@ -477,8 +477,7 @@ plot_stability_diagnostics <- function(fit_results,
         stability_diagnostics,
         ~ tibble::tibble(
           depth = 1:length(.x$jaccard_mean),
-          jaccard = .x$jaccard_mean,
-          jaccard_scaled = .x$jaccard_scaled_mean
+          jaccard = .x$jaccard_mean
         )
       )
     ) |>
@@ -495,9 +494,9 @@ plot_stability_diagnostics <- function(fit_results,
       dplyr::across(tidyselect::all_of(c(group_cols, "depth")))
     ) |>
     dplyr::summarise(
-      mean_jaccard = mean(jaccard_scaled),
-      sd_jaccard = sd(jaccard_scaled),
-      se_jaccard = sd(jaccard_scaled) / sqrt(dplyr::n()),
+      mean_jaccard = mean(jaccard),
+      sd_jaccard = sd(jaccard),
+      se_jaccard = sd(jaccard) / sqrt(dplyr::n()),
       .groups = "drop"
     ) |>
     ggplot2::ggplot() +

### 2025-02-13 README.Rmd
add readmes

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Causal Distillation Trees

[Causal Distillation Trees](https://arxiv.org/abs/2502.07275) (CDT) is a novel machine learning method for estimating interpretable subgroups in causal inference. CDT allows researchers to fit *any* machine learning model of their choice to estimate the individual-level treatment effect, and then leverages a simple, second-stage tree-based model to "distill" the estimated treatment effect into meaningful subgroups. As a result, CDT inherits the improvements in predictive performance from black-box machine learning models while preserving the interpretability of a simple decision tree.

![](causalDT/man/figures/cdt_diagram.png)

Briefly, CDT is a two-stage learner that first fits a teacher model (e.g., a black-box metalearner) to estimate individual-level treatment effects and secondly fits a student model (e.g., a decision tree) to predict the estimated individual-level treatment effects, in effect distilling the estimated individual-level treatment effects and producing interpretable subgroups. This two-stage learner is learned using the training data. Finally, using the estimated subgroups, the subgroup average treatment effects are honestly estimated with a held-out estimation set.

For more details, check out [Huang, M., Tang, T. M., Kenney, A. M. "Distilling heterogeneous treatment effects: Stable subgroup estimation in causal inference." (2025).](https://arxiv.org/abs/2502.07275)

## Organization

This repository contains:

1. An R package `causalDT` to run causal distillation trees on your own data (see [causalDT/](causalDT/))
2. All code necessary to reproduce the analysis and figures in [Huang et al. (2025)](https://arxiv.org/abs/2502.07275) (see [causalDT-manuscript/](causalDT-manuscript/))

## Installation of the R package

You can install the `causalDT` R package via:

``` r
# install.packages("devtools")
devtools::install_github("tiffanymtang/causalDT", subdir = "causalDT")
```

## Example Usage

To illustrate an example usage of `causalDT`, we will use the AIDS Clinical Trials Group Study 175 (ACTG 175), a randomized controlled trial to determine the effectiveness of monotherapy compared to combination therapy on HIV-1-infected patients. This data can be found in the `speff2trial` R package.

```{r}
# install.packages("speff2trial")
library(speff2trial)

data <- speff2trial::ACTG175 |>
  dplyr::filter(arms %in% c(0, 2))

# pre-treatment covariates data
X <- data |> 
  dplyr::select(
    age, wtkg, hemo, homo, drugs, karnof, race, 
    gender, symptom, preanti, strat, cd80
  ) |> 
  as.matrix()
# treatment indicator variable
Z <- data |>
  dplyr::pull(treat)
# response variable
Y <- data |>
  dplyr::pull(cens)
```

Given the pre-treatment covariates data $X$, the treatment variable $Z$, and the response variable $Y$, we can run CDT as follows:

```{r fig.width=12}
library(causalDT)

set.seed(331)
causal_forest_cdt <- causalDT(
  X = X, Y = Y, Z = Z,
  teacher_model = "causal_forest"
)

plot_cdt(causal_forest_cdt)
```

Note that when using CDT, a teacher model must be chosen (the default is a causal forest). To help researchers select an appropriate teacher model, the Jaccard subgroup stability index (SSI) was introduced in [Huang et al. (2025)](https://arxiv.org/abs/2502.07275). Generally, a higher Jaccard SSI indicates a better teacher model. This teacher model selection procedure can be run as follows:

```{r}
# selecting between causal forest versus rboost
rboost_cdt <- causalDT(
  X = as.matrix(X), Y = Y, Z = Z,
  teacher_model = rboost
)
plot_jaccard(`Causal Forest` = causal_forest_cdt, `Rboost` = rboost_cdt)
```

## Citation

```
@article{huang2025distilling,
  title={Distilling heterogeneous treatment effects: Stable subgroup estimation in causal inference}, 
  author={Melody Huang and Tiffany M. Tang and Ana M. Kenney},
  year={2025},
  eprint={2502.07275},
  archivePrefix={arXiv},
  primaryClass={stat.ME},
  url={https://arxiv.org/abs/2502.07275}, 
}
```

### 2025-02-13 causalDT-manuscript/README.Rmd
add readmes

--- 2025-02-13 README.Rmd
@@
 
-![](causalDT/man/figures/cdt_diagram.png)
+![](../causalDT/man/figures/cdt_diagram.png)
 
@@
 
-## Organization
+## Project Structure
 
-This repository contains:
+This directory contains all of the code necessary to reproduce the analysis and figures in [Huang et al. (2025)](https://arxiv.org/abs/2502.07275).
 
-1. An R package `causalDT` to run causal distillation trees on your own data (see [causalDT/](causalDT/))
-2. All code necessary to reproduce the analysis and figures in [Huang et al. (2025)](https://arxiv.org/abs/2502.07275) (see [causalDT-manuscript/](causalDT-manuscript/))
+Moreover, to facilitate reproducibility of this work, we leveraged [`renv`](https://rstudio.github.io/renv/articles/renv.html) to create a reproducible environment and [`simChef`](https://yu-group.github.io/simChef/) to create a reproducible and transparent simulation workflow.
+Thus, to install the necessary dependencies and reproduce the simulation, the following steps are recommended:
 
-## Installation of the R package
+1. Clone this repository.
+2. Open the `causalDT-manuscript.Rproj` in RStudio.
+3. Run the following code in the R console:
 
-You can install the `causalDT` R package via:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("tiffanymtang/causalDT", subdir = "causalDT")
+```r
+# install.packages("renv")
+renv::restore()
 ```
 
-## Example Usage
+4. Run each of the simulation driver scripts in the `meals/` directory.
+5. Render all of the results into a single summary `simChef` documentation by running the `meals/00_render_docs.R` script.
 
-To illustrate an example usage of `causalDT`, we will use the AIDS Clinical Trials Group Study 175 (ACTG 175), a randomized controlled trial to determine the effectiveness of monotherapy compared to combination therapy on HIV-1-infected patients.
-This data can be found in the `speff2trial` R package.
-
-```{r}
-# install.packages("speff2trial")
-library(speff2trial)
-
-data <- speff2trial::ACTG175 |>
-  dplyr::filter(arms %in% c(0, 2))
-
-# pre-treatment covariates data
-X <- data |> 
-  dplyr::select(
-    age, wtkg, hemo, homo, drugs, karnof, race, 
-    gender, symptom, preanti, strat, cd80
-  ) |> 
-  as.matrix()
-# treatment indicator variable
-Z <- data |>
-  dplyr::pull(treat)
-# response variable
-Y <- data |>
-  dplyr::pull(cens)
-```
-
-Given the pre-treatment covariates data $X$, the treatment variable $Z$, and the response variable $Y$, we can run CDT as follows:
-
-```{r fig.width=12}
-library(causalDT)
-
-set.seed(331)
-causal_forest_cdt <- causalDT(
-  X = X, Y = Y, Z = Z,
-  teacher_model = "causal_forest"
-)
-
-plot_cdt(causal_forest_cdt)
-```
-
-Note that when using CDT, a teacher model must be chosen (the default is a causal forest).
-To help researchers select an appropriate teacher model, the Jaccard subgroup stability index (SSI) was introduced in [Huang et al.
-(2025)](https://arxiv.org/abs/2502.07275).
-Generally, a higher Jaccard SSI indicates a better teacher model.
-This teacher model selection procedure can be run as follows:
-
-```{r}
-# selecting between causal forest versus rboost
-rboost_cdt <- causalDT(
-  X = as.matrix(X), Y = Y, Z = Z,
-  teacher_model = rboost
-)
-plot_jaccard(`Causal Forest` = causal_forest_cdt, `Rboost` = rboost_cdt)
-```
+These steps will generate all of the figures and results from the mansucript. The rendered `simChef` documentation can be found in the `results/` directory (see [here](results/Results.html)).
 
@@
 
-```
+```r
 @article{huang2025distilling,

### 2025-02-13 causalDT/README.Rmd
add readmes

--- 2025-02-13 README.Rmd
@@
 "Distilling heterogeneous treatment effects: Stable subgroup estimation in causal inference." (2025).](https://arxiv.org/abs/2502.07275)
-
-## Organization
-
-This repository contains:
-
-1. An R package `causalDT` to run causal distillation trees on your own data (see [causalDT/](causalDT/))
-2. All code necessary to reproduce the analysis and figures in [Huang et al. (2025)](https://arxiv.org/abs/2502.07275) (see [causalDT-manuscript/](causalDT-manuscript/))
 

### 2025-02-13 causalDT-manuscript/results/Results.Rmd
add results

---
author: 'Melody Huang, Tiffany M. Tang, Ana M. Kenney'
date: '`r format(Sys.time(), "%B %d, %Y")`'
title: "Causal Distillation Trees: Supplemental Simulation Results"
output: vthemes::vmodern
params:
  sim_path:
    input: text
    label: 'Path to Simulation Experiment Folder:'
    value: /Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results
---

<script src="/Users/ttang4/Library/Caches/org.R-project.R/R/renv/cache/v5/macos/R-4.4/aarch64-apple-darwin20/simChef/0.1.0.9000/35207a8200887c29dd6eb0e5f5baa7f9/simChef/rmd/js/simchefNavClass.js"></script>

<link rel="stylesheet" href="/Users/ttang4/Library/Caches/org.R-project.R/R/renv/cache/v5/macos/R-4.4/aarch64-apple-darwin20/simChef/0.1.0.9000/35207a8200887c29dd6eb0e5f5baa7f9/simChef/rmd/css/simchef.css">

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.pos = "H",
  fig.height = 12,
  fig.width = 10
)

options(
  width = 10000,
  knitr.kable.NA = 'NA'
)

library(simChef)

local({
  hook_output <- knitr::knit_hooks$get("output")
  knitr::knit_hooks$set(
    # scrollable text output
    output = function(x, options) {
      if (!is.null(options$max.height)) {
        options$attr.output <- c(
          options$attr.output,
          sprintf('style="max-height: %s;"', options$max.height)
        )
      }
      hook_output(x, options)
    },
    # add panel around figures
    add.panel = function(before, options, envir) {
      if (before) {
        HTML("<div class='panel panel-default padded-panel'>")
      } else {
        HTML("</div>")
      }
    }
  )
})
```

```{css}
h5 {
  font-size: 16pt;
}
```

```{r}
#' Get all experiments under a given directory name.
#'
#' @param dir_name Name of directory.
#' @return List of named experiments.
get_descendants <- function(dir_name) {
  experiments <- list()
  for (d in list.dirs(dir_name)) {
    if (file.exists(file.path(d, "experiment.rds"))) {
      if (identical(d, params$sim_path)) {
        exp_name <- "Base"
      } else {
        exp_name <- stringr::str_replace_all(
          stringr::str_remove(d, paste0(params$sim_path, "/")),
          "/", " - "
        )
      }
      experiments[[exp_name]] <- readRDS(file.path(d, "experiment.rds"))
    }
  }
  return(experiments)
}

#' Reads in file if it exists and returns NULL if the file does not exist
#' 
#' @description If filetype is ".rds", the file is read in using readRDS(). 
#'   Otherwise, the file is read in using data.table::fread().
#'
#' @param filename name of file (with file extension) to try reading in
#' @param filetype file extension
#' @param experiment experiment object
#' @param experiment_save_dir directory where experiment results are saved
#' @param field_name one of "evaluator" or "visualizer"
#' @return output of experiment results if the file exists and NULL otherwise
get_results <- function(filename, filetype = ".rds",
                        experiment, experiment_save_dir = NULL,
                        field_name = c("evaluator", "visualizer")) {
  field_name <- match.arg(field_name)
  if (field_name == "evaluator") {
    save_in_bulk <- experiment$get_save_in_bulk()[["eval"]]
  } else if (field_name == "visualizer") {
    save_in_bulk <- experiment$get_save_in_bulk()[["viz"]]
  }
  results <- NULL
  if (save_in_bulk) {
    if (file.exists(filename)) {
      if (filetype == ".rds") {
        results <- readRDS(filename)
      } else {
        results <- data.table::fread(results)
      }
    }
  } else {
    if (is.null(experiment_save_dir)) {
      stop("experiment_save_dir must be provided if save_in_bulk is FALSE")
    }
    if (field_name == "evaluator") {
      obj_names <- names(experiment$get_evaluators())
      obj_dirname <- file.path(experiment_save_dir, "eval_results")
    } else if (field_name == "visualizer") {
      obj_names <- names(experiment$get_visualizers())
      obj_dirname <- file.path(experiment_save_dir, "viz_results")
    }
    if (length(obj_names) == 0) {
      return(NULL)
    }
    names(obj_names) <- obj_names
    results <- purrr::map(
      obj_names, 
      function(obj_name) {
        obj_fname <- file.path(obj_dirname, sprintf("%s%s", obj_name, filetype))
        if (file.exists(obj_fname)) {
          if (filetype == ".rds") {
            results <- readRDS(obj_fname)
          } else {
            results <- data.table::fread(obj_fname)
          }
        } else {
          results <- NULL
        }
        return(results)
      } 
    ) |> 
      purrr::compact()
  }

  return(results)
}

#' Reads in list of image result files
#' 
#' @param filenames vector of filenames (without file extension) to read in
#' @param filetype file extension
#' @return list of image results, wrapped as knitr::include_graphics() objects
get_image_results <- function(filenames, filetype) {
  purrr::map(
    filenames,
    function(f) {
      if (file.exists(sprintf("%s%s", f, filetype))) {
        return(knitr::include_graphics(sprintf("%s%s", f, filetype)))
      } else {
        return(NULL)
      }
    }
  ) |> 
    setNames(basename(filenames)) |> 
    purrr::compact()
}

#' Get results from experiment
#' 
#' @param dir_name name of directory
#' @param show_eval logical; whether or not to show evaluators
#' @param show_viz logical; whether or not to show visualizers
#' @param eval_cache file extension for cached evaluator results to read in.
#'   Typically ".rds" or "none", but can be any file extension where
#'   evaluator results are stored as `eval_results.ext` and can be read in
#'   using `data.table::fread(eval_results.ext)`. If "none", evaluator results
#'   are computed using the experiment via `evaluate_experiment()`.
#' @param viz_cache file extension for cached visualizer results to read in.
#'   Typically ".rds" or "none", but can be any (image) file extension 
#'   (e.g., "png", "jpg") where the visualizer results have been previously 
#'   stored as separate `{visualizer_name}.ext` images (e.g., using
#'   `export_visualizers()`). If "none", visualizer results are computed using
#'   the experiment via `visualize_experiment()`.
get_exp_results <- function(dir_name, 
                            show_eval = TRUE, show_viz = TRUE,
                            eval_cache = ".rds", viz_cache = ".rds") {

  exp_fname <- file.path(dir_name, "experiment.rds")
  eval_fname <- file.path(dir_name, sprintf("eval_results%s", eval_cache))
  viz_fname <- file.path(dir_name, sprintf("viz_results%s", viz_cache))

  if (file.exists(exp_fname)) {
    exp <- readRDS(exp_fname)
  } else {
    results <- list(
      exp = NULL,
      eval_results = NULL,
      viz_results = NULL
    )
    return(results)
  }
  fit_results <- NULL
  eval_results <- NULL
  viz_results <- NULL
  if ((eval_cache != "none") && (viz_cache == ".rds")) {
    if (show_eval) {
      eval_results <- get_results(
        filename = eval_fname, 
        filetype = eval_cache, 
        experiment = exp, 
        experiment_save_dir = dir_name,
        field_name = "evaluator"
      )
    }
    if (show_viz) {
      viz_results <- get_results(
        filename = viz_fname, 
        filetype = viz_cache, 
        experiment = exp, 
        experiment_save_dir = dir_name,
        field_name = "visualizer"
      )
    }
  } else {
    if (show_eval) {
      if (eval_cache == "none") {
        fit_results <- suppressMessages(get_cached_results(exp, "fit"))
        if (is.null(fit_results)) {
          stop("Cannot set eval_cache = 'none' since no cached fit results found. Perhaps try setting eval_cache = '.rds' instead.")
        }
        eval_results <- evaluate_experiment(exp, fit_results)
      } else {
        eval_results <- get_results(
          filename = eval_fname, 
          filetype = eval_cache, 
          experiment = exp, 
          experiment_save_dir = dir_name,
          field_name = "evaluator"
        )
      }
    }
    if (show_viz) {
      if (viz_cache == ".rds") {
        viz_results <- get_results(
          filename = viz_fname, 
          filetype = viz_cache, 
          experiment = exp, 
          experiment_save_dir = dir_name,
          field_name = "visualizer"
        )
      } else if (viz_cache == "none") {
        if (is.null(fit_results)) {
          fit_results <- suppressMessages(get_cached_results(exp, "fit"))
          if (is.null(fit_results)) {
            stop("Cannot set viz_cache = 'none' since no cached fit results found. Perhaps try setting viz_cache = '.rds' instead.")
          }
        }
        if (is.null(eval_results)) {
          eval_results <- suppressMessages(get_cached_results(exp, "eval"))
          if (is.null(eval_results)) {
            eval_results <- evaluate_experiment(exp, fit_results)
          }
        }
        viz_results <- visualize_experiment(exp, fit_results, eval_results)
      } else {
        viz_results <- get_image_results(
          file.path(dir_name, names(exp$get_visualizers())), viz_cache
        )
      }
    }
  }
  results <- list(
    exp = exp,
    eval_results = eval_results,
    viz_results = viz_results
  )
  return(results)
}

#' Print renv lockfile info
#' 
#' @param renv_lockfile renv lockfile object from [renv::lockfile_read()]
#' @param what part of renv lockfile to print; must be one of "R" or "packages"
#' @param print_table logical; whether to print as a nice table (TRUE) or 
#'   simply using the `print` method.
#' @return renv lockfile info
print_renv <- function(renv_lockfile, 
                       what = c("R", "Packages"),
                       print_table = FALSE) {
  what <- match.arg(what)
  if (what == "R") {
    if (print_table) {
      tab <- tibble::tibble(
        `R Version` = renv_lockfile$R$Version, 
        Repositories = paste(
          names(renv_lockfile$R$Repositories), 
          " (", renv_lockfile$R$Repositories, ")", 
          sep = "", collapse = "<br>"
        )
      ) |> 
        vthemes::pretty_DT(
          rownames = FALSE, options = list(dom = "t", ordering = FALSE)
        )
      return(tab)
    } else {
      return(renv_lockfile$R)
    }
  } else {
    if (print_table) {
      tab <- tibble::tibble(
        `Package Name` = purrr::map_chr(
          renv_lockfile$Packages, 
          function(.x) if (!is.null(.x$Package)) .x$Package else "N/A"
        ),
        `Version` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) if (!is.null(.x$Version)) .x$Version else "N/A"
        ),
        `Source` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) if (!is.null(.x$Source)) .x$Source else "N/A"
        ),
        `Repository` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) {
            if (!is.null(.x$Repository)) {
              .x$Repository
            } else if (!is.null(.x$RemoteUrl)) {
              .x$RemoteUrl
            } else if (.x$Source == "GitHub") {
              sprintf("https://github.com/%s/%s", .x$RemoteUsername, .x$RemoteRepo)
            } else {
              "N/A"
            }
          }
        ),
        `Requirements` = purrr::map_chr(
          renv_lockfile$Packages, ~ paste(.x$Requirements, collapse = ", ")
        )
      ) |> 
        vthemes::pretty_DT(rownames = FALSE)
      return(tab)
    } else {
      return(renv_lockfile$Packages)
    }
  }
}

#' Show recipe content.
#' 
#' @param objs List of DGP/Method/Evaluator/Visualizer objects. Should be one of
#'   `dgp_objs`, `method_objs`, `eval_objs`, or `viz_objs` defined below.
#' @param name Name of DGP/Method/Evaluator/Visualizer.
#' @param experiment_name Name of the Experiment.
#' @param what Either "function" or "parameters", indicating whether to return 
#'   the function code or parameters.
show_recipe <- function(objs, name, experiment_name,
                        what = c("function", "parameters")) {
  what <- match.arg(what)
  obj <- objs[[experiment_name]][[name]]
  field_name <- tolower(class(obj)[1])
  func_name <- dplyr::case_when(
    field_name == "evaluator" ~ "eval",
    field_name == "visualizer" ~ "viz",
    TRUE ~ field_name
  )
  if (identical(what, "function")) {
    return(obj[[paste0(func_name, "_fun")]])
  } else if (identical(what, "parameters")) {
    return(obj[[paste0(func_name, "_params")]])
  }
}

#' Show results of Evaluator, Visualizer, or Varying Across Parameters.
#' 
#' @param dir_name Name of directory of Experiment.
#' @param name Name of Evaluator/Visualizer.
#' @param field_name One of "evaluator", "visualizer", or "vary_params", 
#'   indicating whether to return the results of an Evaluator, Visualizer, or
#'   the varying across parameters of the Experiment, respectively.
show_results <- function(results, name,
                         field_name = c("evaluator", "visualizer", "vary_params")) {
  field_name <- match.arg(field_name)
  exp <- results$exp
  eval_results <- results$eval_results
  viz_results <- results$viz_results

  if (field_name == "evaluator") {
    doc_nrows <- exp$get_evaluators()[[name]]$doc_nrows
    if (is.null(doc_nrows)) {
      eval_results_show <- eval_results[[name]]
    } else {
      keep_rows <- 1:min(doc_nrows, nrow(eval_results[[name]]))
      eval_results_show <- eval_results[[name]][keep_rows, ]
    }
    do.call(vthemes::pretty_DT,
            c(list(eval_results_show),
              exp$get_evaluators()[[name]]$doc_options))
  } else if (field_name == "visualizer") {
    viz_results[[name]]
  } else if (field_name == "vary_params") {
    exp$get_vary_across()
  }
}
```

# Simulation Experiment Recipe {.tabset .tabset-vmodern}

```{r}
descendants <- get_descendants(dir_name = params$sim_path)
dgp_objs <- purrr::map(descendants, ~.x$get_dgps())
method_objs <- purrr::map(descendants, ~.x$get_methods())
eval_objs <- purrr::map(descendants, ~.x$get_evaluators())
viz_objs <- purrr::map(descendants, ~.x$get_visualizers())
```

## Objectives

<div class='panel panel-default padded-panel'>

[Huang et al. (2025)]() introduces **causal distillation trees** (CDT) to stably estimate interpretable subgroups. CDT allows researchers to fit any machine learning model of their choice to estimate the individual-level treatment effect, and then leverages a simple, second-stage tree-based model to "distill" the estimated treatment effect into meaningful subgroups.In this supplementary document, we report the full simulation results (originally presented in [Huang et al. (2025)]()) alongside code and necessary details to reproduce the results. This document as well as the simulations were run using the [`simChef`](https://yu-group.github.io/simChef/) R package.

</div>

## Data Generation

<div class='panel panel-default padded-panel'>
For all DGPs, we consider a random treatment assignment process, where $Z_i \stackrel{iid}{\sim} \text{Bernoulli}(1/2)$ for $i = 1, \ldots, n$ samples. Furthermore, we generate $n$ samples and $p$ covariates from a standard multivariate normal distribution (i.e., $X_i \stackrel{iid}{\sim} \text{MVN}(0, I)$, where $X_i \in \mathbb{R}^{p}$ and $i = 1, \ldots, n$). Each DGP is generated via a different treatment effect heterogeneity (i.e., subgroup) process (for $\tau_i$) and outcome process (for $Y_i$), described below.
</div>

<div class='panel panel-default padded-panel'>

### Additive DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the Additive DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1} \left \{X_{i}^{(1)} > 0 \right\} - \mathbf{1}\left \{X_{i}^{(2)} < -0.5 \right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Main Simulations - Additive DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Main Simulations - Additive DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive DGP', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Additive with Linear Covariates DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the Additive with Linear Covariates DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1} \left \{X_{i}^{(1)} > 0 \right\} - \mathbf{1}\left \{X_{i}^{(2)} < -0.5 \right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + X_i^{(3)} + X_i^{(4)} + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'Additive with Linear Covariates DGP', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### AND DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the AND DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1}\left\{X_{i}^{(1)} > 0 \right\} \cdot \mathbf{1}\left\{X_{i}^{(2)} > 0.5\right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - AND DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Main Simulations - AND DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Main Simulations - AND DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND DGP', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### AND with Linear Covariates DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the AND with Linear Covariates DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1}\left\{X_{i}^{(1)} > 0 \right\} \cdot \mathbf{1}\left\{X_{i}^{(2)} > 0.5\right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + X_i^{(3)} + X_i^{(4)} + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - AND with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'AND with Linear Covariates DGP', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### OR DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the OR DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1}\left\{X_{i}^{(1)} > 0 \right\} - \mathbf{1} \left\{(X_{i}^{(2)} > 0.5) \text{ or } (X_i^{(2)} < -0.5)\right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - OR DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Main Simulations - OR DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Main Simulations - OR DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR DGP', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### OR with Linear Covariates DGP {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In the OR with Linear Covariates DGP, the treatment effect heterogeneity (i.e., subgroup) DGP is generated via\begin{align*}\tau_i = 2 \mathbf{1}\left\{X_{i}^{(1)} > 0 \right\} - \mathbf{1} \left\{(X_{i}^{(2)} > 0.5) \text{ or } (X_i^{(2)} < -0.5)\right\} + \epsilon_i, \qquad \text{where } \epsilon_i \stackrel{iid}{\sim} N(0, \sigma_{\tau}^2),\end{align*}and the outcome process is generated via:\begin{align*}Y_i = Z_i \cdot \tau_i + X_i^{(3)} + X_i^{(4)} + \nu_i, \qquad \text{where } \nu_i \stackrel{iid}{\sim} N(0, 0.1^2).\end{align*}

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - OR with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(dgp_objs, 'OR with Linear Covariates DGP', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>
For each DGP, we simulated data with $n = 500$ samples, $p = 10$ features, and varied $\sigma_{\tau}$ such that the proportion of variance explained in $\tau(X)$ by $X$ (i.e., $\text{var}(\mathbb{E}[\tau_i \mid X]) / \text{var}(\tau_i)$) varied across the values $\{0.2, 0.4, 0.6, 0.8, 1\}$. All simulations were run for 100 replicates.
</div>

## Methods

<div class='panel panel-default padded-panel'>

### Distilled Causal Forest {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

Distilled Causal Forest refers to a Causal Distillation Tree [Huang et al. (2025)]() using causal forests as the first-stage learner and CART as the second stage learner. Both pruned and unpruned versions of Distilled Causal Forest were run for comparison.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Distilled Rboost {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

Distilled Rboost refers to a Causal Distillation Tree [Huang et al. (2025)]() using an R-learner with boosting (rboost) as the first-stage learner and CART as the second stage learner. Both pruned and unpruned versions of Distilled Rboost were run for comparison.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Rboost', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Causal Tree {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

Causal trees [Athey and Imbens (2016)](https://www.pnas.org/doi/10.1073/pnas.1510489113) are a type of decision tree, which were specifically designed to estimate heterogeneous treatment effects and subgroups with either reduced or elevated treatment effects. We implement causal trees using the `causalTree` R package with the default parameters shown on [GitHub](https://github.com/susanathey/causalTree).

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Causal Tree', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Virtual Twins {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

Similar to the proposed distillation approach, virtual twins is a two-stage approach for estimating subgroups with heterogeneous treatment effects, where the first-stage aims to predict the response for each unit's "virtual twin" using random forests. We implement the approach described in [Foster et al. (2011)](https://onlinelibrary.wiley.com/doi/10.1002/sim.4322).

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Virtual Twins', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Linear Regression {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

As a baseline comparison method, we implemented a linear regression model with all main effects $X$ and their interactions with the treatment variable $Z$ in order to predict the response $Y$.In the linear regression, we defined a selected subgroup feature to be any covariate whose interaction with the treatment variable yielded a significant p-value ($p < 0.05$).

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Linear Regression', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Linear Regression', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Lasso {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

As a baseline comparison method, we implemented a Lasso regression model [(Tibshirani (1996))](https://www.jstor.org/stable/2346178) with all main effects $X$ and their interactions with the treatment variable $Z$ in order to predict the response $Y$.In the Lasso regression, we defined a selected subgroup feature to be any covariate whose interaction with the treatment variable received a non-zero coefficient.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Lasso', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Lasso', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Distilled Causal Forest (with Rulefit (linear + rules, max depth = 3)) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In this variant of Distilled Causal Forest, we use Rulefit as the second-stage learner (instead of the default CART). The default Rulefit parameters are used except that `type = "both"` and `maxdepth = 3` in `pre::pre()`. That is, both linear structure and rules with maximum depth of 3 are allowed in the fitted Rulefit model.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v1)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Distilled Causal Forest (with Rulefit (linear + rules, max depth = 2)) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In this variant of Distilled Causal Forest, we use Rulefit as the second-stage learner (instead of the default CART). The default Rulefit parameters are used except that `type = "both"` and `maxdepth = 2` in `pre::pre()`. That is, both linear structure and rules with maximum depth of 2 are allowed in the fitted Rulefit model.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v2)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Distilled Causal Forest (with Rulefit (rules only, max depth = 3)) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In this variant of Distilled Causal Forest, we use Rulefit as the second-stage learner (instead of the default CART). The default Rulefit parameters are used except that `type = "rules"` and `maxdepth = 3` in `pre::pre()`. That is, only rules with maximum depth of 3 are allowed in the fitted Rulefit model.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v3)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Distilled Causal Forest (with Rulefit (rules only, max depth = 2)) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

In this variant of Distilled Causal Forest, we use Rulefit as the second-stage learner (instead of the default CART). The default Rulefit parameters are used except that `type = "rules"` and `maxdepth = 2` in `pre::pre()`. That is, only rules with maximum depth of 2 are allowed in the fitted Rulefit model.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(method_objs, 'Distilled Causal Forest (rulefit v4)', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

## Evaluation

<div class='panel panel-default padded-panel'>
At a high-level, we evaluate subgroup estimation performance according to three criteria:

1. **Selected subgroup features**: Whether the features used to define the estimated subgroups match the features used to define the true subgroups (i.e., $X^{(1)}$ and $X^{(2)}$)

2. **Estimated subgroup thresholds**: Whether the estimated subgroup thresholds are close to the true subgroup thresholds

3. **Estimated subgroup average treatment effects (ATEs)**: Whether the estimated subgroup average treatment effects are close to the true subgroup average treatment effects

For tree-based methods, we also evaluate the estimated subgroups under the oracle pruning strategy (i.e., pruning the tree to have depth 2).
</div>

<div class='panel panel-default padded-panel'>

### Subgroup Feature Selection Errors Summary {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each subgroup estimation method, we report the features used to characterize the estimated subgroups and compare them to the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$). In particular, we compute the $F_1$ score, the number of true positives, and the number of false positives between the estimated subgroup features and the true subgroup features.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Feature Selection Errors Summary (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each subgroup estimation method, we report the features used to characterize the estimated subgroups, where the tree has been truncated to a maximum (oracle) depth of 2 for tree-based methods, and compare them to the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$). In particular, we compute the $F_1$ score, the number of true positives, and the number of false positives between the estimated subgroup features and the true subgroup features.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup Feature Selection Errors Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Thresholds Summary {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method, we record all split thresholds for each feature that were used to define the subgroups.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Thresholds Summary (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method, we record the split thresholds for each feature that were used to define the subgroups, up to a maximum tree depth of 2.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Thresholds Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Threshold Distances Summary {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method and for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we compute the root mean squared error between the "best" estimated split threshold for that feature and the true split threshold. In short, we compute the distance between each estimated threshold and each true threshold and report the minimum of these distances for each feature's true threshold.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Threshold Distances Summary (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method and for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we compute the root mean squared error between the "best" estimated split threshold for that feature and the true split threshold. In short, we compute the distance between each estimated threshold and each true threshold and report the minimum of these distances for each feature's true threshold. Only estimated splits that occurred in the first two depths of the tree are considered.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Threshold Distances Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup ATE Errors Summary {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each method, we report the estimation error in subgroup average treatment effect (ATE), measured as the root mean squared error between the true subgroup ATEs and the estimated subgroup ATEs.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup ATE Errors Summary (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each method, we report the estimation error in subgroup average treatment effect (ATE), measured as the root mean squared error between the true subgroup ATEs and the estimated subgroup ATEs. For tree-based methods, the trees have been pruned to a maximum depth of 2.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(eval_objs, 'Subgroup ATE Errors Summary (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

## Visualizations

<div class='panel panel-default padded-panel'>

### Number of Subgroups Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

We plot the total number of estimated subgroups alongside the number of true positive/false positive subgroup features.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - Additive DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - Additive DGP - Varying n', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - AND DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - AND DGP - Varying n', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - OR DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - OR DGP - Varying n', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying n

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Number of Subgroups Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying n', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Feature Selection Errors Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each subgroup estimation method, we plot the $F_1$ score, the number of true positives, and the number of false positives between the estimated subgroup features and the true subgroup features.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Feature Selection Errors Plot (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each subgroup estimation method, we plot the $F_1$ score, the number of true positives, and the number of false positives between the estimated subgroup features and the true subgroup features. Here, the tree-based methods have been pruned to a maximum depth of 2.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Thresholds Distribution Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method and for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we plot the distribution of estimated split thresholds. The true split thresholds are shown as dashed horizontal lines.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Thresholds Distribution Plot (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method abd for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we plot the distribution of estimated split thresholds. The true split thresholds are shown as dashed horizontal lines. Only splits that occurred in the first two depths of the tree are considered.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Threshold Distances Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method and for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we plot the root mean squared error between the "best" estimated split threshold for that feature and the true split threshold. In short, we compute the distance between each estimated threshold and each true threshold and plot the minimum of these distances for each feature's true threshold.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Threshold Distances Plot (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

For each tree-based method and for each of the true subgroup features (i.e., $X^{(1)}$ and $X^{(2)}$), we plot the root mean squared error between the "best" estimated split threshold for that feature and the true split threshold. In short, we compute the distance between each estimated threshold and each true threshold and plot the minimum of these distances for each feature's true threshold. Only estimated splits that occurred in the first two depths of the tree are considered.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Threshold Distances Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup ATE Errors Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

We plot each method's subgroup average treatment effect (ATE) estimation error, measured as the root mean squared error between the true subgroup ATEs and the estimated subgroup ATEs.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - Additive DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - AND DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

##### Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot', 'Varying nrep crossfits - OR DGP-Distilled Rboost (crossfit) - Varying tau_heritability-nreps_crossfit', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup ATE Errors Plot (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

We plot each method's subgroup average treatment effect (ATE) estimation error, measured as the root mean squared error between the true subgroup ATEs and the estimated subgroup ATEs. For tree-based methods, the trees have been pruned to a maximum depth of 2.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup ATE Errors Plot (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Feature and Split Frequency Plots {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

We plot (A) the number of simulation replicates (out of 100), for which each variable was selected (at least once) in the estimated subgroups and (B) the average number of tree splits that used each feature per tree.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots', 'Rulefit Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Feature and Split Frequency Plots (max depth = 2) {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

We plot (A) the number of simulation replicates (out of 100), for which each variable was selected (at least once) in the estimated subgroups and (B) the average number of tree splits that used each feature per tree. Only splits made in the first two depths of the tree are considered.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Feature and Split Frequency Plots (max depth = 2)', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

<div class='panel panel-default padded-panel'>

### Subgroup Stability Diagnostics Plot {.tabset .tabset-pills .tabset-circle .tabset-recipe}

#### `r fontawesome::fa('readme', fill = 'white')` {.tabset .tabset-pills}

[Huang et al. (2025)]() develop a stability-driven model selection procedure to choose an appropriate teacher model in the CDT framework. This teacher model selection procedure leverages the Jaccard subgroup stability index (SSI) to identify the most stable teacher model. We thus perform this teacher model selection procedure and plot the Jaccard SSI for a range of tree depths (1-4). We also plot these teacher model selection results alongside the distribution of features selected at each tree depth across 100 bootstrap samples. Higher Jaccard SSI indicates a more stable teacher model.

#### `r fontawesome::fa('code', fill = 'white')` {.tabset .tabset-pills}

##### Main Simulations - Additive DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - Additive DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - Additive with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - AND DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - AND with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - OR DGP - Varying tau_heritability', what = 'parameters')
```

##### Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability

**Function**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'function')
```

**Input Parameters**

```{r, max.height='200px'}
show_recipe(viz_objs, 'Subgroup Stability Diagnostics Plot', 'Main Simulations - OR with Linear Covariates DGP - Varying tau_heritability', what = 'parameters')
```

</div>

## R Environment {.tabset .tabset-pills .tabset-square}

### R/Packages

#### R {.tabset .tabset-pills .tabset-circle .tabset-recipe}

<div class='panel panel-default padded-panel'>

##### `r fontawesome::fa('table', fill = 'white')`

```{r, results = 'asis'}
print_renv(renv::lockfile_read(project = here::here()), 'R', print_table = TRUE)
```

##### `r fontawesome::fa('code', fill = 'white')`

```{r, max.height='700px'}
print_renv(renv::lockfile_read(project = here::here()), 'R', print_table = FALSE)
```

</div>

#### Packages {.tabset .tabset-pills .tabset-circle .tabset-recipe}

<div class='panel panel-default padded-panel'>

##### `r fontawesome::fa('table', fill = 'white')`

```{r, results = 'asis'}
print_renv(renv::lockfile_read(project = here::here()), 'Packages', print_table = TRUE)
```

##### `r fontawesome::fa('code', fill = 'white')`

```{r, max.height='700px'}
print_renv(renv::lockfile_read(project = here::here()), 'Packages', print_table = FALSE)
```

</div>

### Full renv Diagnostics

<div class='panel panel-default padded-panel'>

```{r, max.height='700px'}
renv::diagnostics()
```

</div>

# Main Simulations {.tabset .tabset-pills .tabset-vmodern}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

## Additive DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

##### Feature and Split Frequency Plots (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## Additive with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive with Linear Covariates DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/Additive with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

##### Feature and Split Frequency Plots (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## AND DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

##### Feature and Split Frequency Plots (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## AND with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND with Linear Covariates DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/AND with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

##### Feature and Split Frequency Plots (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## OR DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## OR with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying n {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR with Linear Covariates DGP/Varying n', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Number of Subgroups Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Number of Subgroups Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Main Simulations/OR with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

##### Subgroup Stability Diagnostics Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 7, fig.width = 11, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Stability Diagnostics Plot', 'visualizer')
```

##### Subgroup Feature Selection Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot (max depth = 2)', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot (max depth = 2)', 'visualizer')
```

##### Threshold Distances Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot (max depth = 2)', 'visualizer')
```

##### Subgroup ATE Errors Plot (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot (max depth = 2)', 'visualizer')
```

##### Feature and Split Frequency Plots (max depth = 2)

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots (max depth = 2)', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

# Rulefit Simulations {.tabset .tabset-pills .tabset-vmodern}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

## Additive DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/Additive DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/Additive DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## Additive with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/Additive with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/Additive with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## AND DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/AND DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/AND DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## AND with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/AND with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/AND with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## OR DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/OR DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/OR DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## OR with Linear Covariates DGP {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/OR with Linear Covariates DGP', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Rulefit Simulations/OR with Linear Covariates DGP/Varying tau_heritability', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Subgroup Thresholds Distribution Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Thresholds Distribution Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

##### Feature and Split Frequency Plots

###### {.tabset .tabset-pills}

```{r, fig.height = 7.5, fig.width = 18, out.width = '100%', add.panel = TRUE}
show_results(results, 'Feature and Split Frequency Plots', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

# Varying nrep crossfits {.tabset .tabset-pills .tabset-vmodern}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

## Additive DGP-Distilled Rboost (crossfit) {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/Additive DGP-Distilled Rboost (crossfit)', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability-nreps_crossfit {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/Additive DGP-Distilled Rboost (crossfit)/Varying tau_heritability-nreps_crossfit', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## AND DGP-Distilled Rboost (crossfit) {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/AND DGP-Distilled Rboost (crossfit)', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability-nreps_crossfit {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/AND DGP-Distilled Rboost (crossfit)/Varying tau_heritability-nreps_crossfit', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

## OR DGP-Distilled Rboost (crossfit) {.tabset .tabset-pills}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/OR DGP-Distilled Rboost (crossfit)', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

### Varying tau_heritability-nreps_crossfit {.tabset .tabset-pills .tabset-circle}

```{r, results = 'asis'}
results <- get_exp_results(
  '/Users/ttang4/Documents/Research/Causal Subgroups/causalDT/causalDT-manuscript/results/Varying nrep crossfits/OR DGP-Distilled Rboost (crossfit)/Varying tau_heritability-nreps_crossfit', show_eval = FALSE, show_viz = TRUE, eval_cache = '.rds', viz_cache = '.png'
)
```

#### `r fontawesome::fa('chart-bar', fill = 'white')`

##### Subgroup Feature Selection Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 5, fig.width = 12, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup Feature Selection Errors Plot', 'visualizer')
```

##### Threshold Distances Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 9, out.width = '100%', add.panel = TRUE}
show_results(results, 'Threshold Distances Plot', 'visualizer')
```

##### Subgroup ATE Errors Plot

###### {.tabset .tabset-pills}

```{r, fig.height = 4.5, fig.width = 8, out.width = '100%', add.panel = TRUE}
show_results(results, 'Subgroup ATE Errors Plot', 'visualizer')
```

#### `r fontawesome::fa('code', fill = 'white')`

**Parameter Values**

```{r, max.height='200px'}
show_results(results, NULL, 'vary_params')
```

### 2025-02-13 README.Rmd
fix readme links

@@
   collapse = TRUE,
-  comment = "#>"
+  comment = "#>",
+  fig.path = file.path("causalDT", "man", "figures", "README-")
 )
@@
 
-```{r}
+```{r load-data}
 # install.packages("speff2trial")
 library(speff2trial)
+library(dplyr)
 
@@
 
-```{r fig.width=12}
+```{r causalDT, fig.width=12}
 library(causalDT)
@@
 
-```{r}
+```{r jaccard}
 # selecting between causal forest versus rboost

### 2025-02-13 causalDT/README.Rmd
fix readme links

@@
   collapse = TRUE,
-  comment = "#>"
+  comment = "#>",
+  fig.path = file.path("man", "figures", "README-")
 )

### 2025-03-21 causalDT-manuscript/meals/shared_experiments.R
update experiments and figures

@@ -1,9 +1,9 @@
 experiment <- create_experiment(
-  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results_bcf", EXP_NAME)
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods
   add_method(distilled_causal_forest_stability_pruned_method) |>
-  # add_method(distilled_rboost_stability_pruned_method) |>
+  add_method(distilled_rboost_stability_pruned_method) |>
   add_method(distilled_bcf_stability_pruned_method) |>
   ### baseline causal tree methods
   add_method(causal_tree_stability_pruned_method) |>
@@ -35,7 +35,7 @@ experiment <- create_experiment(
   # add_visualizer(subgroup_ates_plot) |>
 
 rulefit_experiment <- create_experiment(
-  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results_bcf", EXP_NAME)
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods
   add_method(distilled_causal_forest_method) |>
@@ -56,7 +56,7 @@ rulefit_experiment <- create_experiment(
   add_visualizer(subgroup_nsplits_rulefit_plot)
 
 crossfit_experiment <- create_experiment(
-  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results_bcf", EXP_NAME)
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods without crossfit
   add_method(distilled_rboost_no_crossfit_method) |>
@@ -77,7 +77,7 @@ crossfit_experiment <- create_experiment(
   add_visualizer(subgroup_ates_err_crossfit_plot)
 
 rwd_experiment <- create_experiment(
-  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results_bcf", EXP_NAME)
+  name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   ### distillation methods
   add_method(distilled_causal_forest_stability_pruned_method) |>
@@ -98,7 +98,7 @@ rwd_experiment <- create_experiment(
   add_visualizer(subgroup_stability_plot)
 
 example_experiment <- create_experiment(
[…]

### 2025-03-21 causalDT-manuscript/meals/shared_visualizers.R

@@ -1,8 +1,8 @@
 method_levels <- c(
-  "Distilled Causal Forest",
-  "Distilled Causal Forest (unpruned)",
   "Distilled Rboost",
   "Distilled Rboost (unpruned)",
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
   "Distilled BCF",
   "Distilled BCF (unpruned)",
   "Virtual Twins",
@@ -18,10 +18,10 @@ method_levels <- c(
 )
 
 COLORS <- c(
-  "Distilled Causal Forest" = "#1f5d8f",
-  "Distilled Causal Forest (unpruned)" = "#1f5d8f",
   "Distilled Rboost" = "#6aafe4",
   "Distilled Rboost (unpruned)" = "#6aafe4",
+  "Distilled Causal Forest" = "#1f5d8f",
+  "Distilled Causal Forest (unpruned)" = "#1f5d8f",
   "Distilled BCF" = "#1c3145",
   "Distilled BCF (unpruned)" = "#1c3145",
   "Virtual Twins" = "#768c50",
@@ -36,10 +36,10 @@ COLORS <- c(
   "Rulefit (rules only, max depth = 2)" = "#7570B3"
 )
 LINETYPES <- c(
-  "Distilled Causal Forest" = "solid",
-  "Distilled Causal Forest (unpruned)" = "dashed",
   "Distilled Rboost" = "solid",
   "Distilled Rboost (unpruned)" = "dashed",
+  "Distilled Causal Forest" = "solid",
+  "Distilled Causal Forest (unpruned)" = "dashed",
   "Distilled BCF" = "solid",
   "Distilled BCF (unpruned)" = "dashed",
   "Virtual Twins" = "solid",

### 2025-03-21 causalDT-manuscript/notebooks/paper_figures.Rmd
add BCF (#2)

@@
 COLORS <- c(
+  "Distilled Rboost" = "#6aafe4",
   "Distilled Causal Forest" = "#1f5d8f",
-  "Distilled Rboost" = "#6aafe4",
+  "Distilled BCF" = "#1c3145",
   "Virtual Twins" = "#768c50",
@@
 KEEP_METHODS <- c(
+  "Distilled Rboost",
   "Distilled Causal Forest",
-  "Distilled Rboost",
+  "Distilled BCF",
   "Virtual Twins",
@@
         ggplot2::guides(
-          color = "none", fill = "none"
+          color = "none", fill = "none", linetype = "none"
         )
@@
 KEEP_METHODS <- c(
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
   "Distilled Causal Forest",
   "Distilled Causal Forest (unpruned)",
-  "Distilled Rboost",
-  "Distilled Rboost (unpruned)",
+  "Distilled BCF",
+  "Distilled BCF (unpruned)",
   "Causal Tree",
@@
 KEEP_METHODS <- c(
+  "Distilled Rboost",
   "Distilled Causal Forest",
-  "Distilled Rboost",
+  "Distilled BCF",
   "Causal Tree"
@@
       dplyr::mutate(
-        .metric = "Subgroup ATE RMSE",
+        .metric = "Subgroup\nATE RMSE",
         .value = mean_ate_err
@@
 KEEP_METHODS <- c(
+  "Distilled Rboost",
+  "Distilled Rboost (unpruned)",
   "Distilled Causal Forest",
   "Distilled Causal Forest (unpruned)",
-  "Distilled Rboost",
-  "Distilled Rboost (unpruned)",
+  "Distilled BCF",
+  "Distilled BCF (unpruned)",
   "Virtual Twins",
@@
   filename = file.path(FIG_DIR, "sim_ntrees.pdf"),
-  height = 15.5, 
+  height = 18, 
   width = 13

### 2025-03-21 causalDT-manuscript/meals/shared_experiments.R

@@ -4,6 +4,7 @@ experiment <- create_experiment(
   ### distillation methods
   add_method(distilled_causal_forest_stability_pruned_method) |>
   add_method(distilled_rboost_stability_pruned_method) |>
+  add_method(distilled_bcf_stability_pruned_method) |>
   ### baseline causal tree methods
   add_method(causal_tree_stability_pruned_method) |>
   ### other existing methods
@@ -81,6 +82,7 @@ rwd_experiment <- create_experiment(
   ### distillation methods
   add_method(distilled_causal_forest_stability_pruned_method) |>
   add_method(distilled_rboost_stability_pruned_method) |>
+  add_method(distilled_bcf_stability_pruned_method) |>
   ### baseline causal tree methods
   add_method(causal_tree_stability_pruned_method) |>
   ### other existing methods
@@ -99,6 +101,7 @@ example_experiment <- create_experiment(
   name = EXP_NAME, save_dir = file.path(SAVE_DIR, "results", EXP_NAME)
 ) |>
   add_method(distilled_causal_forest_method) |>
+  add_method(distilled_bcf_method) |>
   add_method(causal_tree_method) |>
   add_evaluator(subgroup_feature_selection_errors_summary) |>
   add_visualizer(num_subgroups_plot)

### 2025-03-21 causalDT-manuscript/meals/shared_methods.R

@@ -16,6 +16,19 @@ distilled_rboost_method <- create_method(
   rpart_prune = "min"
 )
 
+distilled_bcf_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled BCF",
+  teacher_model = purrr::partial(
+    causalDT::bcf, pihat = 0.5, n_threads = 1, verbose = FALSE, no_output = TRUE
+  ),
+  teacher_predict = causalDT::predict_bcf,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1,
+  rpart_prune = "min"
+)
+
+
 # rulefit methods without stability diagnostics
 distilled_causal_forest_rulefit_v1_method <- create_method(
   .method_fun = causalDT_method,
@@ -66,6 +79,19 @@ distilled_rboost_stability_method <- create_method(
   rpart_prune = "min"
 )
 
+distilled_bcf_stability_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled BCF",
+  teacher_model = purrr::partial(
+    causalDT::bcf, pihat = 0.5, n_threads = 1, verbose = FALSE, no_output = TRUE
+  ),
+  teacher_predict = causalDT::predict_bcf,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1,
+  B_stability = 100,
+  rpart_prune = "min"
+)
+
 # with stability diagnostics and pruning options
 distilled_causal_forest_stability_pruned_method <- create_method(
   .method_fun = causalDT_method,
@@ -79,6 +105,19 @@ distilled_rboost_stability_pruned_method <- create_method(
   .method_fun = causalDT_method,
   .name = "Distilled Rboost",
   teacher_model = causalDT::rboost,
+  B_stability = 100,
+  rpart_prune = c("none", "min")
+)
+
+distilled_bcf_stability_pruned_method <- create_method(
+  .method_fun = causalDT_method,
+  .name = "Distilled BCF",
+  teacher_model = purrr::partial(
+    causalDT::bcf, pihat = 0.5, n_threads = 1, verbose = FALSE, no_output = TRUE
+  ),
+  teacher_predict = causalDT::predict_bcf,
+  nfolds_crossfit = 1,
+  nreps_crossfit = 1,
   B_stability = 100,
   rpart_prune = c("none", "min")
 )

### 2025-03-21 causalDT-manuscript/meals/shared_visualizers.R

@@ -1,8 +1,10 @@
 method_levels <- c(
-  "Distilled Causal Forest",
-  "Distilled Causal Forest (unpruned)",
   "Distilled Rboost",
   "Distilled Rboost (unpruned)",
+  "Distilled Causal Forest",
+  "Distilled Causal Forest (unpruned)",
+  "Distilled BCF",
+  "Distilled BCF (unpruned)",
   "Virtual Twins",
   "Causal Tree",
   "Causal Tree (unpruned)",
@@ -16,10 +18,12 @@ method_levels <- c(
 )
 
 COLORS <- c(
-  "Distilled Causal Forest" = "#1f5d8f",
-  "Distilled Causal Forest (unpruned)" = "#1f5d8f",
   "Distilled Rboost" = "#6aafe4",
   "Distilled Rboost (unpruned)" = "#6aafe4",
+  "Distilled Causal Forest" = "#1f5d8f",
+  "Distilled Causal Forest (unpruned)" = "#1f5d8f",
+  "Distilled BCF" = "#1c3145",
+  "Distilled BCF (unpruned)" = "#1c3145",
   "Virtual Twins" = "#768c50",
   "Causal Tree" = "#953a2f",
   "Causal Tree (unpruned)" = "#953a2f",
@@ -32,10 +36,12 @@ COLORS <- c(
   "Rulefit (rules only, max depth = 2)" = "#7570B3"
 )
 LINETYPES <- c(
-  "Distilled Causal Forest" = "solid",
-  "Distilled Causal Forest (unpruned)" = "dashed",
   "Distilled Rboost" = "solid",
   "Distilled Rboost (unpruned)" = "dashed",
+  "Distilled Causal Forest" = "solid",
+  "Distilled Causal Forest (unpruned)" = "dashed",
+  "Distilled BCF" = "solid",
+  "Distilled BCF (unpruned)" = "dashed",
   "Virtual Twins" = "solid",
   "Causal Tree" = "solid",
   "Causal Tree (unpruned)" = "dashed",
@@ -51,6 +57,7 @@ LINETYPES <- c(
 COLORS2 <- COLORS
 COLORS2["Distilled Causal Forest (unpruned)"] <- "#96aac6"
 COLORS2["Distilled Rboost (unpruned)"] <- "#bad6f2"
+COLORS2["Distilled BCF (unpruned)"] <- "#d6d9dd"
 COLORS2["Causal Tree (unpruned)"] <- "#d09a90"
 
 CROSSFIT_COLORS <- c(

### 2025-03-21 causalDT/R/causalDT.R

@@ -39,9 +39,11 @@ NULL
 #'   treatment effects. If NULL, a holdout set of size `holdout_prop` x nrow(X)
 #'   is randomly selected.
 #' @param teacher_model Teacher model used to estimate individual-level
-#'   treatment events. Should be either "causal_forest" (default) or a function.
+#'   treatment events. Should be either "causal_forest" (default),
+#'   "bcf", or a function.
 #'   If "causal_forest", \code{grf::causal_forest()} is used as the teacher
-#'   model. Otherwise, the function should take in the named arguments
+#'   model. If "bcf", \code{bcf::bcf()} is used as the teacher model.
+#'   Otherwise, the function should take in the named arguments
 #'   `X`, `Y`, `Z`, (corresponding to the covariates, outcome, and treatment
 #'   data, respectively) as well as (optional) additional arguments passed to
 #'   the function via `...`. Moreover, the function should return a model object
@@ -168,6 +170,21 @@ causalDT <- function(X, Y, Z,
     }
     if (is.null(nreps_crossfit)) {
       nreps_crossfit <- 1
+    }
+  } else if (identical(teacher_model, "bcf")) {
+    teacher_model <- bcf
+    teacher_predict <- predict_bcf
+    if (is.null(nfolds_crossfit)) {
+      nfolds_crossfit <- 1
+    }
+    if (nfolds_crossfit != 1) {
+      stop("`nfolds_crossfit` must be 1 when `teacher_model` is 'bcf'.")
+    }
+    if (is.null(nreps_crossfit)) {
+      nreps_crossfit <- 1
+    }
+    if (nreps_crossfit != 1) {
+      stop("`nreps_crossfit` must be 1 when `teacher_model` is 'bcf'.")
     }
   } else if (!is.function(teacher_model)) {
     stop("`teacher_model` must be a function or 'causal_forest'.")

### 2025-03-21 causalDT/R/teacher.R

@@ -13,6 +13,7 @@
 #' - \code{rlasso()}: wrapper around \code{rlearner::rlasso()}
 #' - \code{rkern()}: wrapper around \code{rlearner::rkern()}
 #'
+#' @inheritParams bcf::bcf
 #' @inheritParams shared_args
 #' @param ... Additional arguments to pass to the base model functions.
 #'
@@ -55,4 +56,38 @@ rkern <- function(X, Y, Z, ...) {
   rlearner::rkern(
     x = X, y = Y, w = Z, ...
   )
+}
+
+#' @rdname teacher_models
+#' @export
+bcf <- function(X, Y, Z, pihat = "default", w = NULL,
+                nburn = 2000, nsim = 1000, n_threads = 1, ...) {
+  if (identical(pihat, "default")) {
+    pihat_fit <- glm(Z ~ X, family = "binomial")
+    pihat <- predict(pihat_fit, data.frame(X), type = "response")
+  } else if (length(pihat) == 1) {
+    pihat <- rep(pihat, nrow(X))
+  }
+  if (is.null(w)) {
+    w <- rep(1, nrow(X))
+  }
+  dots_ls <- rlang::dots_list(...)
+  if ("x_moderate" %in% names(dots_ls)) {
+    X_moderate <- dots_ls$x_moderate
+  } else {
+    X_moderate <- X
+  }
+  bcf::bcf(
+    y = Y, z = Z, x_control = X, x_moderate = X_moderate,
+    pihat = pihat, w = w, nburn = nburn, nsim = nsim, n_threads = n_threads,
+    ...
+  )
+}
+
+#' @rdname teacher_models
+#' @export
+predict_bcf <- function(...) {
+  # predict(...)
+  object <- rlang::dots_list(...)[[1]]
+  colMeans(object$tau)
 }

### 2025-03-21 causalDT/tests/testthat/test-causalDT.R

@@ -21,6 +21,11 @@ test_that("causalDT works", {
 
   out <- causalDT(
     X = X, Y = Y, Z = Z,
+    teacher_model = "bcf"
+  )
+
+  out <- causalDT(
+    X = X, Y = Y, Z = Z,
     teacher_model = rlasso,
     nfolds_crossfit = 2,
     nreps_crossfit = 50

### 2025-03-21 causalDT/R/diagnostics-stability.R
add general stability function

@@ -189,4 +189,126 @@ evaluate_subgroup_stability <- function(estimator, fit, X, y, Z = NULL,
 }
 
 
+#' Evaluate stability of generic HTE estimator
+#'
+#' @description This function computes the stability of a general HTE estimator,
+#'   fitted across different subsamples of the data. At a high-level, for each
+#'   pair of estimated treatment effect vectors (each estimated using a
+#'   different subsample of the data), some metric (e.g., Jaccard, Adjusted
+#'   Rand Index, or Spearman correlation) is computed to assess the similarity
+#'   between the two candidates. Since Jaccard and Adjusted Rand Index are
+#'   metrics for comparing sets, the estimated treatment effects are discretized
+#'   into `n_strata` strata before computing the metric.
+#'
+#' @inheritParams shared_args
+#'
+#' @param estimator Function used to estimate individual-level treatment
+#'   estimates. The function should take in `X`, `y`, and `Z` (which can be
+#'   `NULL`) and return a vector of estimated treatment effects (should be
+#'   vector of length equal to number of rows in `X`.
+#' @param n_strata Number of strata used to discretize the estimated treatment
+#'   effects when calculating the Jaccard index or Adjusted Rand Index. Default
+#'   is 2:10.
+#' @param metrics Vector of metrics to use in evaluating stability. Options
+#'   include "jaccard", "ARI", and "spearman". Default is all metrics.
+#' @param subsample Proportion of the data to use in each replicate. Default is
+#'   0.8.
+#' @param B Number of subsamples to use in evaluating stability diagnostics.
+#'   Default is 100.
+#'
+#' @returns A list with the following elements:
+#' \item{mean_results}{List of mean stability metrics across all subsamples.}
+#' \item{full_results}{List of (unaggregated) stability metrics across all subsamples.}
+#'
+#' @examples
+#' estimator <- function(X, y, Z) {
+#'   return(rnorm(n = nrow(X)))
+#' }
+#' n <- 100
+#' X <- matrix(rnorm(n), nrow = n, ncol = 10)
+#' y <- rnorm(n)
+#' Z <- rbinom(n, 1, 0.5)
+#' out <- evaluate_stability(estimator, X, y, Z)
+#'
+#' @export
+evaluate_stability <- function(estimator, X, y, Z = NULL,
[…]

### 2025-03-21 causalDT/tests/testthat/test-stability.R

@@ -45,3 +45,17 @@ test_that("jaccard stability works", {
   y <- sample(1:G, size = n, replace = TRUE) - 1
   expect_equal(jaccardSSI(x, y), true_jaccard(x, y))
 })
+
+
+test_that("evaluate_stability works", {
+  estimator <- function(X, ...) {
+    return(rnorm(n = nrow(X)))
+  }
+  B <- 10
+  subsample <- 0.8
+  n <- 100
+  X <- matrix(rnorm(n), nrow = n, ncol = 10)
+  y <- rnorm(n)
+  Z <- rbinom(n, 1, 0.5)
+  out <- evaluate_stability(estimator, X, y, Z)
+})

### 2025-03-21 causalDT/R/teacher.R
add propensity weights argument

@@ -22,9 +22,9 @@ NULL
 
 #' @rdname teacher_models
 #' @export
-causal_forest <- function(X, Y, Z, ...) {
+causal_forest <- function(X, Y, Z, W = NULL, ...) {
   grf::causal_forest(
-    X = X, Y = Y, W = Z, ...
+    X = X, Y = Y, W = Z, W.hat = W, ...
   )
 }
 
@@ -36,37 +36,41 @@ predict_causal_forest <- function(...) {
 
 #' @rdname teacher_models
 #' @export
-rboost <- function(X, Y, Z, ...) {
+rboost <- function(X, Y, Z, W = NULL, ...) {
   rlearner::rboost(
-    x = X, y = Y, w = Z, ...
+    x = X, y = Y, w = Z, p_hat = W, ...
   )
 }
 
 #' @rdname teacher_models
 #' @export
-rlasso <- function(X, Y, Z, ...) {
+rlasso <- function(X, Y, Z, W = NULL, ...) {
   rlearner::rlasso(
-    x = X, y = Y, w = Z, ...
+    x = X, y = Y, w = Z, p_hat = W, ...
   )
 }
 
 #' @rdname teacher_models
 #' @export
-rkern <- function(X, Y, Z, ...) {
+rkern <- function(X, Y, Z, W = NULL, ...) {
   rlearner::rkern(
-    x = X, y = Y, w = Z, ...
+    x = X, y = Y, w = Z, p_hat = W, ...
   )
 }
 
 #' @rdname teacher_models
 #' @export
-bcf <- function(X, Y, Z, pihat = "default", w = NULL,
+bcf <- function(X, Y, Z, W = NULL, pihat = "default", w = NULL,
                 nburn = 2000, nsim = 1000, n_threads = 1, ...) {
-  if (identical(pihat, "default")) {
-    pihat_fit <- glm(Z ~ X, family = "binomial")
-    pihat <- predict(pihat_fit, data.frame(X), type = "response")
-  } else if (length(pihat) == 1) {
-    pihat <- rep(pihat, nrow(X))
+  if (is.null(W)) {
+    if (identical(pihat, "default")) {
+      pihat_fit <- glm(Z ~ X, family = "binomial")
+      pihat <- predict(pihat_fit, data.frame(X), type = "response")
+    } else if (length(pihat) == 1) {
+      pihat <- rep(pihat, nrow(X))
+    }
+  } else {
+    pihat <- W
   }
   if (is.null(w)) {
     w <- rep(1, nrow(X))

### 2025-03-21 causalDT/R/utils-crossfit.R

@@ -1,24 +1,31 @@
 #' Crossfit wrapper around estimators
 #'
 #' @keywords internal
-crossfit <- function(estimator, X, Y, Z, split_idxs, ...) {
+crossfit <- function(estimator, X, Y, Z, W = NULL, split_idxs, ...) {
   nfolds <- length(unique(split_idxs))
   fit_ls <- list()
+  dots_ls <- rlang::dots_list(...)
+  if (length(dots_ls) == 0) {
+    dots_ls <- NULL
+  }
   for (foldid in 1:nfolds) {
     if (nfolds == 1) {
       train_idxs <- rep(TRUE, length(split_idxs))
     } else {
       train_idxs <- split_idxs != foldid
     }
-    fit_ls[[foldid]] <- do.call(
+    fit_ls[[foldid]] <- R.utils::doCall(
       estimator,
-      args = c(
+      alwaysArgs = c(
         list(
           X = X[train_idxs, , drop = FALSE],
           Y = Y[train_idxs],
           Z = Z[train_idxs]
         ),
-        ...
+        dots_ls
+      ),
+      args = list(
+        W = W[train_idxs]
       )
     )
   }

### 2025-03-21 causalDT/tests/testthat/test-causalDT.R

@@ -37,4 +37,23 @@ test_that("causalDT works", {
       teacher_model = teacher_model
     )
   }
+
+  # testing with weights
+  W <- runif(n)
+  out <- causalDT(
+    X = X, Y = Y, Z = Z, W = W,
+    teacher_model = "causal_forest"
+  )
+
+  out <- causalDT(
+    X = X, Y = Y, Z = Z, W = W,
+    teacher_model = "bcf"
+  )
+
+  out <- causalDT(
+    X = X, Y = Y, Z = Z, W = W,
+    teacher_model = rlasso,
+    nfolds_crossfit = 2,
+    nreps_crossfit = 50
+  )
 })
